---
title: "career_plots"
author: "Connor Whalen"
date: "2024-08-26"
output:
  html_document:
    theme: readable
    highlight: textmate
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

##Background
This code was taken from 'lots_sampled' script in the TUBRI repository for the purposes of creating a plot that shows sampled fish AND the extreme weather events that occurred in the area over the specific time-span of the project.
- LA = 1963 to 2005
- NM = 1931 to 2010

### Message from the original code
Creating a map and plot just like the one in the CAREER proposal, but updated to reflect the lat, long, and year of all the samples we ACTUALLY processed (not just the ones that are available at TUBRI).

#### Install packages
```{r install, echo=FALSE, eval=FALSE}
install.packages("mapdata")
install.packages("ggmap")
install.packages("raster")
install.packages("wesanderson")
install.packages("pdftools")
```

#### Load packages
```{r load, echo=FALSE}
library(maps)
library(mapdata)
library(scales) #for transparency
library(maps)
library(ggmap)
library(tidyverse)
library(tidyr)
library(dplyr)
library(cowplot)
library(sp)
library(raster)
library(pdftools)
library(wesanderson)
library(grid)
```

#### Load data about TUBRI lots
```{r}
psite_data <- read.csv("~/Desktop/UW/TUBRI/data/processed/Full_dataset_with_psite_life_history_info_2024.11.21.csv", header = TRUE, sep = ",") %>%
  janitor::clean_names()
```

## Building the plots for the NOLA dataset
### First you need to reduce the dataset to make each fish a row
```{r}
la_fish_sampled <- psite_data %>%
  group_by(fish_sp_x, individual_fish_id, ci, latitude, longitude, year_collected) %>%
  summarize(count = n())

la_fish_sampled <- la_fish_sampled %>%
  group_by(fish_sp_x, ci, year_collected) %>%
  summarize(count = n())
```

### Make the map
```{r}
asd <- la_fish_sampled %>% 
  group_by(fish_sp_x, year_collected) %>% 
  summarize(count=n())

## map function currently not working
bounds <- c(left = -89.855, bottom = 30.69, right = -89.81, top = 30.79)
la_map <- get_stadiamap(bounds, zoom = 12, maptype = "stamen_terrain_background") %>% 
  ggmap() + 
  geom_point(y = 30.76558198250576, x = -89.83398463056083, size = 4) + 
  geom_point(data = la_fish_sampled, aes(x = longitude, y = latitude, fill = ci), shape = 21, size = 4) + 
  scale_fill_manual(values = c("white","tan")) + 
  xlab("Latitude") + 
  ylab("Longitude") +
  theme(
    plot.margin = unit(c(0, 0, 0, 0), "cm"), 
    axis.title.x = element_text(size = 20), 
    axis.title.y = element_text(size = 20), 
    axis.text.x = element_text(size = 8), 
    axis.text.y = element_text(size = 8),
    legend.position = "right"
  )

plot(la_map)
```

Building a standalone legend for the LA map
```{r}
legend_wsn_la_map <- grobTree(
  pointsGrob(x = 0.28, y = 0.4, pch = 21, size = unit(25, "mm"), gp = gpar(col = "black", fill = "white")),
  textGrob("Control (above mill)", x = 0.3, y = 0.4, just = "left", gp = gpar(fontsize = 36)),
  pointsGrob(x = 0.28, y = 0.3, pch = 21, size = unit(25, "mm"), gp = gpar(col = "black", fill = "tan")),
  textGrob("Impact (below mill)", x = 0.3, y = 0.3, just = "left", gp = gpar(fontsize = 36)),
  pointsGrob(x = 0.28, y = 0.2, pch = 21, size = unit(25, "mm"), gp = gpar(col = "black", fill = "black")),
  textGrob("Pulp Mill", x = 0.3, y = 0.2, just = "left", gp = gpar(fontsize = 36))
)


bordered_legend_wsn_la_map <- grobTree(
  rectGrob(x = 0.41, y = 0.31, width = 0.5, height = 0.38, 
           gp = gpar(col = "black", fill = NA, lwd = 2)), 
  legend_wsn_la_map 
)


### make the legend alone
legend_legend_wsn_la_map_final <- ggplot() + 
  annotation_custom(bordered_legend_wsn_la_map, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) + 
  theme_void() 

print(legend_legend_wsn_la_map_final)

```

Create the palette for use in the plot
```{r, echo=FALSE}
wes_palette("Zissou1")
pal<-wes_palette(name = "Zissou1", 6, type = "continuous")
```


Plot all the fish species as well as the extreme weather events in the same plot
This is the one that Daki recommended:
```{r}
cc <- table(la_fish_sampled$ci)
print(cc)

# Create a summary dataframe for the annotations
annotation_data <- data.frame(
  ci = c("impact",
         "control"),
  count = c(742, 446),
  year_collected = 1965  # X-coordinate for all annotations
)

la_fish_plot <- ggplot(data = final_la, 
                       aes(x = year_collected, y = count)) + 
annotate(geom = "rect", xmin = 1963, xmax = 1964, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1964, xmax = 1965, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1968, xmax = 1969, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1970, xmax = 1971, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1973, xmax = 1974, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1978, xmax = 1979, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1984.2, xmax = 1985.2, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1985.2, xmax = 1986.2, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1985.8, xmax = 1986.8, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1988.2, xmax = 1989.2, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1988.8, xmax = 1989.8, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1991, xmax = 1992, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1994, xmax = 1995, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1995.5, xmax = 1996.5, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1996, xmax = 1997, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1997, xmax = 1998, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1998, xmax = 1999, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 1998.5, xmax = 1999.5, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 2002, xmax = 2003, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 2002.5, xmax = 2003.5, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
annotate(geom = "rect", xmin = 2003, xmax = 2004, ymin = -Inf, ymax = Inf, 
         fill = "lightgrey", colour = NA, alpha = 0.75) + # hurricane
   annotate(geom = "rect", xmin = 1966.75, xmax = 1969.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
   annotate(geom = "rect", xmin = 1975.75, xmax = 1977.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
   annotate(geom = "rect", xmin = 1980.75, xmax = 1981.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
   annotate(geom = "rect", xmin = 1984.75, xmax = 1986.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
   annotate(geom = "rect", xmin = 1999.75, xmax = 2001.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
   annotate(geom = "rect", xmin = 1965.50, xmax = 1965.75, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
   annotate(geom = "rect", xmin = 1995.50, xmax = 1995.50, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
   annotate(geom = "rect", xmin = 1972.75, xmax = 1973.50, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
   annotate(geom = "rect", xmin = 1999.75, xmax = 2001.25, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
   geom_point(stat = "identity", aes(colour = fish_sp_x), size = 5, position = "dodge", show.legend = FALSE, stroke = 1.5) + 
   facet_grid(ci ~ ., labeller = labeller(ci = facet_labels_wsn)) + # Facet by category
   scale_color_manual(values = pal[1:7], name = '') +  # Use scale_color_manual for point colors
   xlab("Year Collected") + 
   ylab("Number of Fish Dissected") +
   scale_x_continuous(limits = c(1962, 2006), breaks = c(1960, 1965, 1970, 1975, 1980, 1985, 1990, 1995, 2000, 2005), expand = expansion(mult = c(0, 0))) + 
   theme_bw() + 
   theme(strip.background = element_rect(fill = NA, color = "white"),
         panel.background = element_rect(fill = NA, color = "darkgrey"),
         axis.title = element_text(size = 28),
         axis.text = element_text(size = 26),
         strip.text = element_text(size = 22),
         legend.text = element_text(size = 26)) +
   # Add text annotations dynamically
   geom_text(data = annotation_data, 
             aes(x = year_collected, y = 30, label = paste("n =", count)),
             size = 5, hjust = 1)

plot(la_fish_plot)
```



Simpler plot for use in GRFP
```{r, echo=FALSE}
##### trying new methods for simpler GRFP plot
custom_breaks <- c(0, 20, 40, 60, 80, 100, 120, 140)

la_fish_plot_grfp <- ggplot(data = la_fish_sampled, 
                    aes(x = year_collected)) +
  annotate(geom = "rect", xmin = 1966.75, xmax = 1969.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
  annotate(geom = "rect", xmin = 1975.75, xmax = 1977.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
  annotate(geom = "rect", xmin = 1980.75, xmax = 1981.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
  annotate(geom = "rect", xmin = 1984.75, xmax = 1986.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
  annotate(geom = "rect", xmin = 1999.75, xmax = 2001.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
  annotate(geom = "rect", xmin = 1965.50, xmax = 1965.75, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
  annotate(geom = "rect", xmin = 1995.50, xmax = 1995.50, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
  annotate(geom = "rect", xmin = 1972.75, xmax = 1973.50, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
  annotate(geom = "rect", xmin = 1999.75, xmax = 2001.25, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
  geom_vline(xintercept = 1963, linetype = "dashed") + #collectionstart
  geom_vline(xintercept = 1972.5, linetype="dotted") + #CWA
  geom_vline(xintercept = 2005, linetype="dashed") + #collectionend
  geom_vline(xintercept = 1964, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1965, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1969, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1971, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1974, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1979, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1985.1, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1985.4, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1985.6, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1988.1, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1988.6, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1992, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1995, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1996, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1997, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1998.1, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 1998.6, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 2002.1, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 2002.6, linetype="dotdash", colour = "orange") + #hurricane
  geom_vline(xintercept = 2004, linetype="dotdash", colour = "orange") + #hurricane
  xlim(1962, 2006) +
  geom_histogram(data = la_fish_sampled, 
             aes(x = year_collected), shape = 21, size = 3,
             show.legend = FALSE, bins = 40) +
  xlab("") +
  ylab("") + 
  scale_y_continuous(expand = c(0,0), breaks = custom_breaks, limits = c(0, 120)) + theme_classic()  +
  scale_linetype_manual(name = "Events", 
                        values = c("dashed" = "dashed", "dotted" = "dotted", "dotdash" = "dotdash"),
                        labels = c("Collection Start", "CWA", "Hurricanes")) +
  guides(linetype = guide_legend(override.aes = list(colour = c("black", "black", "brown")))) 

plot(la_fish_plot_grfp)

```

## unedited past this point as of 11/6/2024
## Add the ABQ data and plot
- taken from the UNM repo map file. 

#### load dataset
```{r}
lots<-read.csv("~/Desktop/UW/UNM/data/final_lots_CAREER.csv") %>%
  janitor::clean_names()
```

create the shape for the city map  --- not currently working
```{r}
polygon<-readOGR("Albuquerque_City_Limits-polygon.shp")
polygon_df<-fortify(polygon)

water<-readOGR("NHDArea.shp")
water_df<-fortify(water)
```

create city map
```{r}
bounds <- c(left = -106.89, bottom = 34.82, right = -106.45, top = 35.66)
map <- get_stadiamap(bounds, zoom = 11, maptype = "stamen_terrain_background") %>% 
  ggmap() +
  geom_point() +
  xlab("Longitude (°W)") +
  ylab("Latitude (°N)") +
  theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20),
        axis.text = element_text(size = 14), axis.title = element_text(size = 14)) +
  geom_rect(xmin = -106.89, ymin = 34.8, xmax = -106.45, ymax = 35.2102673, fill = "grey", alpha = 0.2, linetype = "blank") +
  geom_hline(yintercept = 35.2102673, linetype = "dashed") +
  #geom_map(data=water_df,map=water_df,aes(x=long,y=lat,map_id=id),color="lightsteelblue3",fill="lightsteelblue3")+
  #geom_map(data=polygon_df,map=polygon_df,aes(x=long,y=lat,map_id=id),color="black",fill=NA)+
  annotate("text", x = -106.6, y = 35.0975, label = "City of Albuquerque", size = 4.5) +
  annotate("text", x = -106.58, y = 35.33, label = "Rio Grande River", size = 5, angle = 55)
plot(map)
```

make plot of lots
```{r}
nm_fish_plot <- ggplot(data = lots, aes(x = year_collected, y = ci)) +
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 35.2102673,
           fill = "darkgrey", colour = NA, alpha = 0.5) + 
  annotate(geom = "rect", xmin = 1952.75, xmax = 1956.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
  annotate(geom = "rect", xmin = 1937.25, xmax = 1938.25, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
   annotate(geom = "rect", xmin = 1941.25, xmax = 1942.25, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
  geom_point(data = lots, 
             aes(x = jitter(year_collected, factor = 40), y = jitter(latitude, factor = 40), fill = scientific_name, size= number_requested), shape = 21,
             show.legend = FALSE) +
  scale_fill_manual(limits=c("Hybognathus amarus","Pimephales promelas","Gambusia affinis"), labels = c("HA", "PP", "GA"), values = c("#3B9AB2", "#E1AF00", "#F21A00"), name = "Host spp.") +
  scale_size_continuous(limits = c(1, 15), name = "Number of host individuals") +
  geom_hline(yintercept = 35.2102673, linetype = "dashed") + 
  geom_vline(xintercept = 1931, linetype = "dashed") + #collectionstart
  geom_vline(xintercept = 1972.5, linetype="dotted") + #CWA
  geom_vline(xintercept = 2010, linetype="dashed") + #collectionend
  geom_vline(xintercept = 1964, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1974, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1974.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1990, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1993.25, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1993.45, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1993.65, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1993, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1994, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1995, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1996, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2000, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2000.25, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2000.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2000.75, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2001, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2001.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2002, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2002.25, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2002.75, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2003, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2003.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2004, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2005, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.1, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.2, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.3, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.4, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.6, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.7, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.8, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.9, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.15, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.25, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.35, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.45, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.55, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2008, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2008.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2009, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2009.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2010, linetype="dotdash", colour = "brown") + #wildfire
  xlab("Year collected") +
  ylab("Latitude") +
  ylim(34.82, 35.66) +
  xlim(1929, 2011) +
  theme_bw() +
 scale_linetype_manual(name = "Events", 
                        values = c("dashed" = "dashed", "dotted" = "dotted", "dotdash" = "dotdash"),
                        labels = c("Collection Start", "CWA", "Wildfire")) +
  guides(linetype = guide_legend(override.aes = list(colour = c("black", "black", "brown")))) 

#+
 # theme(legend.position = "top",legend.title = element_text(size = 20, face = "bold")) +
#  guides(fill = guide_legend(override.aes = list(size = 7))) +
#  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"), text = element_text(family = 'sans', size = 20),
 # axis.text.y = element_text(size = 14), axis.text.x = element_text(size = 14), legend.text = element_text(size = 18))
plot(nm_fish_plot)


panels_cd <- plot_grid(map, plot, align = "h", axis = "bt", rel_widths = c(1, 3))


nm_final_figure <- ggdraw(plot=NULL,xlim=c(0,20),ylim=c(0,10))+
  #draw_image(panel_a,x=0,y=10,width=10,height=10)+
  #draw_image(panel_b,x=10,y=10,width=10,height=10)+
  draw_plot(panels_cd,x=0,y=0,width=20,height=10)+
  draw_label("(a)",x=0.5,y=9.75,size=30)+
  draw_label("(b)",x=5.5,y=9.75,size=30)
plot(nm_final_figure)



## modifying for GRFP

custom_breaks_nm <- c(0, 20, 40, 60, 80, 100, 120, 140)
custom_breaks_nm_x <- c(1930, 1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010)

nm_fish_plot_grfp <- ggplot(data = lots, aes(x = year_collected)) + 
  annotate(geom = "rect", xmin = 1952.75, xmax = 1956.25, ymin = -Inf, ymax = Inf,
           fill = "pink", colour = NA, alpha = 0.75) + #drought
  annotate(geom = "rect", xmin = 1937.25, xmax = 1938.25, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
   annotate(geom = "rect", xmin = 1941.25, xmax = 1942.25, ymin = -Inf, ymax = Inf,
           fill = "lightblue", colour = NA, alpha = 0.75) + #flood
  geom_vline(xintercept = 1931, linetype = "dashed") + #collectionstart
  geom_vline(xintercept = 2010, linetype="dashed") + #collectionend
  geom_vline(xintercept = 1964, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1974, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1974.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1990, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1993.25, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1993.45, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1993.65, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1993, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1994, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1995, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 1996, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2000, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2000.25, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2000.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2000.75, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2001, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2001.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2002, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2002.25, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2002.75, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2003, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2003.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2004, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2005, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.1, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.2, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.3, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.4, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.6, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.7, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.8, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.9, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.15, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.25, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.35, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.45, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2006.55, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2008, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2008.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2009, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2009.5, linetype="dotdash", colour = "brown") + #wildfire
  geom_vline(xintercept = 2010, linetype="dotdash", colour = "brown") + #wildfire
  geom_histogram(data = lots, 
             aes(x = year_collected), bins = 25) +
  scale_y_continuous(expand = c(0,0), breaks = custom_breaks_nm, limits = c(0, 140)) + 
  xlab("") +
  ylab("") +
     xlim(1929, 2011) +
  scale_x_continuous(expand = c(0,0), limits = c(1929, 2015), breaks = custom_breaks_nm_x,) +
  theme_classic() + 
 scale_linetype_manual(name = "Events", 
                        values = c("dotdash" = "dotdash"),
                        labels = c("Wildfire")) +
  guides(linetype = guide_legend(override.aes = list(colour = c("brown")))) 

plot(nm_fish_plot_grfp)


```

```{r}

legend_grob <- grobTree(
  textGrob("Legend", x = 0.3, y = 0.9, gp = gpar(fontsize = 16, fontface = "bold")),
  segmentsGrob(x0 = 0.1, x1 = 0.2, y0 = 0.8, y1 = 0.8, gp = gpar(col = "grey", lwd = 3)),
  textGrob("No Clean Water Act", x = 0.3, y = 0.8, just = "left", gp = gpar(fontsize = 14)),
  segmentsGrob(x0 = 0.1, x1 = 0.2, y0 = 0.7, y1 = 0.7, gp = gpar(col = "pink", lwd = 3)),
  textGrob("Drought", x = 0.3, y = 0.7, just = "left", gp = gpar(fontsize = 14)),
  segmentsGrob(x0 = 0.1, x1 = 0.2, y0 = 0.6, y1 = 0.6, gp = gpar(col = "lightblue", lwd = 3)),
  textGrob("Flood", x = 0.3, y = 0.6, just = "left", gp = gpar(fontsize = 14)),
  segmentsGrob(x0 = 0.1, x1 = 0.2, y0 = 0.5, y1 = 0.5, gp = gpar(col = "orange", lwd = 3, lty = "dotdash")),
  textGrob("Hurricane", x = 0.3, y = 0.5, just = "left", gp = gpar(fontsize = 14)),
  segmentsGrob(x0 = 0.1, x1 = 0.2, y0 = 0.4, y1 = 0.4, gp = gpar(col = "brown", lwd = 3, lty = "dotdash")),
  textGrob("Wildfire", x = 0.3, y = 0.4, just = "left", gp = gpar(fontsize = 14)),
  segmentsGrob(x0 = 0.1, x1 = 0.2, y0 = 0.3, y1 = 0.3, gp = gpar(col = "darkgrey", lwd = 3)),
  textGrob("South of Urbanization", x = 0.3, y = 0.3, just = "left", gp = gpar(fontsize = 14)),
  segmentsGrob(x0 = 0.1, x1 = 0.2, y0 = 0.2, y1 = 0.2, gp = gpar(col = "black", lwd = 3, lty = "dotted")),
  textGrob("Collection Start/End", x = 0.3, y = 0.2, just = "left", gp = gpar(fontsize = 14))
)


bordered_legend <- grobTree(
  rectGrob(x = 0.5, y = 0.5, width = 0.9, height = 0.9, 
           gp = gpar(col = "black", fill = NA, lwd = 2)), 
  legend_grob 
)


final_figure <- ggdraw(plot = NULL, xlim = c(0, 6), ylim = c(0, 10)) + 
  draw_plot(la_fish_plot + theme(legend.position = "none"), x = 0, y = 5, width = 5, height = 5) +
  draw_plot(nm_fish_plot + theme(legend.position = "none"), x = 0, y = 0, width = 5, height = 5) + 
  draw_label("(a)", x = 0.055, y = 9.75, size = 25) +
  draw_label("(b)", x = 0.1, y = 4.75, size = 25) +
  draw_grob(bordered_legend, x = 5, y = 4, width = 1, height = 2.5)


plot(final_figure)

#### grfp
final_figure_grfp <- ggdraw(plot = NULL, xlim = c(0, 2 ), ylim = c(0, 1)) + 
  draw_plot(la_fish_plot_grfp) +
  draw_plot(nm_fish_plot_grfp) + 
  draw_label("(a)", x = 0.055, y = 9.75, size = 25) +
  draw_label("(b)", x = 0.1, y = 4.75, size = 25)

plot(final_figure_grfp)

grfp_final <- ggarrange(la_fish_plot_grfp, nm_fish_plot_grfp, common.legend = TRUE, legend = "bottom", labels = c("A", "B"))

grfp_final <- annotate_figure(grfp_final,
                                  left = text_grob("Number of Fish", rot = 90, vjust = 1, size = 14),
                                  bottom = text_grob("Year Collected", vjust = -0.5, size = 14))
plot(grfp_final)

```
assign category to parasites themselves
```{r}
full <- read_csv("~/Desktop/UW/TUBRI/data/processed/Full_dataset_with_psite_life_history_info_2024.08.16.csv") %>%
  janitor::clean_names()
```


```{r}
# List of hurricane years
hurricane_years <- c(1964, 1965, 1969, 1971, 1974, 1979, 
                     1985.1, 1985.4, 1985.6, 1988.1, 1988.6, 
                     1992, 1995, 1996, 1997, 1998.1, 1998.6, 
                     2002.1, 2002.6, 2004)
drought_years <- c(1975, 1976, 1977, 1980, 1981, 1984, 1985, 1986, 1999, 2000, 2001)
flood_years <- c(1965, 1966, 1995, 1996, 1972, 1973, 1974, 1999, 2000, 2001)


# Add a column to mark hurricane events
full <- full %>%
  mutate(event = case_when(
    year_collected %in% hurricane_years & year_collected %in% drought_years ~ "Hurricane + Drought",
    year_collected %in% hurricane_years & year_collected %in% flood_years ~ "Hurricane + Flood",
    year_collected %in% hurricane_years ~ "Hurricane",
    year_collected %in% drought_years ~ "Drought",
    year_collected %in% flood_years ~ "Flood",
    TRUE ~ "No Event"
  )) %>%
  mutate(category = case_when(
    ci == "impact" & event == "Hurricane + Drought" ~ "Hurricane + Drought + Impact",
    ci == "control" & event == "Hurricane + Drought" ~ "Hurricane + Drought + Control",
    ci == "impact" & event == "Hurricane + Flood" ~ "Hurricane + Flood + Impact",
    ci == "control" & event == "Hurricane + Flood" ~ "Hurricane + Flood + Control",
    ci == "impact" & event == "Hurricane" ~ "Hurricane + Impact",
    ci == "control" & event == "Hurricane" ~ "Hurricane + Control",
    ci == "impact" & event == "Drought" ~ "Drought + Impact",
    ci == "control" & event == "Drought" ~ "Drought + Control",
    ci == "impact" & event == "Flood" ~ "Flood + Impact",
    ci == "control" & event == "Flood" ~ "Flood + Control",
    ci == "impact" & event == "No Event" ~ "No Event + Impact",
    ci == "control" & event == "No Event" ~ "No Event + Control"
  ))

# Prepare data for table plotting
table_data <- full %>%
  group_by(event, category) %>%
  summarize(count = n(), .groups = 'drop')

# Print the table
print(table_data)


#Hurricane + Control	4475			
#Hurricane + Impact	5438			
#No Hurricane + Control	7415			
#No Hurricane + Impact	13850


```









