---
title: "CAREER Project"
author: "Connor Whalen"
date: "2024-07-12"
output:
  html_document:
    theme: readable
    highlight: textmate
    toc: true
    toc_float: true
    toc_depth: 3
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```
## Questions


### Defining Extreme Weather Events
- flood ##
- drought ##
- hurricanes ##
- tornadoes
- wildfire ##
- heatwaves
- cold snaps
- thunderstorms 
- blizzards 
- ice storms
- hail storms
- dust storms 
- landslides
- mudslides
- deposits from volcanic eruptions




## Methods

#### Install packages.
```{r package install, eval=FALSE, echo=FALSE}
install.packages("tidyverse")
install.packages("janitor")
install.packages("ggeffects")
install.packages("ggpubr")
install.packages("glmmTMB")
install.packages("devtools")
devtools::install_github("johannesbjork/LaCroixColoR")
install.packages("patchwork")
install.packages("ggh4x")
install.packages("vistime")
install.packages("DHARMa")
```


#### Load packages.
```{r package load, echo=FALSE}
library(ggpubr)
library(ggeffects)
library(tidyverse)
library(readr)
library(dbplyr)
library(lubridate)
library(ggplot2)
library(stringr)
library(glmmTMB)
#library(lmerTest)
library(lme4)
source("~/Desktop/UW/Dissertation/theme_ctmt.R")
library(LaCroixColoR)
library(patchwork)
library(ggh4x)
library(vistime)
library(car)
library(DHARMa)
```


#### Import dataset and assign dataframe 
Load full dataset
```{r datasets and dataframe loading, echo=FALSE}
full_data <- read.csv("~/Desktop/UW/TUBRI/data/processed/Full_dataset_physical_2024.09.25.csv") %>% 
  janitor::clean_names()

SPI_data <- read.csv("~/Desktop/UW/Chapter1 NOLA/datasets/SPI data - Sheet1.csv") %>% 
  janitor::clean_names()
```

Prep all data. 
```{r}
full_data <- full_data %>%
  mutate(psite_type = case_when(
    str_detect(fish_psite_combo, "ACAN") ~ "acanthocephalan",
    str_detect(fish_psite_combo, "ACANTH") ~ "acanthocephalan",
    str_detect(fish_psite_combo, "CEST") ~ "cestode",
    str_detect(fish_psite_combo, "CILI") ~ "ciliate",
    str_detect(fish_psite_combo, "COPE") ~ "copepod",
    str_detect(fish_psite_combo, "LEECH") ~ "leech",
    str_detect(fish_psite_combo, "META") ~ "trematode_metacercaria",
    str_detect(fish_psite_combo, "MONO") ~ "monogenean",
    str_detect(fish_psite_combo, "MYX") ~ "myxozoan",
    str_detect(fish_psite_combo, "MYXO") ~ "myxozoan",
    str_detect(fish_psite_combo, "NEM") ~ "nematode",
    str_detect(fish_psite_combo, "NMORPH") ~ "nematomorph",
    str_detect(fish_psite_combo, "TREM") ~ "trematode",
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(psite_abundance = case_when(
    str_detect(fish_psite_combo, "ACAN") ~ psite_count,
    str_detect(fish_psite_combo, "ACANTH") ~ psite_count,
    str_detect(fish_psite_combo, "CEST") ~ psite_count,
    str_detect(fish_psite_combo, "CILI") ~ psite_count,
    str_detect(fish_psite_combo, "COPE") ~ psite_count,
    str_detect(fish_psite_combo, "LEECH") ~ psite_count,
    str_detect(fish_psite_combo, "META") ~ psite_count,
    str_detect(fish_psite_combo, "MONO") ~ psite_count,
    str_detect(fish_psite_combo, "NEM") ~ psite_count,
    str_detect(fish_psite_combo, "NMORPH") ~ psite_count,
    str_detect(fish_psite_combo, "TREM") ~ psite_count,
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(psite_prevalence = case_when(
    str_detect(fish_psite_combo, "MYX") ~ 1,
    str_detect(fish_psite_combo, "MYXO") ~ 1,
    TRUE ~ 0
  ))

full_data <- full_data %>%
  mutate(date = as.Date(paste(year_collected, month_collected, day_collected, sep = "-"))) 

SPI_data <- SPI_data %>% 
  mutate(date = as.Date(date))

full_data <- full_data %>% 
  mutate(psite_prevalence = as.character(psite_prevalence))

full_data <- full_data %>% 
  left_join(SPI_data, by = "date")
```


### Add columns for extreme weather events to the full dataset
#### DROUGHT
Find dates of no flood or droughts
```{r}
# 1963, 1964, 1966, 1970, 1971, 1974, 1975, 1978, 1980, 1982, 1983, 1984, 1987, 1988, 1989, 1990, 1991, 1992, 1993, 1994, 1996
# 1997, 1998, 1999, 2001, 2002, 2003, 2004

# select years to represent as controls: alternate years to turn 28 non event years in 14 to match # of years in events - make sure no controls overlap with events (+ before and after)
# 1963, 1988, 1989, 1990, 1991, 1992, 1993, 1996
# 1997, 2002, 2003, 2004

```

Find average dates of flood and drought
```{r}
average_d <- drought_flood_df %>%
  filter(str_detect(ewe_type, "drought")) %>%
  mutate(
    month = month(date),
    day = day(date)
  ) %>%
  summarise(
    average_month = mean(month),
    average_day = mean(day)
  )

 # average drought occurs on 6/17 of each year

average_f <- drought_flood_df %>%
  filter(str_detect(ewe_type, "flood")) %>%
  mutate(
    month = month(date),
    day = day(date)
  ) %>%
  summarise(
    average_month = mean(month),
    average_day = mean(day)
  )

 # average flood occurs on 7/17 of each year

# find average duration of each event

# Define date ranges for events
drought_events <- data.frame(
  start_date = as.Date(c("1967-01-01", "1976-01-01", "1981-01-01", 
                         "1985-01-01", "2000-01-01")),
  end_date = as.Date(c("1969-01-01", "1978-01-01", "1982-01-01", 
                       "1987-01-01", "2001-01-01"))
)

flood_events <- data.frame(
  start_date = as.Date(c("1965-08-27", "1972-12-01", "1979-04-01", "1995-05-08")),
  end_date = as.Date(c("1965-09-12", "1973-06-01", "1979-05-01", "1995-05-10"))
)

# Calculate durations of each event
drought_events$duration <- as.numeric(drought_events$end_date - drought_events$start_date)
flood_events$duration <- as.numeric(flood_events$end_date - flood_events$start_date)

# Calculate the average duration
average_duration_d <- mean(drought_events$duration)
average_duration_f <- mean(flood_events$duration)

# Print result
average_duration_d
 # 584 days -- 1 year, 6 months

average_duration_f
 # 57 days -- 2 months, 27 days
```


-6 month buffer on either side of hurricane events
- generate datasets for each type of weather event
```{r}
# create drought/flood dataset
drought_flood_df <- full_data %>% 
  mutate(ewe_type = case_when(
    date >= as.Date("1966-06-01") & date <= as.Date("1966-12-31") ~ "pre_drought",
    date >= as.Date("1967-01-01") & date <= as.Date("1970-01-01") ~ "drought",
    date >= as.Date("1970-01-02") & date <= as.Date("1970-06-01") ~ "post_drought",
    date >= as.Date("1975-06-01") & date <= as.Date("1975-12-31") ~ "pre_drought",
    date >= as.Date("1976-01-01") & date <= as.Date("1978-01-01") ~ "drought",
    date >= as.Date("1978-01-02") & date <= as.Date("1978-06-01") ~ "post_drought",
    date >= as.Date("1980-06-01") & date <= as.Date("1980-12-31") ~ "pre_drought",
    date >= as.Date("1981-01-01") & date <= as.Date("1982-01-01") ~ "drought",
    date >= as.Date("1982-01-02") & date <= as.Date("1982-06-01") ~ "post_drought",
    date >= as.Date("1984-06-01") & date <= as.Date("1984-12-31") ~ "pre_drought",
    date >= as.Date("1985-01-01") & date <= as.Date("1987-01-01") ~ "drought",
    date >= as.Date("1987-01-02") & date <= as.Date("1987-06-01") ~ "post_drought",
    date >= as.Date("1999-06-01") & date <= as.Date("1999-12-31") ~ "pre_drought",
    date >= as.Date("2000-01-01") & date <= as.Date("2001-01-01") ~ "drought",
    date >= as.Date("2001-01-02") & date <= as.Date("2001-06-02") ~ "post_drought",
    date >= as.Date("1965-02-26") & date <= as.Date("1965-08-26") ~ "pre_flood",
    date >= as.Date("1965-08-27") & date <= as.Date("1965-09-12") ~ "flood",
    date >= as.Date("1965-09-13") & date <= as.Date("1966-03-13") ~ "post_flood",
    date >= as.Date("1972-05-01") & date <= as.Date("1972-11-30") ~ "pre_flood",
    date >= as.Date("1972-12-01") & date <= as.Date("1973-06-01") ~ "flood",
    date >= as.Date("1973-06-02") & date <= as.Date("1973-12-02") ~ "post_flood",
    date >= as.Date("1978-10-01") & date <= as.Date("1978-03-31") ~ "pre_flood",
    date >= as.Date("1979-04-01") & date <= as.Date("1979-05-01") ~ "flood",
    date >= as.Date("1979-05-02") & date <= as.Date("1979-11-02") ~ "post_flood",
    date >= as.Date("1994-11-07") & date <= as.Date("1995-05-07") ~ "pre_flood",
    date >= as.Date("1995-05-08") & date <= as.Date("1995-05-10") ~ "flood",
    date >= as.Date("1995-05-11") & date <= as.Date("1995-11-11") ~ "post_flood",
    TRUE ~ "no event"
  ))

# create controls for the same dataset -- non events
# only calculated using the drought timeframe, because it encompasses the flood timeframe in it
drought_flood_df <- drought_flood_df %>% 
  mutate(control = case_when(
    date >= as.Date("1963-01-15") & date <= as.Date("1963-06-16") ~ "pre_control",
    date >= as.Date("1963-06-17") & date <= as.Date("1963-12-17") ~ "control",
    date >= as.Date("1964-12-18") & date <= as.Date("1964-06-18") ~ "post_control",
    date >= as.Date("1988-01-15") & date <= as.Date("1988-06-16") ~ "pre_control",
    date >= as.Date("1988-06-17") & date <= as.Date("1988-12-17") ~ "control",
    date >= as.Date("1988-12-18") & date <= as.Date("1989-06-18") ~ "post_control",
    date >= as.Date("1989-01-15") & date <= as.Date("1989-06-16") ~ "pre_control",
    date >= as.Date("1989-06-17") & date <= as.Date("1989-12-17") ~ "control",
    date >= as.Date("1989-12-18") & date <= as.Date("1990-06-18") ~ "post_control",
    date >= as.Date("1990-01-15") & date <= as.Date("1990-06-16") ~ "pre_control",
    date >= as.Date("1990-06-17") & date <= as.Date("1990-12-17") ~ "control",
    date >= as.Date("1990-12-18") & date <= as.Date("1991-06-18") ~ "post_control",
    date >= as.Date("1991-01-15") & date <= as.Date("1991-06-16") ~ "pre_control",
    date >= as.Date("1991-06-17") & date <= as.Date("1991-12-17") ~ "control",
    date >= as.Date("1991-12-18") & date <= as.Date("1992-06-18") ~ "post_control",
    date >= as.Date("1992-01-15") & date <= as.Date("1992-06-16") ~ "pre_control",
    date >= as.Date("1992-06-17") & date <= as.Date("1992-12-17") ~ "control",
    date >= as.Date("1992-12-18") & date <= as.Date("1993-06-18") ~ "post_control",
    date >= as.Date("1993-01-15") & date <= as.Date("1993-06-16") ~ "pre_control",
    date >= as.Date("1993-06-17") & date <= as.Date("1993-12-17") ~ "control",
    date >= as.Date("1993-12-18") & date <= as.Date("1994-06-18") ~ "post_control",
    date >= as.Date("1996-01-15") & date <= as.Date("1996-06-16") ~ "pre_control",
    date >= as.Date("1996-06-17") & date <= as.Date("1996-12-17") ~ "control",
    date >= as.Date("1996-12-18") & date <= as.Date("1997-06-18") ~ "post_control",
    date >= as.Date("1997-01-15") & date <= as.Date("1997-06-16") ~ "pre_control",
    date >= as.Date("1997-06-17") & date <= as.Date("1997-12-17") ~ "control",
    date >= as.Date("1997-12-18") & date <= as.Date("1998-06-18") ~ "post_control",
    date >= as.Date("2002-01-15") & date <= as.Date("2002-06-16") ~ "pre_control",
    date >= as.Date("2002-06-17") & date <= as.Date("2002-12-17") ~ "control",
    date >= as.Date("2002-12-18") & date <= as.Date("2003-06-18") ~ "post_control",
    date >= as.Date("2003-01-15") & date <= as.Date("2003-06-16") ~ "pre_control",
    date >= as.Date("2003-06-17") & date <= as.Date("2003-12-17") ~ "control",
    date >= as.Date("2003-12-18") & date <= as.Date("2004-06-18") ~ "post_control",
    date >= as.Date("2004-01-15") & date <= as.Date("2004-06-16") ~ "pre_control",
    date >= as.Date("2004-06-17") & date <= as.Date("2004-12-17") ~ "control",
    date >= as.Date("2004-12-18") & date <= as.Date("2005-06-18") ~ "post_control",
    TRUE ~ "no event"
  ))

drought_flood_df <- drought_flood_df %>% 
  mutate(event = case_when(
    ewe_type == "drought" ~ "drought",
    ewe_type == "flood" ~ "flood",
    ewe_type == "pre_drought" ~ "drought",
    ewe_type == "pre_flood" ~ "flood",
    ewe_type == "post_drought" ~ "drought",
    ewe_type == "post_flood" ~ "flood",
    ewe_type == "no event" & control == "pre_control" ~ "control",
    ewe_type == "no event" & control == "post_control" ~ "control",
    ewe_type == "no event" & control == "control" ~ "control",
    TRUE ~ "NA"
  )) %>%
  filter(!str_detect(event, "NA")) 

drought_flood_df <- drought_flood_df %>% 
  mutate(timing = case_when(
    ewe_type == "pre_drought" ~ "pre",
    ewe_type == "post_drought" ~ "post",    
    ewe_type == "pre_flood" ~ "pre",
    ewe_type == "post_flood" ~ "post",
    control == "pre_control" ~ "pre",
    control == "post_control" ~ "post",
    ewe_type == "drought" & event == "drought" ~ "drought",
    ewe_type == "flood" & event == "flood" ~ "flood",
    control == "control" & event == "control" ~ "control",
    TRUE ~ "NA"
  )) %>%
  filter(!str_detect(timing, "NA")) 

drought_flood_df <- drought_flood_df %>%
  mutate(timing = factor(timing, levels = c("pre", "post"))) %>%
  mutate(timing = relevel(timing, ref = "pre"))

df_table <- table(drought_flood_df$timing)
df_table <- table(drought_flood_df$event)
# view(df_table)

```

Does mean streamflow corrrelate to drought and flood events?
- find average streamflow for years with drought/flood and for years without --> is there significant difference between the two?
- plot mean streamflow against time to see if there are spikes/dips in streamflow at drought/flood (or hurricane), or not
```{r}
# isolate each type 
drought_df <- drought_flood_df %>%
  filter(ewe_type == "drought")

flood_df <- drought_flood_df %>%
  filter(ewe_type == "flood")

df_control_df <- drought_flood_df %>%
  filter(ewe_type == "a_no event")

# find average streamflow for drought, flood, and non-event years
avg_stream_drought <- sum(drought_df$mean_streamflow, na.rm = TRUE ) / 2315
 # 234.387345106971

num_NAs <- sum(is.na(flood_df$mean_streamflow)) # 1640
avg_stream_flood <- sum(flood_df$mean_streamflow, na.rm = TRUE) / 2418
 # 167.276084130924
  
num_NAs <- sum(is.na(df_control_df$mean_streamflow)) # 8794
avg_stream_dfcontrol <- sum(df_control_df$mean_streamflow, na.rm = TRUE) / 15891
 # 212.373462064365

# plot individual streamflows next to each other for each dataset
a <- ggplot(data = drought_df, 
       aes(x = collection_date, y = mean_streamflow)) + 
  geom_point() + xlab("Collection Date") + ylab("Mean Streamflow") +
   theme(strip.background = element_rect(fill = NA, color = NA),
         panel.background = element_rect(fill = NA, color = NA),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.spacing.x = unit(0, "lines"),
         panel.spacing.y = unit(0, "lines"))

b <- ggplot(data = flood_df, 
       aes(x = collection_date, y = mean_streamflow)) + 
  geom_point() + xlab("Collection Date") + ylab("Mean Streamflow") +
   theme(strip.background = element_rect(fill = NA, color = NA),
         panel.background = element_rect(fill = NA, color = NA),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.spacing.x = unit(0, "lines"),
         panel.spacing.y = unit(0, "lines"))

c <- ggplot(data = df_control_df, 
       aes(x = collection_date, y = mean_streamflow)) + 
  geom_point() + xlab("Collection Date") + ylab("Mean Streamflow") +
   theme(strip.background = element_rect(fill = NA, color = NA),
         panel.background = element_rect(fill = NA, color = NA),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.spacing.x = unit(0, "lines"),
         panel.spacing.y = unit(0, "lines"))

abc <- ggarrange(a, b, c, common.legend = TRUE, legend = "bottom", labels = c("A", "B"))

print(abc)

# plot average streamflows next to each other

ggplot(data = drought_flood_df, 
       aes(x = year_collected, y = mean_streamflow)) +
  facet_wrap(~ewe_type) +
  geom_point() + xlab("Collection Date") + ylab("Mean Streamflow") +
   theme(strip.background = element_rect(fill = NA, color = NA),
         panel.background = element_rect(fill = NA, color = NA),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.spacing.x = unit(0, "lines"),
         panel.spacing.y = unit(0, "lines"))


```

Break drought and flood into their own dataset? drought vs control and flood vs control? 
randomly pull identical number of datapoints to use as control to drought and flood 
```{r}
ddf <- drought_flood_df %>%
  filter(ewe_type != "flood")

fdf <- drought_flood_df %>%
  filter(ewe_type != "drought")
```


#### HURRICANE

Pick out years where there was no hurricane:
```{r}
# 1963, 1966, 1967, 1968, 1970, 1972, 1973, 
# 1975, 1976, 1977, 1978, 1980, 1981, 1982,
# 1983, 1984, 1986, 1987, 1989,
# 1990, 1991, 1993, 1994, 1999, 2000, 2003
```

Add actual hurricane timeline parameters for 6 month
```{r}
hurricane_df6 <- full_data %>%
  mutate(ewe_type = case_when(
    date >= as.Date("1969-02-14") & date <= as.Date("1969-08-14") ~ "pre_5",
    date >= as.Date("1969-08-14") & date <= as.Date("1969-08-22") ~ "hurricane_5", #camille
    date >= as.Date("1969-08-22") & date <= as.Date("1970-02-22") ~ "post_5",
    date >= as.Date("1971-03-05") & date <= as.Date("1971-09-05") ~ "pre_5",
    date >= as.Date("1971-09-05") & date <= as.Date("1971-09-15") ~ "hurricane_5", #edith
    date >= as.Date("1971-09-15") & date <= as.Date("1972-03-15") ~ "post_5",
    date >= as.Date("1992-02-16") & date <= as.Date("1992-08-16") ~ "pre_5",
    date >= as.Date("1992-08-16") & date <= as.Date("1992-08-19") ~ "hurricane_5", #andrew
    date >= as.Date("1992-08-19") & date <= as.Date("1993-03-19") ~ "post_5",
    date >= as.Date("2004-03-02") & date <= as.Date("2004-09-02") ~ "pre_5",
    date >= as.Date("2004-09-02") & date <= as.Date("2004-09-25") ~ "hurricane_5", #ivan -- external
    date >= as.Date("2004-09-25") & date <= as.Date("2005-03-25") ~ "post_5",
    date >= as.Date("1964-03-28") & date <= as.Date("1964-09-28") ~ "pre_4",
    date >= as.Date("1964-09-28") & date <= as.Date("1964-10-05") ~ "hurricane_4", #hilda
    date >= as.Date("1964-10-05") & date <= as.Date("1965-04-05") ~ "post_4",
    date >= as.Date("1965-02-27") & date <= as.Date("1965-08-27") ~ "pre_4",
    date >= as.Date("1965-08-27") & date <= as.Date("1965-09-13") ~ "hurricane_4", #betsy
    date >= as.Date("1965-09-13") & date <= as.Date("1966-03-13") ~ "post_4",
    date >= as.Date("1974-02-28") & date <= as.Date("1974-08-29") ~ "pre_4",
    date >= as.Date("1974-08-29") & date <= as.Date("1974-09-10") ~ "hurricane_4", #carmen -- external
    date >= as.Date("1974-09-10") & date <= as.Date("1975-03-10") ~ "post_4",
    date >= as.Date("1998-03-15") & date <= as.Date("1998-09-15") ~ "pre_4",
    date >= as.Date("1998-09-15") & date <= as.Date("1998-10-01") ~ "hurricane_4", #georges
    date >= as.Date("1998-10-01") & date <= as.Date("1999-04-01") ~ "post_4",
    date >= as.Date("2002-03-21") & date <= as.Date("2002-09-21") ~ "pre_4",
    date >= as.Date("2002-09-21") & date <= as.Date("2002-10-04") ~ "hurricane_4", #lili -- external 
    date >= as.Date("2002-10-04") & date <= as.Date("2003-04-04") ~ "post_4",
    date >= as.Date("1985-02-28") & date <= as.Date("1985-08-28") ~ "pre_3",
    date >= as.Date("1985-08-28") & date <= as.Date("1985-09-04") ~ "hurricane_3", #elena
    date >= as.Date("1985-09-04") & date <= as.Date("1986-03-04") ~ "post_3",
    date >= as.Date("2002-03-14") & date <= as.Date("2002-09-14") ~ "pre_3",
    date >= as.Date("2002-09-14") & date <= as.Date("2002-09-27") ~ "hurricane_3", #isidore 
    date >= as.Date("2002-09-27") & date <= as.Date("2003-03-27") ~ "post_3",
    date >= as.Date("1979-01-09") & date <= as.Date("1979-07-09") ~ "pre_1",
    date >= as.Date("1979-07-09") & date <= as.Date("1979-07-16") ~ "hurricane_1", #bob
    date >= as.Date("1979-07-16") & date <= as.Date("1980-01-16") ~ "post_1",
    date >= as.Date("1985-02-12") & date <= as.Date("1985-08-12") ~ "pre_1",
    date >= as.Date("1985-08-12") & date <= as.Date("1985-08-20") ~ "hurricane_1", #danny -- external
    date >= as.Date("1985-08-20") & date <= as.Date("1986-02-20") ~ "post_1",
    date >= as.Date("1985-04-26") & date <= as.Date("1985-10-26") ~ "pre_1",
    date >= as.Date("1985-10-26") & date <= as.Date("1985-11-03") ~ "hurricane_1", #juan
    date >= as.Date("1985-11-03") & date <= as.Date("1986-05-03") ~ "post_1",
    date >= as.Date("1988-03-07") & date <= as.Date("1988-09-07") ~ "pre_1",
    date >= as.Date("1988-09-07") & date <= as.Date("1988-09-11") ~ "hurricane_1", #florence
    date >= as.Date("1988-09-11") & date <= as.Date("1989-03-11") ~ "post_1",
    date >= as.Date("1997-01-16") & date <= as.Date("1997-07-16") ~ "pre_1",
    date >= as.Date("1997-07-16") & date <= as.Date("1997-07-27") ~ "hurricane_1", #danny
    date >= as.Date("1997-07-27") & date <= as.Date("1998-01-27") ~ "post_1",
    date >= as.Date("1988-02-07") & date <= as.Date("1988-08-07") ~ "pre_ts",
    date >= as.Date("1988-08-08") & date <= as.Date("1988-08-10") ~ "tropical_storm", #beryl
    date >= as.Date("1988-08-11") & date <= as.Date("1989-02-11") ~ "post_ts",
    date >= as.Date("1998-03-26") & date <= as.Date("1998-09-26") ~ "pre_ts",
    date >= as.Date("1998-09-27") & date <= as.Date("1998-09-30") ~ "tropical_storm", #hermine
    date >= as.Date("1998-10-01") & date <= as.Date("1999-04-01") ~ "post_ts",
    date >= as.Date("2000-12-05") & date <= as.Date("2001-06-05") ~ "pre_ts",
    date >= as.Date("2001-06-05") & date <= as.Date("2001-06-20") ~ "tropical_storm", #allison
    date >= as.Date("2001-06-20") & date <= as.Date("2001-12-20") ~ "post_ts",
    date >= as.Date("2002-02-04") & date <= as.Date("2002-08-04") ~ "pre_ts",
    date >= as.Date("2002-08-04") & date <= as.Date("2002-08-09") ~ "tropical_storm", #bertha
    date >= as.Date("2002-08-09") & date <= as.Date("2003-02-09") ~ "post_ts",
    date >= as.Date("2002-03-12") & date <= as.Date("2002-09-12") ~ "pre_ts",
    date >= as.Date("2002-09-12") & date <= as.Date("2002-09-15") ~ "tropical_storm", #hanna
    date >= as.Date("2002-09-15") & date <= as.Date("2003-03-15") ~ "post_ts",
    date >= as.Date("2002-12-27") & date <= as.Date("2003-06-27") ~ "pre_ts",
    date >= as.Date("2003-06-28") & date <= as.Date("2003-07-03") ~ "tropical_storm", #bill
    date >= as.Date("2003-07-04") & date <= as.Date("2004-01-04") ~ "post_ts",
    date >= as.Date("1965-03-23") & date <= as.Date("1965-09-23") ~ "pre_ts",
    date >= as.Date("1965-09-24") & date <= as.Date("1965-09-30") ~ "tropical_storm", #debbie
    date >= as.Date("1965-10-01") & date <= as.Date("1966-04-01") ~ "post_ts",
    date >= as.Date("1995-01-30") & date <= as.Date("1995-07-30") ~ "pre_double",
    date >= as.Date("1995-07-31") & date <= as.Date("1995-10-06") ~ "hurricane_double", #opal (4) and erin (2) combined
    date >= as.Date("1995-10-07") & date <= as.Date("1996-04-07") ~ "post_double",
    TRUE ~ "no event"
  ))


# make a new column for storm intensity

hurricane_df6 <- hurricane_df6 %>%
  mutate(storm_intensity = case_when(
    str_detect(ewe_type, "1") ~ "one",
    str_detect(ewe_type, "2") ~ "two",
    str_detect(ewe_type, "3") ~ "three",
    str_detect(ewe_type, "4") ~ "four",
    str_detect(ewe_type, "5") ~ "five",
    str_detect(ewe_type, "ts") ~ "ts",
    str_detect(ewe_type, "double") ~ "double",
    TRUE ~ "no event"
  ))


# create hurricane control categories just like with the other dataset by assigning non-event years to have a pre and post category -- 6 months

hurricane_df6 <- hurricane_df6 %>%
  mutate(control = case_when(
    date >= as.Date("1963-03-18") & date <= as.Date("1963-09-18") ~ "pre_control",
    date >= as.Date("1963-09-18") & date <= as.Date("1963-09-28") ~ "control",
    date >= as.Date("1963-09-28") & date <= as.Date("1964-03-28") ~ "post_control",
    date >= as.Date("1966-03-18") & date <= as.Date("1966-09-18") ~ "pre_control",
    date >= as.Date("1966-09-18") & date <= as.Date("1966-09-28") ~ "control",
    date >= as.Date("1966-09-28") & date <= as.Date("1967-03-28") ~ "post_control",
    date >= as.Date("1967-03-18") & date <= as.Date("1967-09-18") ~ "pre_control",
    date >= as.Date("1967-09-18") & date <= as.Date("1967-09-28") ~ "control",
    date >= as.Date("1967-09-28") & date <= as.Date("1968-03-28") ~ "post_control",
    date >= as.Date("1968-03-18") & date <= as.Date("1968-09-18") ~ "pre_control",
    date >= as.Date("1968-09-18") & date <= as.Date("1968-09-28") ~ "control",
    date >= as.Date("1968-09-28") & date <= as.Date("1969-03-28") ~ "post_control",
    date >= as.Date("1970-03-18") & date <= as.Date("1970-09-18") ~ "pre_control",
    date >= as.Date("1970-09-18") & date <= as.Date("1970-09-28") ~ "control",
    date >= as.Date("1970-09-28") & date <= as.Date("1971-03-28") ~ "post_control",
    date >= as.Date("1972-03-18") & date <= as.Date("1972-09-18") ~ "pre_control",
    date >= as.Date("1972-09-18") & date <= as.Date("1972-09-28") ~ "control",
    date >= as.Date("1972-09-28") & date <= as.Date("1973-03-28") ~ "post_control",
    date >= as.Date("1973-03-18") & date <= as.Date("1973-09-18") ~ "pre_control",
    date >= as.Date("1973-09-18") & date <= as.Date("1973-09-28") ~ "control",
    date >= as.Date("1973-09-28") & date <= as.Date("1974-03-28") ~ "post_control",
    date >= as.Date("1975-03-18") & date <= as.Date("1975-09-18") ~ "pre_control",
    date >= as.Date("1975-09-18") & date <= as.Date("1975-09-28") ~ "control",
    date >= as.Date("1975-09-28") & date <= as.Date("1976-03-28") ~ "post_control",
    date >= as.Date("1976-03-18") & date <= as.Date("1976-09-18") ~ "pre_control",
    date >= as.Date("1976-09-18") & date <= as.Date("1976-09-28") ~ "control",
    date >= as.Date("1976-09-28") & date <= as.Date("1977-03-28") ~ "post_control",
    date >= as.Date("1977-03-18") & date <= as.Date("1977-09-18") ~ "pre_control",
    date >= as.Date("1977-09-18") & date <= as.Date("1977-09-28") ~ "control",
    date >= as.Date("1977-09-28") & date <= as.Date("1978-03-28") ~ "post_control",
    date >= as.Date("1978-03-18") & date <= as.Date("1978-09-18") ~ "pre_control",
    date >= as.Date("1978-09-18") & date <= as.Date("1978-09-28") ~ "control",
    date >= as.Date("1978-09-28") & date <= as.Date("1979-03-28") ~ "post_control",
    date >= as.Date("1980-03-18") & date <= as.Date("1980-09-18") ~ "pre_control",
    date >= as.Date("1980-09-18") & date <= as.Date("1980-09-28") ~ "control",
    date >= as.Date("1980-09-28") & date <= as.Date("1981-03-28") ~ "post_control",
    date >= as.Date("1981-03-18") & date <= as.Date("1981-09-18") ~ "pre_control",
    date >= as.Date("1981-09-18") & date <= as.Date("1981-09-28") ~ "control",
    date >= as.Date("1981-09-28") & date <= as.Date("1982-03-28") ~ "post_control",
    date >= as.Date("1982-03-18") & date <= as.Date("1982-09-18") ~ "pre_control",
    date >= as.Date("1982-09-18") & date <= as.Date("1982-09-28") ~ "control",
    date >= as.Date("1982-09-28") & date <= as.Date("1983-03-28") ~ "post_control",
    date >= as.Date("1983-03-18") & date <= as.Date("1983-09-18") ~ "pre_control",
    date >= as.Date("1983-09-18") & date <= as.Date("1983-09-28") ~ "control",
    date >= as.Date("1983-09-28") & date <= as.Date("1984-03-28") ~ "post_control",
    date >= as.Date("1987-03-18") & date <= as.Date("1987-09-18") ~ "pre_control",
    date >= as.Date("1987-09-18") & date <= as.Date("1987-09-28") ~ "control",
    date >= as.Date("1987-09-28") & date <= as.Date("1988-03-28") ~ "post_control",
    date >= as.Date("1989-03-18") & date <= as.Date("1989-09-18") ~ "pre_control",
    date >= as.Date("1989-09-18") & date <= as.Date("1989-09-28") ~ "control",
    date >= as.Date("1989-09-28") & date <= as.Date("1990-03-28") ~ "post_control",
    date >= as.Date("1990-03-18") & date <= as.Date("1990-09-18") ~ "pre_control",
    date >= as.Date("1990-09-18") & date <= as.Date("1990-09-28") ~ "control",
    date >= as.Date("1990-09-28") & date <= as.Date("1991-03-28") ~ "post_control",
    date >= as.Date("1991-03-18") & date <= as.Date("1991-09-18") ~ "pre_control",
    date >= as.Date("1991-09-18") & date <= as.Date("1991-09-28") ~ "control",
    date >= as.Date("1991-09-28") & date <= as.Date("1992-03-28") ~ "post_control",
    date >= as.Date("1999-03-18") & date <= as.Date("1999-09-18") ~ "pre_control",
    date >= as.Date("1999-09-18") & date <= as.Date("1999-09-28") ~ "control",
    date >= as.Date("1999-09-28") & date <= as.Date("2000-03-28") ~ "post_control",
    date >= as.Date("2000-03-18") & date <= as.Date("2000-09-18") ~ "pre_control",
    date >= as.Date("2000-09-18") & date <= as.Date("2000-09-28") ~ "control",
    date >= as.Date("2000-09-28") & date <= as.Date("2001-03-28") ~ "post_control",
    date >= as.Date("2003-03-18") & date <= as.Date("2003-09-18") ~ "pre_control",
    date >= as.Date("2003-09-18") & date <= as.Date("2003-09-28") ~ "control",
    date >= as.Date("2003-09-28") & date <= as.Date("2004-03-28") ~ "post_control",
    TRUE ~ "no event"
  ))

hurricane_df6 <- hurricane_df6 %>%
  mutate(event = case_when(
    ewe_type == "pre_5" ~ "hurricane",
    ewe_type == "post_5" ~ "hurricane",
    ewe_type == "pre_4" ~ "hurricane",
    ewe_type == "post_4" ~ "hurricane",
    ewe_type == "pre_3" ~ "hurricane",
    ewe_type == "post_3" ~ "hurricane",
    ewe_type == "pre_2" ~ "hurricane",
    ewe_type == "post_2" ~ "hurricane",
    ewe_type == "pre_1" ~ "hurricane",
    ewe_type == "post_1" ~ "hurricane",
    ewe_type == "pre_ts" ~ "hurricane",
    ewe_type == "post_ts" ~ "hurricane",
    ewe_type == "pre_double" ~ "hurricane",
    ewe_type == "post_double" ~ "hurricane",
    ewe_type == "no event" & control == "pre_control" ~ "control",
    ewe_type == "no event" & control == "post_control" ~ "control",
    TRUE ~ "NA"
  )) %>%
  filter(event != "NA")

hurricane_df6 <- hurricane_df6 %>%
  mutate(timing = case_when(
    ewe_type == "pre_5" ~ "pre",
    ewe_type == "post_5" ~ "post",
    ewe_type == "pre_4" ~ "pre",
    ewe_type == "post_4" ~ "post",
    ewe_type == "pre_3" ~ "pre",
    ewe_type == "post_3" ~ "post",
    ewe_type == "pre_2" ~ "pre",
    ewe_type == "post_2" ~ "post",
    ewe_type == "pre_1" ~ "pre",
    ewe_type == "post_1" ~ "post",
    ewe_type == "pre_ts" ~ "pre",
    ewe_type == "post_ts" ~ "post",
    ewe_type == "pre_double" ~ "pre",
    ewe_type == "post_double" ~ "post",
    control == "pre_control" ~ "pre",
    control == "post_control" ~ "post",
    ewe_type == "hurricane_4" ~ "during",
    TRUE ~ "NA"
  )) %>%
  filter(timing != "NA")


hurricane_df6 <- hurricane_df6 %>%
  mutate(timing = factor(timing, levels = c("pre", "post"))) %>%
  mutate(timing = relevel(timing, ref = "pre")) #%>% 
 # mutate(event = factor(event, levels = c("hurricane", "control"))) %>%
 # mutate(event = relevel(event, ref = "control"))

ewe_table6 <- table(hurricane_df6$event)
# view(ewe_table6)
ewe_table6_2 <- table(hurricane_df6$timing)
# view(ewe_table6_2)
```

find the average date of a hurricane:
```{r}
average_hurr <- hurricane_df6 %>%
  filter(str_detect(ewe_type, "hurricane")) %>%
  mutate(
    month = month(date),
    day = day(date)
  ) %>%
  summarise(
    average_month = mean(month),
    average_day = mean(day)
  )

# average hurricane happens on 9/18 each year

# find average duration of hurricane event

# Define date ranges for hurricane events
hurricane_events <- data.frame(
  start_date = as.Date(c("1969-08-14", "1971-09-05", "1988-09-08", 
                         "1992-08-16", "2004-09-02", "1964-09-28", 
                         "1965-08-27", "1974-08-29", "1995-09-27", 
                         "1998-09-15", "2002-09-21", "1985-08-28", 
                         "2004-09-14", "1979-07-09", "1985-08-12", 
                         "1985-10-26", "1988-09-07", "1997-07-16")),
  end_date = as.Date(c("1969-08-22", "1971-09-15", "1988-09-19", 
                       "1992-08-19", "2004-09-25", "1964-10-05", 
                       "1965-09-13", "1974-09-10", "1995-10-06", 
                       "1998-10-01", "2002-10-04", "1985-09-04", 
                       "2004-09-27", "1979-07-16", "1985-08-20", 
                       "1985-11-03", "1988-09-11", "1997-07-27"))
)

# Calculate durations of each hurricane event
hurricane_events$duration <- as.numeric(hurricane_events$end_date - hurricane_events$start_date)

# Calculate the average duration
average_duration <- mean(hurricane_events$duration)

# Print result
average_duration

# average is 10 days

```

##### 3 month -- needs to be updated to match new storms and dates
Further refine hurricane parameters for 3 months buffer
```{r}
hurricane_df3 <- full_data %>%
  mutate(ewe_type = case_when(
    date >= as.Date("1969-05-14") & date <= as.Date("1969-08-14") ~ "pre_5",
    date >= as.Date("1969-08-14") & date <= as.Date("1969-08-22") ~ "hurricane_5",
    date >= as.Date("1969-08-22") & date <= as.Date("1969-11-22") ~ "post_5",
    date >= as.Date("1971-06-05") & date <= as.Date("1971-09-05") ~ "pre_5",
    date >= as.Date("1971-09-05") & date <= as.Date("1971-09-15") ~ "hurricane_5",
    date >= as.Date("1971-09-15") & date <= as.Date("1971-12-15") ~ "post_5",
    date >= as.Date("1988-06-08") & date <= as.Date("1988-09-08") ~ "pre_5",
    date >= as.Date("1988-09-08") & date <= as.Date("1988-09-19") ~ "hurricane_5",
    date >= as.Date("1988-09-19") & date <= as.Date("1988-12-19") ~ "post_5",
    date >= as.Date("1992-05-16") & date <= as.Date("1992-08-16") ~ "pre_5",
    date >= as.Date("1992-08-16") & date <= as.Date("1992-08-19") ~ "hurricane_5",
    date >= as.Date("1992-08-19") & date <= as.Date("1992-11-19") ~ "post_5",
    date >= as.Date("2004-06-02") & date <= as.Date("2004-09-02") ~ "pre_5",
    date >= as.Date("2004-09-02") & date <= as.Date("2004-09-25") ~ "hurricane_5",
    date >= as.Date("2004-09-25") & date <= as.Date("2004-12-25") ~ "post_5",
    date >= as.Date("1964-06-28") & date <= as.Date("1964-09-28") ~ "pre_4",
    date >= as.Date("1964-09-28") & date <= as.Date("1964-10-05") ~ "hurricane_4",
    date >= as.Date("1964-10-05") & date <= as.Date("1965-01-05") ~ "post_4",
    date >= as.Date("1965-05-27") & date <= as.Date("1965-08-27") ~ "pre_4",
    date >= as.Date("1965-08-27") & date <= as.Date("1965-09-13") ~ "hurricane_4",
    date >= as.Date("1965-09-13") & date <= as.Date("1965-12-13") ~ "post_4",
    date >= as.Date("1974-05-28") & date <= as.Date("1974-08-29") ~ "pre_4",
    date >= as.Date("1974-08-29") & date <= as.Date("1974-09-10") ~ "hurricane_4",
    date >= as.Date("1974-09-10") & date <= as.Date("1974-12-10") ~ "post_4",
    date >= as.Date("1995-06-27") & date <= as.Date("1995-09-27") ~ "pre_4",
    date >= as.Date("1995-09-27") & date <= as.Date("1995-10-06") ~ "hurricane_4",
    date >= as.Date("1995-10-06") & date <= as.Date("1996-01-06") ~ "post_4",
    date >= as.Date("1998-06-15") & date <= as.Date("1998-09-15") ~ "pre_4",
    date >= as.Date("1998-09-15") & date <= as.Date("1998-10-01") ~ "hurricane_4",
    date >= as.Date("1998-10-01") & date <= as.Date("1999-01-01") ~ "post_4",
    date >= as.Date("2002-06-21") & date <= as.Date("2002-09-21") ~ "pre_4",
    date >= as.Date("2002-09-21") & date <= as.Date("2002-10-04") ~ "hurricane_4",
    date >= as.Date("2002-10-04") & date <= as.Date("2003-01-04") ~ "post_4",
    date >= as.Date("1985-05-28") & date <= as.Date("1985-08-28") ~ "pre_3",
    date >= as.Date("1985-08-28") & date <= as.Date("1985-09-04") ~ "hurricane_3",
    date >= as.Date("1985-09-04") & date <= as.Date("1985-12-04") ~ "post_3",
    date >= as.Date("2004-06-14") & date <= as.Date("2004-09-14") ~ "pre_3",
    date >= as.Date("2004-09-14") & date <= as.Date("2004-09-27") ~ "hurricane_3",
    date >= as.Date("2004-09-27") & date <= as.Date("2004-12-27") ~ "post_3",
    date >= as.Date("1979-04-09") & date <= as.Date("1979-07-09") ~ "pre_1",
    date >= as.Date("1979-07-09") & date <= as.Date("1979-07-16") ~ "hurricane_1",
    date >= as.Date("1979-07-16") & date <= as.Date("1979-10-16") ~ "post_1",
    date >= as.Date("1985-05-12") & date <= as.Date("1985-08-12") ~ "pre_1",
    date >= as.Date("1985-08-12") & date <= as.Date("1985-08-20") ~ "hurricane_1",
    date >= as.Date("1985-08-20") & date <= as.Date("1985-11-20") ~ "post_1",
    date >= as.Date("1985-07-26") & date <= as.Date("1985-10-26") ~ "pre_1",
    date >= as.Date("1985-10-26") & date <= as.Date("1985-11-03") ~ "hurricane_1",
    date >= as.Date("1985-11-03") & date <= as.Date("1986-02-03") ~ "post_1",
    date >= as.Date("1988-06-07") & date <= as.Date("1988-09-07") ~ "pre_1",
    date >= as.Date("1988-09-07") & date <= as.Date("1988-09-11") ~ "hurricane_1",
    date >= as.Date("1988-09-11") & date <= as.Date("1988-12-11") ~ "post_1",
    date >= as.Date("1997-04-16") & date <= as.Date("1997-07-16") ~ "pre_1",
    date >= as.Date("1997-07-16") & date <= as.Date("1997-07-27") ~ "hurricane_1",
    date >= as.Date("1997-07-27") & date <= as.Date("1997-10-27") ~ "post_1",
    date >= as.Date("1996-07-04") & date <= as.Date("1996-10-04") ~ "pre_ts",
    date >= as.Date("1996-10-04") & date <= as.Date("1996-10-13") ~ "tropical_storm",
    date >= as.Date("1996-10-13") & date <= as.Date("1997-01-13") ~ "post_ts",
    date >= as.Date("1998-06-08") & date <= as.Date("1998-09-08") ~ "pre_ts",
    date >= as.Date("1998-09-08") & date <= as.Date("1998-09-13") ~ "tropical_storm",
    date >= as.Date("1998-09-13") & date <= as.Date("1998-12-13") ~ "post_ts",
    date >= as.Date("2001-03-05") & date <= as.Date("2001-06-05") ~ "pre_ts",
    date >= as.Date("2001-06-05") & date <= as.Date("2001-06-20") ~ "tropical_storm",
    date >= as.Date("2001-06-20") & date <= as.Date("2001-09-20") ~ "post_ts",
    date >= as.Date("2002-05-04") & date <= as.Date("2002-08-04") ~ "pre_ts",
    date >= as.Date("2002-08-04") & date <= as.Date("2002-08-09") ~ "tropical_storm",
    date >= as.Date("2002-08-09") & date <= as.Date("2002-11-09") ~ "post_ts",
    date >= as.Date("2002-06-12") & date <= as.Date("2002-09-12") ~ "pre_ts",
    date >= as.Date("2002-09-12") & date <= as.Date("2002-09-15") ~ "tropical_storm",
    date >= as.Date("2002-09-15") & date <= as.Date("2002-12-15") ~ "post_ts",
    TRUE ~ "no event"
  ))

# make a new column for storm intensity

hurricane_df3 <- hurricane_df3 %>%
  mutate(storm_intensity = case_when(
    str_detect(ewe_type, "1") ~ "one",
    str_detect(ewe_type, "2") ~ "two",
    str_detect(ewe_type, "3") ~ "three",
    str_detect(ewe_type, "4") ~ "four",
    str_detect(ewe_type, "5") ~ "five",
    str_detect(ewe_type, "ts") ~ "tropical storm",
    TRUE ~ "no event"
  ))


# create hurricane control categories just like with the other dataset by assigning non-event years to have a pre and post category -- 3 months

hurricane_df3 <- hurricane_df3 %>%
  mutate(control = case_when(
    date >= as.Date("1963-06-18") & date <= as.Date("1963-09-18") ~ "pre_control",
    date >= as.Date("1963-09-18") & date <= as.Date("1963-09-28") ~ "control",
    date >= as.Date("1963-09-28") & date <= as.Date("1963-12-28") ~ "post_control",
    date >= as.Date("1966-06-18") & date <= as.Date("1966-09-18") ~ "pre_control",
    date >= as.Date("1966-09-18") & date <= as.Date("1966-09-28") ~ "control",
    date >= as.Date("1966-09-28") & date <= as.Date("1966-12-28") ~ "post_control",
    date >= as.Date("1967-06-18") & date <= as.Date("1967-09-18") ~ "pre_control",
    date >= as.Date("1967-09-18") & date <= as.Date("1967-09-28") ~ "control",
    date >= as.Date("1967-09-28") & date <= as.Date("1967-12-28") ~ "post_control",
    date >= as.Date("1968-06-18") & date <= as.Date("1968-09-18") ~ "pre_control",
    date >= as.Date("1968-09-18") & date <= as.Date("1968-09-28") ~ "control",
    date >= as.Date("1968-09-28") & date <= as.Date("1968-12-28") ~ "post_control",
    date >= as.Date("1970-06-18") & date <= as.Date("1970-09-18") ~ "pre_control",
    date >= as.Date("1970-09-18") & date <= as.Date("1970-09-28") ~ "control",
    date >= as.Date("1970-09-28") & date <= as.Date("1970-12-28") ~ "post_control",
    date >= as.Date("1972-06-18") & date <= as.Date("1972-09-18") ~ "pre_control",
    date >= as.Date("1972-09-18") & date <= as.Date("1972-09-28") ~ "control",
    date >= as.Date("1972-09-28") & date <= as.Date("1972-12-28") ~ "post_control",
    date >= as.Date("1973-06-18") & date <= as.Date("1973-09-18") ~ "pre_control",
    date >= as.Date("1973-09-18") & date <= as.Date("1973-09-28") ~ "control",
    date >= as.Date("1973-09-28") & date <= as.Date("1973-12-28") ~ "post_control",
    date >= as.Date("1975-06-18") & date <= as.Date("1975-09-18") ~ "pre_control",
    date >= as.Date("1975-09-18") & date <= as.Date("1975-09-28") ~ "control",
    date >= as.Date("1975-09-28") & date <= as.Date("1975-12-28") ~ "post_control",
    date >= as.Date("1976-06-18") & date <= as.Date("1976-09-18") ~ "pre_control",
    date >= as.Date("1976-09-18") & date <= as.Date("1976-09-28") ~ "control",
    date >= as.Date("1976-09-28") & date <= as.Date("1976-12-28") ~ "post_control",
    date >= as.Date("1977-06-18") & date <= as.Date("1977-09-18") ~ "pre_control",
    date >= as.Date("1977-09-18") & date <= as.Date("1977-09-28") ~ "control",
    date >= as.Date("1977-09-28") & date <= as.Date("1977-12-28") ~ "post_control",
    date >= as.Date("1978-06-18") & date <= as.Date("1978-09-18") ~ "pre_control",
    date >= as.Date("1978-09-18") & date <= as.Date("1978-09-28") ~ "control",
    date >= as.Date("1978-09-28") & date <= as.Date("1978-12-28") ~ "post_control",
    date >= as.Date("1980-06-18") & date <= as.Date("1980-09-18") ~ "pre_control",
    date >= as.Date("1980-09-18") & date <= as.Date("1980-09-28") ~ "control",
    date >= as.Date("1980-09-28") & date <= as.Date("1980-12-28") ~ "post_control",
    date >= as.Date("1981-06-18") & date <= as.Date("1981-09-18") ~ "pre_control",
    date >= as.Date("1981-09-18") & date <= as.Date("1981-09-28") ~ "control",
    date >= as.Date("1981-09-28") & date <= as.Date("1981-12-28") ~ "post_control",
    date >= as.Date("1982-06-18") & date <= as.Date("1982-09-18") ~ "pre_control",
    date >= as.Date("1982-09-18") & date <= as.Date("1982-09-28") ~ "control",
    date >= as.Date("1982-09-28") & date <= as.Date("1982-12-28") ~ "post_control",
    date >= as.Date("1983-06-18") & date <= as.Date("1983-09-18") ~ "pre_control",
    date >= as.Date("1983-09-18") & date <= as.Date("1983-09-28") ~ "control",
    date >= as.Date("1983-09-28") & date <= as.Date("1983-12-28") ~ "post_control",
    date >= as.Date("1987-06-18") & date <= as.Date("1987-09-18") ~ "pre_control",
    date >= as.Date("1987-09-18") & date <= as.Date("1987-09-28") ~ "control",
    date >= as.Date("1987-09-28") & date <= as.Date("1987-12-28") ~ "post_control",
    date >= as.Date("1989-06-18") & date <= as.Date("1989-09-18") ~ "pre_control",
    date >= as.Date("1989-09-18") & date <= as.Date("1989-09-28") ~ "control",
    date >= as.Date("1989-09-28") & date <= as.Date("1989-12-28") ~ "post_control",
    date >= as.Date("1990-06-18") & date <= as.Date("1990-09-18") ~ "pre_control",
    date >= as.Date("1990-09-18") & date <= as.Date("1990-09-28") ~ "control",
    date >= as.Date("1990-09-28") & date <= as.Date("1990-12-28") ~ "post_control",
    date >= as.Date("1991-06-18") & date <= as.Date("1991-09-18") ~ "pre_control",
    date >= as.Date("1991-09-18") & date <= as.Date("1991-09-28") ~ "control",
    date >= as.Date("1991-09-28") & date <= as.Date("1991-12-28") ~ "post_control",
    date >= as.Date("1994-06-18") & date <= as.Date("1994-09-18") ~ "pre_control",
    date >= as.Date("1994-09-18") & date <= as.Date("1994-09-28") ~ "control",
    date >= as.Date("1994-09-28") & date <= as.Date("1994-12-28") ~ "post_control",
    date >= as.Date("1999-06-18") & date <= as.Date("1999-09-18") ~ "pre_control",
    date >= as.Date("1999-09-18") & date <= as.Date("1999-09-28") ~ "control",
    date >= as.Date("1999-09-28") & date <= as.Date("1999-12-28") ~ "post_control",
    date >= as.Date("2000-06-18") & date <= as.Date("2000-09-18") ~ "pre_control",
    date >= as.Date("2000-09-18") & date <= as.Date("2000-09-28") ~ "control",
    date >= as.Date("2000-09-28") & date <= as.Date("2000-12-28") ~ "post_control",
    date >= as.Date("2003-06-18") & date <= as.Date("2003-09-18") ~ "pre_control",
    date >= as.Date("2003-09-18") & date <= as.Date("2003-09-28") ~ "control",
    date >= as.Date("2003-09-28") & date <= as.Date("2003-12-28") ~ "post_control",
    TRUE ~ "no event"
  ))

hurricane_df3 <- hurricane_df3 %>%
  mutate(event = case_when(
    ewe_type == "pre_5" ~ "hurricane",
    ewe_type == "post_5" ~ "hurricane",
    ewe_type == "pre_4" ~ "hurricane",
    ewe_type == "post_4" ~ "hurricane",
    ewe_type == "pre_3" ~ "hurricane",
    ewe_type == "post_3" ~ "hurricane",
    ewe_type == "pre_1" ~ "hurricane",
    ewe_type == "post_1" ~ "hurricane",
    ewe_type == "pre_ts" ~ "hurricane",
    ewe_type == "post_ts" ~ "hurricane",
    ewe_type == "no event" & control == "pre_control" ~ "control",
    ewe_type == "no event" & control == "post_control" ~ "control",
    TRUE ~ "NA"
  )) %>%
  filter(event != "NA")

hurricane_df3 <- hurricane_df3 %>%
  mutate(timing = case_when(
    ewe_type == "pre_5" ~ "pre",
    ewe_type == "post_5" ~ "post",
    ewe_type == "pre_4" ~ "pre",
    ewe_type == "post_4" ~ "post",
    ewe_type == "pre_3" ~ "pre",
    ewe_type == "post_3" ~ "post",
    ewe_type == "pre_1" ~ "pre",
    ewe_type == "post_1" ~ "post",
    ewe_type == "pre_ts" ~ "pre",
    ewe_type == "post_ts" ~ "post",
    control == "pre_control" ~ "pre",
    control == "post_control" ~ "post",
    TRUE ~ "NA"
  )) %>%
  filter(timing != "NA")

hurricane_df3 <- hurricane_df3 %>%
  mutate(timing = factor(timing, levels = c("pre", "post"))) %>%
  mutate(timing = relevel(timing, ref = "pre")) #%>% 
 # mutate(event = factor(event, levels = c("hurricane", "control"))) %>%
 # mutate(event = relevel(event, ref = "control"))

ewe_table3 <- table(hurricane_df3$event)
view(ewe_table3)

```





## Plots
#### 554 main plot
create color palette
```{r}
lacroix_palettes_list <- LaCroixColoR::lacroix_palettes

my_pal <- lacroix_palette("Pamplemousse", n = 5, type = "continuous")
```

Faceting Labels
```{r}
parasite_order <- c(
  "trematode", "trematode_metacercaria", "myxozoan", "monogenean", "ciliate",
  "nematode", "acanthocephalan", "cestode", "copepod", "nematomorph"
)

parasite_labels <- c(
  "trematode" = "Trematode",
  "trematode_metacercaria" = "Metacercaria",
  "myxozoan" = "Myxozoan",
  "monogenean" = "Monogenean",
  "ciliate" = "Ciliate",
  "nematode" = "Nematode",
  "cestode" = "Cestode",
  "acanthocephalan" = "Acanthocephalan",
  "copepod" = "Copepod", 
  "nematomorph" = "Nematomorph"
)


storm_order <- c("five", "four", "three", "two", "one", "ts", "control")

storm_labels <- c(
  "five" = "5",
  "four" = "4",
  "three" = "3",
  "two" = "2",
  "one" = "1",
  "ts" = "TS", 
  "no event" = "control"
)

#season_order <- c(
#  "winter", "spring", "summer", "fall"
#)

#season_labels <- c(
#  "winter" = "Winter",
#  "spring" = "Spring", 
#  "summer" = "Summer", 
#  "fall" = "Fall"
#)

timing_order <- c(
  "pre", "during", "post"
)

timing_labels <- c(
  "pre" = "Pre",
  "post" = "Post", 
  "control" = "During",
  "flood" = "During", 
  "drought" = "During"
)

event_labels <- c(
  "drought" = "drought", 
  "flood" = "flood"
)

```

Mutate the hurricane dataset so that the total sum of each type of parasite can be plotted:
```{r}
hurricane_df6_sum <- hurricane_df6 %>%
  group_by(psite_type, year_collected, storm_intensity, event, timing) %>%
  summarize(total_psite_count = sum(psite_count, na.rm = TRUE), .groups = "drop") %>% 
  filter(total_psite_count != "0") %>%
  filter(!is.na(psite_type), 
         psite_type != "leech",
         psite_type != "nematomorph")

hurricane_df6_sum <- hurricane_df6_sum %>%
    mutate(psite_type = fct_relevel(psite_type, parasite_order))

hurricane_df6_sum <- hurricane_df6_sum %>%
    mutate(storm_intensity = fct_relevel(storm_intensity, storm_order))

hurricane_df6_sum <- hurricane_df6_sum %>%
    mutate(timing = fct_relevel(timing, timing_order))


## including zeroes
hurricane_df6_sum2 <- hurricane_df6 %>%
  group_by(psite_type, year_collected, storm_intensity, event, timing) %>%
  summarize(total_psite_count = sum(psite_count, na.rm = TRUE), .groups = "drop") %>%
  filter(!is.na(psite_type), 
         psite_type != "leech")

hurricane_df6_sum2 <- hurricane_df6_sum2 %>%
    mutate(psite_type = fct_relevel(psite_type, parasite_order))

hurricane_df6_sum2 <- hurricane_df6_sum2 %>%
    mutate(storm_intensity = fct_relevel(storm_intensity, storm_order))

hurricane_df6_sum2 <- hurricane_df6_sum2 %>%
    mutate(timing = fct_relevel(timing, timing_order))

```

Mutate the drought/flood dataset so that the total sum of each type of parasite can be plotted:
```{r}
drought_flood_df_sum <- drought_flood_df %>%
  group_by(psite_type, year_collected, event, timing, drought_flood, category) %>%
  summarize(total_psite_count = sum(psite_count, na.rm = TRUE), .groups = "drop") %>% 
  filter(total_psite_count != "0") %>%
  filter(!is.na(psite_type), 
         psite_type != "leech", 
         psite_type != "nematomorph")

drought_flood_df_sum <- drought_flood_df_sum %>%
    mutate(psite_type = fct_relevel(psite_type, parasite_order))

#drought_flood_df_sum <- drought_flood_df_sum %>%
 #   mutate(season = fct_relevel(season, season_order))

drought_flood_df_sum <- drought_flood_df_sum %>%
    mutate(timing = fct_relevel(timing, timing_order))


# inclduing zeroes
drought_flood_df_sum2 <- drought_flood_df %>%
  group_by(psite_type, year_collected, season, event, timing, drought_flood, category) %>%
  summarize(total_psite_count = sum(psite_count, na.rm = TRUE), .groups = "drop") %>%
  filter(!is.na(psite_type), 
         psite_type != "leech")

drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
    mutate(psite_type = fct_relevel(psite_type, parasite_order))

#drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
#    mutate(season = fct_relevel(season, season_order))

drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
    mutate(timing = fct_relevel(timing, timing_order))


```

Designate average changes in parasitism --> scale to the mean 
```{r}
# drought first
sum(drought_flood_df_sum2$total_psite_count, na.rm = TRUE)
28842/195 # average rate of parasitism across all observations is 147.9077
# in this case, each categorical 0 is counted only once, so the sum of each category includes summing all the zeroes but if there is only zeroes in a category, then those will show up as zero

drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
  mutate(relative_count = total_psite_count - 148)

# hurricane
sum(hurricane_df6_sum2$total_psite_count, na.rm = TRUE)
33422/868  # average rate of parasitism across all observations is 38.50461
# in this case, each categorical 0 is counted only once, so the sum of each category includes summing all the zeroes but if there is only zeroes in a category, then those will show up as zero

hurricane_df6_sum2 <- hurricane_df6_sum2 %>% 
  mutate(relative_count = total_psite_count - 39)

```

### Drought/Flood Plots

plot drought-flood from NOAA data
```{r}
ggplot(drought_flood_df_sum,
       aes(x = year_collected, y = drought_flood, fill = event)) + 
  geom_col(position = "dodge") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("") + 
  xlab("") + 
  scale_fill_manual(
  values = c("drought" = "#F28A8A", "flood" = "#1BB6AF"), 
  name = "",
  labels = timing_labels) 
```


```{r}
custom_y_t3 <- list(
  scale_y_continuous(limits = c(0, 3000), breaks = c(0, 1500, 3000)),
  scale_y_continuous(limits = c(0, 1200), breaks = c(0, 600, 1200)),
  scale_y_continuous(limits = c(0, 600), breaks = c(0, 300, 600)),
  scale_y_continuous(limits = c(0, 400), breaks = c(0, 200, 400)),
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100)),
  scale_y_continuous(limits = c(0, 50), breaks = c(0, 25, 50)),  
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 10, 20)),
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 5, 10)),
  scale_y_continuous(limits = c(0, 2), breaks = c(0, 1, 2))
)

# by parasite spp
ggplot(drought_flood_df_sum,
       aes(x = event, y = total_psite_count, fill = timing)) + 
  geom_col(position = "dodge") + 
  facet_wrap(~ psite_type, labeller = labeller(psite_type = parasite_labels), scales = "free_y") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF", "drought" = "#95C65C", "flood" = "#95C65C", "control" = "#95C65C"), 
  name = "",
  labels = timing_labels) 

## by just timing
ggplot(drought_flood_df_sum,
       aes(x = event, y = total_psite_count, fill = timing)) + 
  geom_col() + 
  facet_wrap(~ timing) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF", "drought" = "#95C65C", "flood" = "#95C65C", "control" = "#95C65C"), 
  name = "",
  labels = timing_labels) 

## by species??

## by relative count
ggplot(drought_flood_df_sum2,
       aes(x = event, y = relative_count, fill = timing)) + 
  geom_col(position = "dodge") + 
  facet_wrap(~ psite_type, labeller = labeller(psite_type = parasite_labels), scales = "free_y") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF", "drought" = "#95C65C", "flood" = "#95C65C", "control" = "#95C65C"), 
  name = "",
  labels = timing_labels) 


## include year of collection
ggplot(drought_flood_df_sum2,
       aes(x = year_collected, y = relative_count, fill = event)) + 
  geom_col() +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) + 
  geom_hline(yintercept = 0, color = "black") +
  ylab("Relative Parasite Count") + 
  xlab("Year Collected") + 
  scale_fill_manual(
    values = c("drought" = "#F28A8A", "flood" = "#1BB6AF", "control" = "#95C65C"), 
    name = "",
    labels = season_labels
  )
```


```{r}
ggplot(drought_flood_df_sum,
       aes(x = event, y = total_psite_count, fill = event)) + 
  geom_col() +
  facet_wrap(~ timing) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("drought" = "#F28A8A", "flood" = "#1BB6AF", "control" = "#95C65C"), 
  name = "",
  labels = season_labels) 

```


### Hurricane Plots
This is the final one for 554 Hurricane:
```{r}
custom_y <- list(
  scale_y_continuous(limits = c(0, 3000), breaks = c(0, 1500, 3000)),
  scale_y_continuous(limits = c(0, 1200), breaks = c(0, 600, 1200)),
  scale_y_continuous(limits = c(0, 600), breaks = c(0, 300, 600)),
  scale_y_continuous(limits = c(0, 400), breaks = c(0, 200, 400)),
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100)),
  scale_y_continuous(limits = c(0, 50), breaks = c(0, 25, 50)),  
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 10, 20)),
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 5, 10)),
  scale_y_continuous(limits = c(0, 2), breaks = c(0, 1, 2))
)

## by season
#ggplot(hurricane_df6_sum,
#       aes(x = storm_intensity, y = total_psite_count, fill = season)) + 
#  geom_col() + 
 # facet_wrap(~psite_type, labeller = labeller(psite_type = parasite_labels), scales = "free_y") +
 # theme(
 #   strip.background = element_rect(fill = NA, color = NA),
 #   panel.background = element_rect(fill = NA, color = "white"),
 #   panel.grid.major = element_blank(),
#    panel.grid.minor = element_blank(),
#    panel.spacing.x = unit(0, "lines"),
#    panel.spacing.y = unit(0, "lines"),
#    axis.text = element_text(size = 8, color = "grey30"),
#    axis.ticks = element_line(size = 0.2, color = "darkgrey")
#  ) +
#  ylab("Parasite Count") + 
#  xlab("Hurricane Category") + 
#  scale_fill_manual(
#  values = c("spring" = "#1BB6AF", "summer" = "#EA7580", "fall" = "#F6A1A5", "winter" = "#088BBE"), 
#  name = "",
#  labels = season_labels) +
 # scale_x_discrete(labels = storm_labels) +
#  facetted_pos_scales(y = custom_y)

## by timing 
custom_y_t <- list(
  scale_y_continuous(limits = c(0, 1400), breaks = c(0, 700, 1400)),
  scale_y_continuous(limits = c(0, 1000), breaks = c(0, 500, 1000)),
  scale_y_continuous(limits = c(0, 400), breaks = c(0, 200, 400)),
  scale_y_continuous(limits = c(0, 400), breaks = c(0, 200, 400)),
  scale_y_continuous(limits = c(0, 60), breaks = c(0, 30, 60)),
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 10, 20)),  
  scale_y_continuous(limits = c(0, 12), breaks = c(0, 6, 12)),
  scale_y_continuous(limits = c(0, 4), breaks = c(0, 2, 4)),
  scale_y_continuous(limits = c(0, 2), breaks = c(0, 1, 2))
)

ggplot(hurricane_df6_sum,
       aes(x = storm_intensity, y = total_psite_count, fill = timing)) + 
  geom_col(position = "dodge") + 
  facet_wrap(~ psite_type, labeller = labeller(psite_type = parasite_labels), scales = "free_y") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Hurricane Category") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF"), 
  name = "",
  labels = season_labels) +
  scale_x_discrete(labels = storm_labels)
```


is before and after diversity different? -- remove intensity of storms

```{r}
## by timing and event
custom_y_t2 <- list(
  scale_y_continuous(limits = c(0, 5000), breaks = c(0, 2500, 5000)),
  scale_y_continuous(limits = c(0, 8000), breaks = c(0, 4000, 8000)),
  scale_y_continuous(limits = c(0, 800), breaks = c(0, 400, 800)),
  scale_y_continuous(limits = c(0, 400), breaks = c(0, 200, 400)),
  scale_y_continuous(limits = c(0, 80), breaks = c(0, 40, 80)),
  scale_y_continuous(limits = c(0, 12), breaks = c(0, 6, 12)),  
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 00, 20)),
  scale_y_continuous(limits = c(0, 8), breaks = c(0, 4, 8)),
  scale_y_continuous(limits = c(0, 2), breaks = c(0, 1, 2))
)

ggplot(hurricane_df6_sum,
       aes(x = event, y = total_psite_count, fill = timing)) + 
  geom_col(position = "dodge") + 
  facet_wrap(~ psite_type, labeller = labeller(psite_type = parasite_labels), scales = "free_y") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF"), 
  name = "",
  labels = season_labels) #+
 # facetted_pos_scales(y = custom_y_t2)

## include year of collection
ggplot(hurricane_df6_sum,
       aes(x = year_collected, y = total_psite_count, color = timing)) + 
  geom_line(linejoin = "round") + 
  facet_wrap(~ psite_type, labeller = labeller(psite_type = parasite_labels), scales = "free_y") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("hurricane" = "#F28A8A", "control" = "#1BB6AF"), 
  name = "",
  labels = season_labels)


## include year of collection
ggplot(hurricane_df6_sum2,
       aes(x = year_collected, y = relative_count, fill = event)) + 
  geom_smooth(method = "loess",
              se = FALSE,
              formula = 'y ~ x',
              span = 0.8) +
  stat_smooth(se=FALSE, geom="area",
              method = 'loess', alpha=.5,
              span = 0.8,aes(fill=event)) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Relative Parasite Count") + 
  xlab("Year Collected") + 
  scale_fill_manual(
  values = c("hurricane" = "#F28A8A", "control" = "#1BB6AF"), 
  name = "",
  labels = season_labels) 

ggplot(hurricane_df6_sum2,
       aes(x = year_collected, y = relative_count, fill = event)) + 
  geom_col() +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) + 
  geom_hline(yintercept = 0, color = "black") +
  ylab("Relative Parasite Count") + 
  xlab("Year Collected") + 
  scale_fill_manual(
    values = c("hurricane" = "#F28A8A", "control" = "#95C65C"), 
    name = "",
    labels = season_labels
  )
```

Just by total pre and post, hurricane and control
```{r}
ggplot(hurricane_df6_sum,
       aes(x = timing, y = total_psite_count, fill = timing)) + 
  geom_col() +
  facet_wrap(~ event) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF"), 
  name = "",
  labels = season_labels) 

```


Plot frequency of different storm intensities 
```{r}
view(table(hurricane_df6$storm_intensity))

# total number of storms: cat 5 = 4, cat 4 = 6, cat 3 = 2, cat 2 = 1, cat 1 = 5, ts = 7
```

Create and plot a timeline of hurricane events:
```{r}
# Create a timeline-specific dataframe
timeline_data <- hurricane_df6 %>%
  filter(ewe_type != "no event") %>%  # Exclude rows where there is no event
  mutate(
    start = date, 
    end = case_when(
      ewe_type == "pre_5" ~ date + 180, 
      ewe_type == "post_5" ~ date + 180,
      ewe_type == "pre_4" ~ date + 180, 
      ewe_type == "post_4" ~ date + 180,
      ewe_type == "pre_3" ~ date + 180, 
      ewe_type == "post_3" ~ date + 180,
      ewe_type == "pre_1" ~ date + 180, 
      ewe_type == "post_1" ~ date + 180,
      ewe_type == "pre_ts" ~ date + 180, 
      ewe_type == "post_ts" ~ date + 180,
      TRUE ~ date  # Default case for unknown types
    ),
    event_type = ewe_type  # This will be used as the label for the event
  )

# Plot the timeline using vistime
gg_vistime(timeline_data, 
        col.start = "start", 
        col.end = "end", 
        col.event = "ewe_type", 
        title = "Hurricane Event Timeline") 


```


### More plots

Prelim plots, hurricane only
```{r}
ggplot(hurricane_df6,
       aes(x = psite_abundance, y = psite_prevalence)) + 
         geom_point() + facet_wrap(~timing) +
   theme(strip.background = element_rect(fill = NA, color = NA),
         panel.background = element_rect(fill = NA, 
                                         color = "darkgrey"),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.spacing.x = unit(0, "lines"),
         panel.spacing.y = unit(0, "lines")) +
  ylab("") + 
  xlab("")
```

More prelim plots
```{r}
ggplot(hurricane_df6,
       aes(x = storm_intensity, y = mean_streamflow)) + 
         geom_boxplot() + 
   theme(strip.background = element_rect(fill = NA, color = NA),
         panel.background = element_rect(fill = NA, 
                                         color = "darkgrey"),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.spacing.x = unit(0, "lines"),
         panel.spacing.y = unit(0, "lines")) +
  ylab("") + 
  xlab("")

ggplot(hurricane_df6,
       aes(x = ewe_type, y = psite_count)) + 
         geom_col() + 
   theme(strip.background = element_rect(fill = NA, color = NA),
         panel.background = element_rect(fill = NA, 
                                         color = "darkgrey"),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.spacing.x = unit(0, "lines"),
         panel.spacing.y = unit(0, "lines")) +
  ylab("") + 
  xlab("")

ggplot(hurricane_df6,
       aes(x = ewe_type, y = mean_streamflow)) + 
         geom_boxplot() + 
   theme(strip.background = element_rect(fill = NA, color = NA),
         panel.background = element_rect(fill = NA, 
                                         color = "darkgrey"),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.spacing.x = unit(0, "lines"),
         panel.spacing.y = unit(0, "lines")) +
  ylab("") + 
  xlab("")


ggplot(hurricane_df6,
       aes(x = ewe_type, y = mean_temperature, fill = season)) + 
  geom_boxplot() + 
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "darkgrey"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines")
  ) +
  ylab("") + 
  xlab("") +
  scale_fill_manual(values = my_pal[1:5], name = '')

ggplot(hurricane_df6,
       aes(x = psite_count)) + 
         geom_histogram() + 
   theme(strip.background = element_rect(fill = NA, color = NA),
         panel.background = element_rect(fill = NA, 
                                         color = "darkgrey"),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.spacing.x = unit(0, "lines"),
         panel.spacing.y = unit(0, "lines")) +
  ylab("") + 
  xlab("")


```

Prelim plots, drought and flood only
```{r}
facet_labels2 <- c(
  "drought" = "Drought",
  "flood" = "Flood"
)

ggplot(drought_flood_df,
       aes(x = season, y = psite_abundance, fill = ewe_type)) + 
  geom_boxplot() + facet_wrap(~ci) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "darkgrey"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines")
  ) +
  ylab("Parasite Abundance") + 
  xlab("Collection Date") +
  scale_fill_manual(values = my_pal[1:5], name = '')
```

more plots 
```{r}

# remove non-comparable sites:
hdf_pp <- hurricane_df6 %>%
  filter(site != "CD",
         site != "CC", 
         site != "IB")

z <- ggplot(hdf_pp,
       aes(x = timing, y = mean_temperature, fill = timing)) + 
  geom_boxplot() + facet_grid(.~site) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "grey99"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"), 
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("Mean Temperature (C)") + 
  xlab("Pre or Post Hurricane") +
  scale_fill_manual(values = my_pal[1:4], name = '', labels = pp_label)

x <- ggplot(hdf_pp,
       aes(x = timing, y = mean_streamflow, fill = timing)) + 
  geom_boxplot() + facet_grid(.~site) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    strip.text = element_blank(),
    panel.background = element_rect(fill = NA, color = "grey99"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"), 
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks = element_blank()
  ) +
 ylab("Mean Streamflow (m³/s)") + 
  xlab("") +
  scale_fill_manual(values = my_pal[1:4], name = '', labels = pp_label) 

zx <- ggarrange(z, x, common.legend = TRUE, legend = "bottom", labels = c("A", "B"), align = "v", ncol = 1)

print(zx)

```


### other adjustments -- dataset by species only
Adjust datasets for model to help with trends seen -- by parasite species only 
```{r}
hurricane_df6_trem <- hurricane_df6 %>%
  filter(!is.na(psite_type), 
         psite_type == "trematode")
```




## Model
#### drought flood - count
```{r}
# summary(drfl_1 <- glmmTMB(psite_count ~ ewe_type + (1|catalog_number/site) + (1|season) + (1|year_collected) + (1|psite_type/fish_sp_y), data = drought_flood_df_clean_noci, family = "nbinom1"))

# drought and flood against control together
summary(drfl_1 <- glmmTMB(psite_abundance ~ ewe_type + (1|catalog_number) + (1|season) + (1|year_collected) + (1|psite_type/fish_sp_y), 
                          data = drought_flood_df, family = "nbinom1"))

# just droughts vs. control
summary(d_1 <- glmmTMB(psite_abundance ~ ewe_type + (1|catalog_number) + (1|season) + (1|year_collected) + (1|psite_type/fish_sp_y), 
                          data = ddf, family = "nbinom1"))

# just floods vs. control
summary(f_1 <- glmmTMB(psite_abundance ~ ewe_type + (1|catalog_number) + (1|season) + (1|year_collected) + (1|psite_type/fish_sp_y), 
                          data = fdf, family = "nbinom1"))



### this is the main one:
# trying with the new code and model - same as hurricane
summary(df_count <- glmmTMB(psite_abundance ~ event*timing + (1|ci/catalog_number) + (1|year_collected/season) + (1|fish_sp_y/psite_type), 
                          data = drought_flood_df, family = "nbinom1"))

summary(df_count <- glmmTMB(psite_abundance ~ event*timing + (1|ci/catalog_number) + (1|year_collected/season) + (1|fish_sp_y/psite_type), 
                          data = drought_flood_df, family = nbinom1(link = "sqrt"))) 

summary(df_count <- glmmTMB(psite_abundance ~ event*timing + (1|ci/catalog_number) + (1|year_collected/season) + (1|fish_sp_y/psite_type), 
                          data = drought_flood_df, family = nbinom2(link = "sqrt"))) 

summary(df_count <- glmmTMB(psite_abundance ~ event*timing + (1|ci/catalog_number) + (1|year_collected/season) + (1|fish_sp_y/psite_type), 
                          data = drought_flood_df, family = nbinom2(link = "log")))





# diagnostics
#Evaluate residuals
s_df = simulateResiduals(fittedModel = df_count, n = 250)
s_df$scaledResiduals
plot(s_df)

```

#### drought flood - prevalence
```{r}
# drought and flood against control together
summary(drfl_2 <- glmmTMB(psite_prevalence ~ ewe_type + (1|catalog_number) + (1|season) + (1|year_collected) + (1|psite_type/fish_sp_y), 
                          data = drought_flood_df, family = "binomial"))

# just droughts vs. control
summary(d_2 <- glmmTMB(psite_prevalence ~ ewe_type + (1|catalog_number) + (1|season) + (1|year_collected) + (1|psite_type/fish_sp_y), 
                          data = ddf, family = "nbinom1"))

# just floods vs. control
summary(f_2 <- glmmTMB(psite_prevalence ~ ewe_type + (1|catalog_number) + (1|season) + (1|year_collected) + (1|psite_type/fish_sp_y), 
                          data = fdf, family = "nbinom1"))
```


#### hurricane model - count (abundance)
```{r}

# family options:, family = "nbinom1" , family = nbinom1(link="sqrt"), , family = nbinom2(link="sqrt"), , family = nbinom2(link="log")

## updated model following meeting on 1/27

summary(hurricane_count <- glmmTMB(psite_abundance ~ event*timing*psite_type + (total_length_mm|fish_sp_x/parasite_taxonomic_group) + (1|ci/catalog_number) + (1|storm_intensity) + (1|year_collected/season) + (1|fish_sp_y/psite_spp_y), 
                          data = hurricane_df6, family = "nbinom1")) 


# diagnostics
#Evaluate residuals
s = simulateResiduals(fittedModel = hurricane_count, n = 250)
s$scaledResiduals
plot(s)

```

#### hurricane model - prevalence
```{r}
summary(hurricane_prevalence <- glmmTMB(psite_prevalence ~ ewe_type + ci + (1|storm_intensity) + (1|catalog_number/site) + (1|season) + (1|year_collected) + (1|psite_type/fish_sp_y), 
                          data = hurricane_df6, family = binomial))
```


