---
title: 'Drought and Flood: NOLA CAREER Project'
author: "Connor Whalen"
date: "2025-02-18"
output:
  word_document:
    toc: true
    toc_depth: '3'
  html_document:
    theme: readable
    highlight: textmate
    toc: true
    toc_float: true
    toc_depth: 3
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Introduction
This file contains all code pertaining to the CAREER project in NOLA's drought and flood analysis. 

# Setup
#### Install packages.
```{r package install, eval=FALSE, echo=FALSE}
install.packages("tidyverse")
install.packages("janitor")
install.packages("ggeffects")
install.packages("ggpubr")
install.packages("glmmTMB")
install.packages("devtools")
devtools::install_github("johannesbjork/LaCroixColoR")
install.packages("patchwork")
install.packages("ggh4x")
install.packages("vistime")
install.packages("DHARMa")
```

#### Load packages.
```{r package load, echo=FALSE}
library(ggpubr)
library(ggeffects)
library(tidyverse)
library(readr)
library(dbplyr)
library(lubridate)
library(ggplot2)
library(stringr)
library(glmmTMB)
library(lme4)
library(LaCroixColoR)
library(patchwork)
library(ggh4x)
library(parameters)
library(vistime)
library(car)
library(DHARMa)
```
#### Set up aesthetic for plots
```{r}
# color palette -- hurricane = #CB87B4, control = #F4B95A, drought = #D84D16, flood = #1BB6AF
# trem = #c9ad79 , meta = #F66387 , mono = #A6E000 , myxo = #07c4c5
connor_theme <- theme(legend.position = "top", 
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 14),
        strip.background = element_rect(fill = NA, color = NA),
        panel.background = element_rect(fill = NA, color = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.spacing.x = unit(0, "lines"),
        panel.spacing.y = unit(0, "lines"),
        axis.text = element_text(size = 8, color = "grey30"),
        axis.ticks = element_line(size = 0.2, color = "darkgrey"))
```
## Data prep and cleaning
#### Load full datasets (parasites collected and NOAA SPI precipitation data) and prep data for analysis
```{r datasets and dataframe loading and general df clean and prep for analysis, echo=FALSE}
full_data <- read.csv("~/Desktop/UW/TUBRI/data/processed/Full_dataset_physical_2024.09.25.csv") %>% 
  janitor::clean_names()

SPI_data <- read.csv("~/Desktop/UW/Chapter1 NOLA/datasets/SPI data - Sheet1.csv") %>% 
  janitor::clean_names()

# Prep all data for analysis, inclduing assigning parasite type categories, abundance and prevalence counts, and establishing correct column date structure
full_data <- full_data %>%
  mutate(psite_type = case_when(
    str_detect(fish_psite_combo, "ACAN") ~ "acanthocephalan",
    str_detect(fish_psite_combo, "ACANTH") ~ "acanthocephalan",
    str_detect(fish_psite_combo, "CEST") ~ "cestode",
    str_detect(fish_psite_combo, "CILI") ~ "ciliate",
    str_detect(fish_psite_combo, "COPE") ~ "copepod",
    str_detect(fish_psite_combo, "LEECH") ~ "leech",
    str_detect(fish_psite_combo, "META") ~ "trematode_metacercaria",
    str_detect(fish_psite_combo, "MONO") ~ "monogenean",
    str_detect(fish_psite_combo, "MYX") ~ "myxozoan",
    str_detect(fish_psite_combo, "MYXO") ~ "myxozoan",
    str_detect(fish_psite_combo, "NEM") ~ "nematode",
    str_detect(fish_psite_combo, "NMORPH") ~ "nematomorph",
    str_detect(fish_psite_combo, "TREM") ~ "trematode",
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(psite_abundance = case_when(
    str_detect(fish_psite_combo, "ACAN") ~ psite_count,
    str_detect(fish_psite_combo, "ACANTH") ~ psite_count,
    str_detect(fish_psite_combo, "CEST") ~ psite_count,
    str_detect(fish_psite_combo, "CILI") ~ psite_count,
    str_detect(fish_psite_combo, "COPE") ~ psite_count,
    str_detect(fish_psite_combo, "LEECH") ~ psite_count,
    str_detect(fish_psite_combo, "META") ~ psite_count,
    str_detect(fish_psite_combo, "MONO") ~ psite_count,
    str_detect(fish_psite_combo, "NEM") ~ psite_count,
    str_detect(fish_psite_combo, "NMORPH") ~ psite_count,
    str_detect(fish_psite_combo, "TREM") ~ psite_count,
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(psite_prevalence = case_when(
    str_detect(fish_psite_combo, "MYX") ~ psite_count,
    str_detect(fish_psite_combo, "MYXO") ~ psite_count,
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(date = as.Date(paste(year_collected, month_collected, day_collected, sep = "-"))) 

SPI_data <- SPI_data %>% 
  mutate(date = as.Date(date))

full_data <- full_data %>% 
  mutate(psite_prevalence = as.integer(psite_prevalence))

full_data <- full_data %>% 
  left_join(SPI_data, by = "date")

## assign control and flood categories to the different SPI value categories 
# category = average = true control
# category = abnormally wet / dry = marginal control 
# category = exceptionally wet / dry = full drought/flood

full_data <- full_data %>%
  mutate(event = case_when(
    str_detect(category, "exceptionally wet") ~ "flood",
    str_detect(category, "extremely wet") ~ "flood",
    str_detect(category, "severely wet") ~ "flood",
    str_detect(category, "moderately wet") ~ "flood",
    str_detect(category, "exceptionally dry") ~ "drought",
    str_detect(category, "extremely dry") ~ "drought",
    str_detect(category, "severely dry") ~ "drought",
    str_detect(category, "moderately dry") ~ "drought",
    str_detect(category, "abnormally wet") ~ "control",
    str_detect(category, "abnormally dry") ~ "control",
    str_detect(category, "average") ~ "control", # there are no parasites collected in the "average" grouping
    TRUE ~ "marginal"
  )) %>% 
  mutate(event = as.factor(event)) %>% 
  mutate(category = as.factor(category)) %>% 
  mutate(psite_type = as.factor(psite_type))

# change fish names to shorthand
full_data <- full_data %>%
  mutate(fish_sp_x = case_when(
    fish_sp_x == "Gambusia affinis" ~ "gamaff",
    fish_sp_x == "Pimephales vigilax" ~ "pimvig",
    fish_sp_x == "Percina vigil" ~ "pervig",
    fish_sp_x == "Carpiodes velifer" ~ "carvel",
    fish_sp_x == "Hybognathus nuchalis" ~ "hybnuc",
    fish_sp_x == "Notropis atherinoides" ~ "notath",
    fish_sp_x == "Ictalurus punctatus" ~ "ictpun",
    TRUE ~ fish_sp_x
  ))

full_data <- full_data %>%
  mutate(month_day = format(date, "%m-%d"))

# what are total counts of each parasite type in the main dataset?
summary <- full_data %>%
  group_by(psite_type) %>%
  summarise(
    total_observations = n(),
    total_parasite_count = sum(psite_count, na.rm = TRUE)
  )

# drop low replicate categories
drought_flood_df <- full_data %>%
  filter(psite_type %in% c("trematode", "trematode_metacercaria", "monogenean")) %>% 
  mutate(psite_type = factor(psite_type, 
                             levels = c("monogenean", "trematode", "trematode_metacercaria")))

# filter out all remaining NAs from the psite_abundance column
drought_flood_df_a <- drought_flood_df %>%
  filter(!is.na(psite_abundance))

# create new category for myxos
drought_flood_df_m <- full_data %>%
  filter(psite_type %in% c("myxozoan"))

# filter out all remaining NAs from the psite_prevalence column
drought_flood_df_m <- drought_flood_df_m %>%
  filter(!is.na(psite_prevalence))
```

# Abundance
## Plot raw data (as averages not sums) to identify any trends in the data or inconsistencies.
```{r}
# how many replicates are in each category --> this is just the number of occurrences, not abundance of parasites
dfa.reps <- drought_flood_df_a %>% 
  group_by(event, category, psite_type, fish_sp_x) %>% 
  summarize(observations = n(), .groups = "drop")

# plot how many of each category we have
raw1 <- ggplot(dfa.reps,
       aes(x = fish_sp_x, y = observations, fill = psite_type)) +
  facet_wrap(~ event) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
  labs(x = "Fish Species", y = "Number of Observations", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

# hurricane abundance with parasite type
dfa.bins1 <- drought_flood_df_a %>% 
  group_by(event, category, psite_type) %>% 
  summarize(avg.bin = mean(psite_abundance))

# use this as the raw plot of data
raw2 <- ggplot(dfa.bins1,
       aes(x = event, y = avg.bin, fill = psite_type)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
  labs(x = "Event", y = "Estimate", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

# hurricane abundance with fish species and parasite type
dfa.bins2 <- drought_flood_df_a %>% 
  group_by(event, category, psite_type, fish_sp_x) %>% 
  summarize(avg.bin = mean(psite_abundance))

# use this as the raw plot of data
raw3 <- ggplot(dfa.bins2,
       aes(x = fish_sp_x, y = avg.bin, fill = psite_type)) +
  facet_wrap(~ event) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
  labs(x = "Fish Species", y = "Estimate", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

df_abundance_raw <- ggarrange(raw1, raw2, raw3, common.legend = FALSE, legend = "bottom", labels = c("A", "B", "C"))
plot(df_abundance_raw)
```

## Drop carvel and pervig from analysis since they do not have monos and metas consistently
```{r}
drought_flood_df_a_only_full <- drought_flood_df_a %>% 
  filter(!fish_sp_x %in% c("pervig", "carvel"))

# plot new raw data
# how many replicates are in each category--> this is just the number of occurrences, not abundance of parasites
dfa.reps <- drought_flood_df_a_only_full %>% 
  group_by(event, category, psite_type, fish_sp_x) %>% 
  summarize(observations = n(), .groups = "drop")

# plot how many of each category we have
raw1_f <- ggplot(dfa.reps,
       aes(x = fish_sp_x, y = observations, fill = psite_type)) +
  facet_wrap(~ event) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
  labs(x = "Fish Species", y = "Number of Observations", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

# hurricane abundance with parasite type --> average abundances 
dfa.bins1 <- drought_flood_df_a_only_full %>% 
  group_by(event, category, psite_type) %>% 
  summarize(avg.bin = mean(psite_abundance))

# use this as the raw plot of data
raw2_f <- ggplot(dfa.bins1,
       aes(x = event, y = avg.bin, fill = psite_type)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
  labs(x = "Event", y = "Average Parasite Abundance", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

# hurricane abundance with fish species and parasite type
dfa.bins2 <- drought_flood_df_a_only_full %>% 
  group_by(event, category, psite_type, fish_sp_x) %>% 
  summarize(avg.bin = mean(psite_abundance))

# use this as the raw plot of data
raw3_f <- ggplot(dfa.bins2,
       aes(x = fish_sp_x, y = avg.bin, fill = psite_type)) +
  facet_wrap(~ event) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
  labs(x = "Fish Species", y = "Average Parasite Abundance", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

df_abundance_raw_only_full <- ggarrange(raw1_f, raw2_f, raw3_f, common.legend = FALSE, legend = "bottom", labels = c("A", "B", "C"))
plot(df_abundance_raw_only_full)
```
## Seasonality influencing distribution of abundance
```{r}
# month and day against number of replicates
dfp.season <- drought_flood_df_a %>% 
  group_by(event, psite_type, fish_sp_x, season, month_day, year_collected) %>% 
  summarize(observations = n(), .groups = "drop")

# insert a dummy year as an anchor
dfp.season <- dfp.season %>%
  mutate(month_day_date = as.Date(paste0("2025-", month_day), format = "%Y-%m-%d"))

dfp.season$month_day_date <- as.Date(format(as.Date(dfp.season$month_day_date), "2025-%m-%d"))

range(dfp.season$month_day_date)


ggplot(dfp.season,
       aes(x = month_day_date, y = event, fill = psite_type)) +
  geom_violin(scale = "count", trim = FALSE) +
  geom_point(position = position_jitter(height = 0.2), shape = 21, size = 3, stroke = 0.2) +
  scale_x_date(
    limits = as.Date(c("2025-01-03", "2025-12-26")),
    date_labels = "%b",
    date_breaks = "1 month",
    expand = c(0.01, 0)
  ) +
  scale_fill_manual(values = c(
    "trematode_metacercaria" = "#AFDFEF",
    "monogenean" = "#A6E000",
    "trematode" = "#c9ad79",
    "myxozoan" = "#07c3c5"
  )) +
  labs(x = "Month", y = "Event", fill = "Parasite Type") +
  connor_theme

# run a model to see if season has an effect on occurrences
season_model <- glmmTMB(observations ~ season*event, family = nbinom2, data = dfp.season)
simulateResiduals(fittedModel = season_model, plot = TRUE)
summary(season_model)
plot(parameters(season_model))
```

## Abundance Models
### 3 parasite types
```{r, eval=FALSE, echo=FALSE}
# nbinom1 log

nbinom1log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom1, data = drought_flood_df_a_only_full)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_a_only_full)

# nbinom2 log

nbinom2log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2, data = drought_flood_df_a_only_full)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df_a_only_full)

# nbinom12 log

nbinom12log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom12, data = drought_flood_df_a_only_full)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df_a_only_full)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = drought_flood_df_a_only_full)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_a_only_full)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = drought_flood_df_a_only_full)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df_a_only_full)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = drought_flood_df_a_only_full)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df_a_only_full)


# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff
  )

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()
```

## Final d/f abundance model 
```{r}

df_abundance_final <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + (total_length_mm|fish_psite_combo), 
                                family = nbinom2, data = drought_flood_df_a_only_full)


simulateResiduals(fittedModel = df_abundance_final, plot = TRUE)
summary(df_abundance_final)
plot(parameters(df_abundance_final))


# relevel to have trems in the reference cateogory:
drought_flood_df_a_only_full <- drought_flood_df_a_only_full %>%
  filter(psite_type %in% c("trematode", "trematode_metacercaria", "monogenean")) %>% 
  mutate(psite_type = factor(psite_type, 
                             levels = c("trematode", "trematode_metacercaria", "monogenean")))

df_abundance_final <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + (total_length_mm|fish_psite_combo), 
                                family = nbinom2, data = drought_flood_df_a_only_full)


simulateResiduals(fittedModel = df_abundance_final, plot = TRUE)
summary(df_abundance_final)
plot(parameters(df_abundance_final))

# gives NA in the AIC
```
# Plots - abundance
```{r}
df1a <- ggpredict(df_abundance_final, terms = c("psite_type", "event"))
df1a <- df1a %>%
  rename(
    psite_type = x,
    estimate = predicted,
    se = std.error,
    lower = conf.low,
    upper = conf.high,
    event = group)

# add significance bars
meta_sig_df <- data.frame(
  group1 = c("control", "control", "control"),
  group2 = c("drought", "drought", "flood"),
  psite_type = c("trematode", "trematode_metacercaria", "trematode_metacercaria"),
  y.position = c(6, 7, 8), 
  p.value = c(0.04806, 0.0000000147, 0.00559) 
)

meta_sig_df <- meta_sig_df %>%
  mutate(
    stars = cut(p.value,
                breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                labels = c("***", "**", "*", "ns"))
  )

dodge_offset <- 0.16

meta_sig_df_dodged <- meta_sig_df %>%
  filter(psite_type == "trematode_metacercaria") %>%
  mutate(
    xmin = as.numeric(factor(group1, levels = c("control", "drought", "flood"))) + dodge_offset,
    xmax = as.numeric(factor(group2, levels = c("control", "drought", "flood"))) + dodge_offset
  )

meta_sig_df_nododge <- meta_sig_df %>%
  filter(psite_type == "trematode") %>%
  mutate(
    xmin = as.numeric(factor(group1, levels = c("control", "drought", "flood"))),
    xmax = as.numeric(factor(group2, levels = c("control", "drought", "flood")))
  )

# plot df1a
df1a <- ggplot(df1a,
       aes(x = event, y = estimate)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, group = psite_type),
                width = 0.05,
                position = position_dodge(width = 0.5)) +
  geom_line(aes(group = psite_type, linetype = psite_type),
            position = position_dodge(width = 0.5)) +
  geom_point(aes(fill = psite_type, group = psite_type),
             pch = 21, size = 5,
             position = position_dodge(width = 0.5)) +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
    scale_y_continuous(limits = c(0, 8), breaks = seq(0, 8, by = 2)) + 
  labs(x = "Event", y = "Estimate", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme  + 
  stat_pvalue_manual(
    data = meta_sig_df_dodged,
    label = "stars",
    xmin = "xmin",
    xmax = "xmax",
    y.position = "y.position",
    tip.length = 0.01
  ) +
  stat_pvalue_manual(
    data = meta_sig_df_nododge,
    label = "stars",
    xmin = "xmin",
    xmax = "xmax",
    y.position = "y.position",
    tip.length = 0.01
  )
```

## Plot abundance model and raw data next to each other
```{r}
df_abundance_raw_and_model <- ggarrange(df1a, raw2_f, common.legend = FALSE, legend = "bottom", labels = c("A", "B"))
plot(df_abundance_raw_and_model)

# Why don't raw and modeled data look the same?

# mono result is opposite the raw data
# trem result is roughly the same, but control should be higher than drought in the raw
# meta result is mostly fine, but flood should be higher than control in the raw

# let's look again at our raw data from above 
plot(raw3_f)

# looks like hybnuc in both drought and flood have very high counts of monogenes, let's remove hybog from the raw data and see if it more closely matches the expected model result
no_hybnuc <- drought_flood_df_a_only_full %>% 
  group_by(event, category, psite_type, fish_sp_x) %>% 
  summarize(avg.bin = mean(psite_abundance))

no_hybnuc <- no_hybnuc %>% 
  filter(!fish_sp_x %in% c("hybnuc"))

no_hn <- ggplot(no_hybnuc,
       aes(x = event, y = avg.bin, fill = psite_type)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
  labs(x = "Event", y = "Average Parasite Abundance", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

# plot this no-hybnuc result next to the model plot

df_abundance_raw_and_model_corrected <- ggarrange(df1a, no_hn, common.legend = FALSE, legend = "bottom", labels = c("A", "B"))
plot(df_abundance_raw_and_model_corrected)

# it helps, but does not fix the problem entirely, but maybe it is ok?
```


## Zero inflated results plotted - abundance
```{r}
#### A 
azi1 <- ggemmeans(df_abundance_final, terms = c("psite_type", "event"), component = "zi")

azi1 <- azi1 %>%
  rename(
    psite_type = x,
    estimate = predicted,
    se = std.error,
    lower = conf.low,
    upper = conf.high,
    event = group
  )

azi1p <- ggplot(azi1, aes(x = event, y = estimate)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, group = psite_type),
                width = 0.05,
                position = position_dodge(0.5)) +
  geom_line(aes(group = psite_type, linetype = psite_type),
            position = position_dodge(0.5)) +
  geom_point(aes(fill = psite_type, group = psite_type),
             pch = 21, size = 5,
             position = position_dodge(0.5)) +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF",
                               "monogenean" = "#A6E000",
                               "trematode" = "#c9ad79",
                               "myxozoan" = "#07c3c5")) +
  scale_y_continuous(limits = c(0, 80), breaks = seq(0, 80, 10)) +
  labs(x = "Event",
       y = "Zero-Inflation Estimate",
       fill = "Parasite Type",
       linetype = "Parasite Type") +
  connor_theme

#### C
azi3 <- ggemmeans(df_abundance_final, terms = c("psite_type", "event"), component = "zi")

azi3 <- azi3 %>%
  rename(
    psite_type = x,
    estimate = predicted,
    se = std.error,
    lower = conf.low,
    upper = conf.high,
    event = group
  )

azi3 <- azi3 %>% 
  filter(psite_type %in% c("trematode"))

azi3p <- ggplot(azi3,
       aes(x = event, y = estimate)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, group = event),
                width = 0.05,
                position = position_dodge(width = 0.5)) +
  geom_line(aes(group = psite_type, linetype = psite_type),
            position = position_dodge(width = 0.5)) +
  geom_point(aes(fill = psite_type, group = psite_type),
             pch = 21, size = 5,
             position = position_dodge(width = 0.5)) +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
    scale_y_continuous(limits = c(0, 80), breaks = seq(0, 80, 10)) + 
  labs(x = "Event", y = "Zero-Inflation Estimate", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

#### E
azi5 <- ggemmeans(df_abundance_final, terms = c("psite_type", "event"), component = "zi")

azi5 <- azi5 %>%
  rename(
    psite_type = x,
    estimate = predicted,
    se = std.error,
    lower = conf.low,
    upper = conf.high,
    event = group
  )

azi5 <- azi5 %>% 
  filter(psite_type %in% c("trematode_metacercaria"))

azi5p <- ggplot(azi5,
       aes(x = event, y = estimate)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, group = event),
                width = 0.05,
                position = position_dodge(width = 0.5)) +
  geom_line(aes(group = psite_type, linetype = psite_type),
            position = position_dodge(width = 0.5)) +
  geom_point(aes(fill = psite_type, group = psite_type),
             pch = 21, size = 5,
             position = position_dodge(width = 0.5)) +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
    scale_y_continuous(limits = c(0, 60), breaks = seq(0, 60, 10)) + 
  labs(x = "Event", y = "Zero-Inflation Estimate", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

# try to plot only monos
azi6 <- ggemmeans(df_abundance_final, terms = c("psite_type", "event"), component = "zi")

azi6 <- azi6 %>%
  rename(
    psite_type = x,
    estimate = predicted,
    se = std.error,
    lower = conf.low,
    upper = conf.high,
    event = group
  )

azi6 <- azi6 %>% 
  filter(psite_type %in% c("monogenean"))

azi6p <- ggplot(azi6,
       aes(x = event, y = estimate)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, group = event),
                width = 0.05,
                position = position_dodge(width = 0.5)) +
  geom_line(aes(group = psite_type, linetype = psite_type),
            position = position_dodge(width = 0.5)) +
  geom_point(aes(fill = psite_type, group = psite_type),
             pch = 21, size = 5,
             position = position_dodge(width = 0.5)) +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
    scale_y_continuous(limits = c(0, 40), breaks = seq(0, 40, 10)) + 
  labs(x = "Event", y = "Zero-Inflation Estimate", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

df_abundance_plot_zi <- ggarrange(azi1p, azi3p, azi5p, azi6p, common.legend = FALSE, legend = "bottom", labels = c("A", "B", "C", "D", "E", "F"))
plot(df_abundance_plot_zi)
```


# Prevalence  
Plot raw data (as averages not sums) to identify any trends in the data or inconsistencies.
```{r}
# how many replicates are in each category --> this is just the number of occurrences, not abundance of parasites
dfp.reps <- drought_flood_df_m %>% 
  group_by(event, psite_type, fish_sp_x) %>% 
  summarize(observations = n(), .groups = "drop")

# plot how many of each category we have
raw1p <- ggplot(dfp.reps,
       aes(x = fish_sp_x, y = observations, fill = psite_type)) +
  facet_wrap(~ event) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
  labs(x = "Fish Species", y = "Number of Observations", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

# hurricane abundance with parasite type
dfp.bins1 <- drought_flood_df_m %>% 
  group_by(event, psite_type) %>% 
  summarize(avg.bin = mean(psite_prevalence))

# use this as the raw plot of data
raw2p <- ggplot(dfp.bins1,
       aes(x = event, y = avg.bin, fill = psite_type)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
  labs(x = "Event", y = "Estimate", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

# hurricane abundance with fish species and parasite type
dfp.bins2 <- drought_flood_df_m %>% 
  group_by(event, psite_type, fish_sp_x) %>% 
  summarize(avg.bin = mean(psite_prevalence))

# use this as the raw plot of data
raw3p <- ggplot(dfp.bins2,
       aes(x = fish_sp_x, y = avg.bin, fill = psite_type)) +
  facet_wrap(~ event) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
  labs(x = "Fish Species", y = "Estimate", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

df_prevalence_raw <- ggarrange(raw1p, raw2p, raw3p, common.legend = FALSE, legend = "bottom", labels = c("A", "B", "C"))
plot(df_prevalence_raw)

# no myxos in percina -- is already not in the database
```

## Seasonality influencing distribution - prevalence
```{r}
# month and day against number of replicates
dfp.season <- drought_flood_df_m %>% 
  group_by(event, psite_type, fish_sp_x, season, month_day, year_collected) %>% 
  summarize(observations = n(), .groups = "drop")

# insert a dummy year as an anchor
dfp.season <- dfp.season %>%
  mutate(month_day_date = as.Date(paste0("2025-", month_day), format = "%Y-%m-%d"))

dfp.season$month_day_date <- as.Date(format(as.Date(dfp.season$month_day_date), "2025-%m-%d"))

range(dfp.season$month_day_date)


ggplot(dfp.season,
       aes(x = month_day_date, y = event, fill = psite_type)) +
  geom_violin(scale = "count", trim = FALSE) +
  geom_point(position = position_jitter(height = 0.2), shape = 21, size = 3, stroke = 0.2) +
  scale_x_date(
    limits = as.Date(c("2025-01-03", "2025-12-26")),
    date_labels = "%b",
    date_breaks = "1 month",
    expand = c(0.01, 0)
  ) +
  scale_fill_manual(values = c(
    "trematode_metacercaria" = "#AFDFEF",
    "monogenean" = "#A6E000",
    "trematode" = "#c9ad79",
    "myxozoan" = "#07c3c5"
  )) +
  labs(x = "Month", y = "Event", fill = "Parasite Type") +
  connor_theme

# run a model to see if season has an effect on occurrences
season_model <- glmmTMB(observations ~ season*event, family = nbinom2, data = dfp.season)
simulateResiduals(fittedModel = season_model, plot = TRUE)
summary(season_model)
plot(parameters(season_model))

```
## Prevalence model validation
```{r, echo=FALSE, eval=FALSE}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1, data = drought_flood_df_m)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_m)

# nbinom2 log

nbinom2log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = drought_flood_df_m)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df_m)

# nbinom12 log

nbinom12log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom12, data = drought_flood_df_m)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df_m)

## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = drought_flood_df_m)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_m)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = drought_flood_df_m)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df_m)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = drought_flood_df_m)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df_m)


# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff")

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()
```

## Final prevalence model drought/flood
```{r}
# this model is the best fit 

df_prevalence_final <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = drought_flood_df_m)

simulateResiduals(fittedModel = df_prevalence_final, plot = TRUE)
summary(df_prevalence_final)
plot(parameters(df_prevalence_final))

```

## Plots -- d/f prevalence
```{r}
#### prevalence plot
df1p <- ggpredict(df_prevalence_final, terms = c("event"))

df1p <- df1p %>%
  rename(
    event = x,
    estimate = predicted,
    se = std.error,
    lower = conf.low,
    upper = conf.high)

df_f <- ggplot(df1p,
       aes(x = event, y = estimate)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, group = event),
                width = 0.05,
                position = position_dodge(width = 0.5)) +
  geom_point(aes(fill = event, group = event),
             pch = 21, size = 5,
             position = position_dodge(width = 0.5)) +
  scale_fill_manual(values = c("drought" = "#D84D16", "flood" = "#1BB6AF","control" = "#F4B95A", "impact" = "#FF69B4")) + 
    scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 2)) +
  labs(x = "Event", y = "Estimate", fill = "Event") +
  connor_theme

```

PLot prevalence model and raw data together 
```{r}
df_prevalence_raw_and_model <- ggarrange(df_f, raw2p, common.legend = FALSE, legend = "bottom", labels = c("A", "B"))
plot(df_prevalence_raw_and_model)

# control and flood do not match raw estimate to predicted (should be flipped)

# let's look again at our raw data from above 
plot(raw1p)

# looks like hybnuc and carvel in control have very high counts of myxos, let's remove hybog from the raw data and see if it more closely matches the expected model result
no_hybnuc <- drought_flood_df_m %>% 
  group_by(event, category, psite_type, fish_sp_x) %>% 
  summarize(avg.bin = mean(psite_prevalence))

no_hybnuc <- no_hybnuc %>% 
  filter(!fish_sp_x %in% c("hybnuc", "carvel"))

no_hn <- ggplot(no_hybnuc,
       aes(x = event, y = avg.bin, fill = psite_type)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
  labs(x = "Event", y = "Average Parasite Abundance", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme

# plot this no-hybnuc result next to the model plot

df_prevalence_raw_and_model_corrected <- ggarrange(df_f, no_hn, common.legend = FALSE, legend = "bottom", labels = c("A", "B"))
plot(df_prevalence_raw_and_model_corrected)

# the data is now technically correct and matches
```

## Zero Inflated prevalence plots
```{r}
pzi1 <- ggemmeans(df_prevalence_final, terms = c("event"), component = "zi")

pzi1 <- pzi1 %>%
  rename(
    event = x,
    estimate = predicted,
    se = std.error,
    lower = conf.low,
    upper = conf.high,
    psite_type = group
  ) %>%
  mutate(psite_type = ifelse(psite_type == "1", "myxozoan", psite_type)) %>%
  drop_na()

pzi1p <- ggplot(pzi1,
       aes(x = event, y = estimate)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, group = event),
                width = 0.05,
                position = position_dodge(width = 0.5)) +
  geom_point(aes(fill = event, group = event),
             pch = 21, size = 5,
             position = position_dodge(width = 0.5)) +
  scale_fill_manual(values = c("drought" = "#D84D16", "flood" = "#1BB6AF","control" = "#F4B95A", "impact" = "#FF69B4")) + 
    scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 2)) +
  labs(x = "Event", y = "Zero Inflation Estimate", fill = "Event") +
  connor_theme

df_prevalence_plot_zi <- ggarrange(pzi1p, common.legend = FALSE, legend = "bottom", labels = c("A"))
plot(df_prevalence_plot_zi)

```
## Plot Zi and conditional model outputs together -- prevalence
```{r}
df_prevalence_plot_total <- ggarrange(df_f, pzi1p, common.legend = TRUE, legend = "bottom", labels = c("A", "B"))
plot(df_prevalence_plot_total)
```


# Estimating Biodiversity Changes
Jackknife estimates 
```{r}
# create DF for biodiversity estimates -- drop species that have very low replication, so kick out all cilliate, nematomorph, leech, copepod observations (but lets keep in nematodes, cestodes, and acanths)
# Remove unwanted parasite types and drop their factor levels
df_biodiv_df <- drought_flood_df %>% 
  filter(!psite_type %in% c("nematomorph", "ciliate", "leech", "copepod")) %>% 
  droplevels()
# these are already absent from the drought_flood_df

# Get all unique combinations of grouping variables
group_combos <- unique(df_biodiv_df[, c("event", "ci", "psite_type", "fish_sp_x", "psite_spp_y")])

# Empty results data frame
jackknife_results <- data.frame(
  event = character(),
  ci = character(),
  psite_type = character(),
  fish_sp_x = character(),
  psite_spp_y = character(),
  jackknife_mean_richness = numeric(),
  total_psite_count = numeric(),
  stringsAsFactors = FALSE
)

# Loop over each combination
for (i in 1:nrow(group_combos)) {
  event <- group_combos$event[i]
  ci <- group_combos$ci[i]
  psite <- group_combos$psite_type[i]
  fish <- group_combos$fish_sp_x[i]
  rich <- group_combos$psite_spp_y[i]
  
  # Safe subsetting using which()
  sub_df <- df_biodiv_df[which(
    df_biodiv_df$event == event &
    df_biodiv_df$ci == ci &
    df_biodiv_df$psite_type == psite &
    df_biodiv_df$fish_sp_x == fish &
    df_biodiv_df$psite_spp_y == rich
  ), ]
  
  # Remove 0-counts
  sub_df <- sub_df[sub_df$psite_count != 0, ]
  
  # Skip if no data
  if (nrow(sub_df) == 0) next
  
  # Unique samples
  sample_ids <- unique(sub_df$x)
  richness_values <- numeric(length(sample_ids))
  
  for (j in seq_along(sample_ids)) {
    id_to_leave_out <- sample_ids[j]
    df_minus_one <- sub_df[sub_df$x != id_to_leave_out, ]
    richness_values[j] <- length(unique(df_minus_one$psite_spp_x))
  }
  
  total_count <- sum(sub_df$psite_count, na.rm = TRUE)
  
  jackknife_results <- rbind(jackknife_results, data.frame(
    event = event,
    ci = ci,
    psite_type = as.character(psite), 
    fish_sp_x = as.character(fish),
    psite_spp_y = as.character(rich),
    jackknife_mean_richness = mean(richness_values),
    total_psite_count = total_count
  ))
}

# Remove incomplete rows
jackknife_results <- jackknife_results[complete.cases(jackknife_results), ]


# create plots for the variety of combinations of factors we want to investigate

# event
ggplot(jackknife_results,
       aes(x = psite_type, y = jackknife_mean_richness, fill = psite_type)) +
  geom_col(position = "dodge") +
  facet_wrap(~ event) +
  theme_minimal(base_size = 12) +
  labs(
    x = "Fish species",
    y = "Mean Parasite Richness (Jackknife)",
    fill = "Parasite type"
  ) + connor_theme
```

## Plot jacknife estimates
```{r, eval=FALSE}
ggplot(jackknife_results,
       aes(x = psite_type, y = jackknife_mean_richness, fill = psite_spp_y)) +
  geom_col(position = "dodge") +
  facet_wrap(timing ~ event) +
  theme_minimal(base_size = 12) +
  labs(
    x = "Fish species",
    y = "Mean Parasite Richness (Jackknife)",
    fill = "Parasite type"
  ) + connor_theme 

# trim df to be one df for each type of parasite
acanths <- jackknife_results %>% 
  filter(psite_type %in% c("acanthocephalan")) %>% 
  droplevels()

jk_a <- ggplot(jackknife_results,
       aes(x = timing, y = jackknife_mean_richness, fill = psite_spp_y)) +
  geom_col(position = "dodge") +
  facet_wrap(~ event) +
  theme_minimal(base_size = 12) +
  labs(
    x = "Fish species",
    y = "Mean Parasite Richness (Jackknife)",
    fill = "Parasite type"
  ) + connor_theme + guides(fill = "none")


nems <- jackknife_results %>% 
  filter(psite_type %in% c("nematode")) %>% 
  droplevels()

jk_n <- ggplot(nems,
       aes(x = timing, y = jackknife_mean_richness, fill = psite_spp_y)) +
  geom_col(position = "dodge") +
  facet_wrap(~ event) +
  theme_minimal(base_size = 12) +
  labs(
    x = "Fish species",
    y = "Mean Parasite Richness (Jackknife)",
    fill = "Parasite type"
  ) + connor_theme + guides(fill = "none")

cest <- jackknife_results %>% 
  filter(psite_type %in% c("cestode")) %>% 
  droplevels()

jk_c <- ggplot(cest,
       aes(x = timing, y = jackknife_mean_richness, fill = psite_spp_y)) +
  geom_col(position = "dodge") +
  facet_wrap(~ event) +
  theme_minimal(base_size = 12) +
  labs(
    x = "Fish species",
    y = "Mean Parasite Richness (Jackknife)",
    fill = "Parasite type"
  ) + connor_theme + guides(fill = "none")

trem <- jackknife_results %>% 
  filter(psite_type %in% c("trematode")) %>% 
  droplevels() 

jk_t <- ggplot(trem,
       aes(x = timing, y = jackknife_mean_richness, fill = psite_spp_y)) +
  geom_col(position = "dodge") +
  facet_wrap(~ event) +
  theme_minimal(base_size = 12) +
  labs(
    x = "Fish species",
    y = "Mean Parasite Richness (Jackknife)",
    fill = "Parasite type"
  ) + connor_theme + guides(fill = "none")

trem_meta <- jackknife_results %>% 
  filter(psite_type %in% c("trematode_metacercaria")) %>% 
  droplevels()

jk_tm <- ggplot(trem_meta,
       aes(x = timing, y = jackknife_mean_richness, fill = psite_spp_y)) +
  geom_col(position = "dodge") +
  facet_wrap(~ event) +
  theme_minimal(base_size = 12) +
  labs(
    x = "Fish species",
    y = "Mean Parasite Richness (Jackknife)",
    fill = "Parasite type"
  ) + connor_theme + guides(fill = "none")

mono <- jackknife_results %>% 
  filter(psite_type %in% c("monogenean")) %>% 
  droplevels()

jk_mono <- ggplot(mono,
       aes(x = timing, y = jackknife_mean_richness, fill = psite_spp_y)) +
  geom_col(position = "dodge") +
  facet_wrap(~ event) +
  theme_minimal(base_size = 12) +
  labs(
    x = "Fish species",
    y = "Mean Parasite Richness (Jackknife)",
    fill = "Parasite type"
  ) + connor_theme + guides(fill = "none")

myxo <- jackknife_results %>% 
  filter(psite_type %in% c("myxozoan")) %>% 
  droplevels()

jk_myxo <- ggplot(myxo,
       aes(x = timing, y = jackknife_mean_richness, fill = psite_spp_y)) +
  geom_col(position = "dodge") +
  facet_wrap(~ event) +
  theme_minimal(base_size = 12) +
  labs(
    x = "Fish species",
    y = "Mean Parasite Richness (Jackknife)",
    fill = "Parasite type"
  ) + connor_theme + guides(fill = "none")

# combine all plots into one
biodiv_plot_hurricane <- ggarrange(jk_a, jk_n, jk_c, jk_t, jk_tm, jk_mono, jk_myxo, common.legend = FALSE, legend = "bottom", labels = c("A", "B", "C", "D", "E", "F", "G"))
plot(biodiv_plot_hurricane)

```

```



What about overlaying drought flood with hurricane occurances? maybe on some sort of map?
