---
title: "Drought and Flood: NOLA CAREER Project"
author: "Connor Whalen"
date: "2025-02-18"
output:
  html_document:
    theme: readable
    highlight: textmate
    toc: true
    toc_float: true
    toc_depth: 3
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Introduction
This file contains all code pertaining to the CAREER project in NOLA's drought and flood analysis. 

# Setup
#### Install packages.
```{r package install, eval=FALSE, echo=FALSE}
install.packages("tidyverse")
install.packages("janitor")
install.packages("ggeffects")
install.packages("ggpubr")
install.packages("glmmTMB")
install.packages("devtools")
devtools::install_github("johannesbjork/LaCroixColoR")
install.packages("patchwork")
install.packages("ggh4x")
install.packages("vistime")
install.packages("DHARMa")
```

#### Load packages.
```{r package load, echo=FALSE}
library(ggpubr)
library(ggeffects)
library(tidyverse)
library(readr)
library(dbplyr)
library(lubridate)
library(ggplot2)
library(stringr)
library(glmmTMB)
#library(lmerTest)
library(lme4)
source("~/Desktop/UW/Dissertation/theme_ctmt.R")
library(LaCroixColoR)
library(patchwork)
library(ggh4x)
library(vistime)
library(car)
library(DHARMa)
```
#### Load full datasets (parasites collected and NOAA SPI precipitation data) and prep data for analysis
```{r datasets and dataframe loading and general df clean and prep for analysis, echo=FALSE}
full_data <- read.csv("~/Desktop/UW/TUBRI/data/processed/Full_dataset_physical_2024.09.25.csv") %>% 
  janitor::clean_names()

SPI_data <- read.csv("~/Desktop/UW/Chapter1 NOLA/datasets/SPI data - Sheet1.csv") %>% 
  janitor::clean_names()

# Prep all data for analysis, inclduing assigning parasite type categories, abundance and prevalence counts, and establishing correct column date structure
full_data <- full_data %>%
  mutate(psite_type = case_when(
    str_detect(fish_psite_combo, "ACAN") ~ "acanthocephalan",
    str_detect(fish_psite_combo, "ACANTH") ~ "acanthocephalan",
    str_detect(fish_psite_combo, "CEST") ~ "cestode",
    str_detect(fish_psite_combo, "CILI") ~ "ciliate",
    str_detect(fish_psite_combo, "COPE") ~ "copepod",
    str_detect(fish_psite_combo, "LEECH") ~ "leech",
    str_detect(fish_psite_combo, "META") ~ "trematode_metacercaria",
    str_detect(fish_psite_combo, "MONO") ~ "monogenean",
    str_detect(fish_psite_combo, "MYX") ~ "myxozoan",
    str_detect(fish_psite_combo, "MYXO") ~ "myxozoan",
    str_detect(fish_psite_combo, "NEM") ~ "nematode",
    str_detect(fish_psite_combo, "NMORPH") ~ "nematomorph",
    str_detect(fish_psite_combo, "TREM") ~ "trematode",
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(psite_abundance = case_when(
    str_detect(fish_psite_combo, "ACAN") ~ psite_count,
    str_detect(fish_psite_combo, "ACANTH") ~ psite_count,
    str_detect(fish_psite_combo, "CEST") ~ psite_count,
    str_detect(fish_psite_combo, "CILI") ~ psite_count,
    str_detect(fish_psite_combo, "COPE") ~ psite_count,
    str_detect(fish_psite_combo, "LEECH") ~ psite_count,
    str_detect(fish_psite_combo, "META") ~ psite_count,
    str_detect(fish_psite_combo, "MONO") ~ psite_count,
    str_detect(fish_psite_combo, "NEM") ~ psite_count,
    str_detect(fish_psite_combo, "NMORPH") ~ psite_count,
    str_detect(fish_psite_combo, "TREM") ~ psite_count,
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(psite_prevalence = case_when(
    str_detect(fish_psite_combo, "MYX") ~ psite_count,
    str_detect(fish_psite_combo, "MYXO") ~ psite_count,
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(date = as.Date(paste(year_collected, month_collected, day_collected, sep = "-"))) 

SPI_data <- SPI_data %>% 
  mutate(date = as.Date(date))

full_data <- full_data %>% 
  mutate(psite_prevalence = as.numeric(psite_prevalence))

full_data <- full_data %>% 
  left_join(SPI_data, by = "date")

# view(table(full_data$category))

## assign control and flood categories to the different SPI value categories 
# category = average = true control
# category = abnormally wet / dry = marginal control 
# category = exceptionally wet / dry = full drought/flood

full_data <- full_data %>%
  mutate(event = case_when(
    str_detect(category, "exceptionally wet") ~ "flood",
    str_detect(category, "extremely wet") ~ "flood",
    str_detect(category, "severely wet") ~ "flood",
    str_detect(category, "moderately wet") ~ "flood",
    str_detect(category, "exceptionally dry") ~ "drought",
    str_detect(category, "extremely dry") ~ "drought",
    str_detect(category, "severely dry") ~ "drought",
    str_detect(category, "moderately dry") ~ "drought",
    str_detect(category, "abnormally wet") ~ "control",
    str_detect(category, "abnormally dry") ~ "control",
    str_detect(category, "average") ~ "control", # there are no parasites collected in the "average" grouping
    TRUE ~ "marginal"
  )) %>% 
  mutate(event = as.factor(event)) %>% 
  mutate(category = as.factor(category)) %>% 
  mutate(psite_type = as.factor(psite_type))

```

## Data Prep and Cleaning
```{r filtering, eval = FALSE}
# check how many observations are in each category
table(full_data$psite_type)
# check how many of these are > 0 
full_data %>%
  filter(psite_abundance > 0) %>%
  count(psite_type)


# drop low replicate categories
drought_flood_df <- full_data %>%
  filter(psite_type %in% c("trematode", "trematode_metacercaria", "monogenean"))

# filter out all remaining NAs from the psite_abundance column
drought_flood_df <- drought_flood_df %>%
  filter(!is.na(psite_abundance))

#relevel to drop the non-used categories
drought_flood_df <- drought_flood_df %>%
  mutate(psite_type = factor(psite_type, 
                             levels = c("monogenean", "trematode", "trematode_metacercaria")))

# create new category for myxos
drought_flood_df_m <- full_data %>%
  filter(psite_type %in% c("myxozoan"))

# filter out all remaining NAs from the psite_abundance column
drought_flood_df_m <- drought_flood_df_m %>%
  filter(!is.na(psite_prevalence))

# filter each parasite type into their own df
dfam <- drought_flood_df %>% 
  filter(psite_type %in% c("monogenean"))
dfat <- drought_flood_df %>% 
  filter(psite_type %in% c("trematode"))
dfatm <- drought_flood_df %>% 
  filter(psite_type %in% c("trematode_metacercaria"))

save(drought_flood_df_m, file = "df_myxo.RData")
```

Visualization and checking of data frame.
```{r head}
head(drought_flood_df)
table(drought_flood_df$event)
```

# Estimating Biodiversity Changes
Jackknife estimates -- taken from the hurricane page, needs to be updated for drought and flood data 4/30
```{r}
# prep dataframe to include only data on biodiversity

hurricane_diveristy <- hurricane_df6 %>%
  select(x, psite_type, psite_count, event, timing, category, ci, psite_spp_x, fish_psite_combo) %>%
  mutate(psite_spp_id = as.numeric(factor(psite_spp_x))) %>% 
  filter(psite_count != 0)

# overall species before and after plus timing


# Get all unique combinations of event, timing, and ci
group_combos <- unique(hurricane_df6[, c("event", "timing", "ci")])

# Empty results data frame
jackknife_results <- data.frame(
  event = character(),
  timing = character(),
  ci = character(),
  jackknife_mean_richness = numeric(),
  total_psite_count = numeric(),
  stringsAsFactors = FALSE
)

# Loop over each event × timing × ci combo
for (i in 1:nrow(group_combos)) {
  e <- group_combos$event[i]
  t <- group_combos$timing[i]
  c <- group_combos$ci[i]
  
  # Subset data for this combination
  sub_df <- hurricane_df6[hurricane_df6$event == e &
                          hurricane_df6$timing == t &
                          hurricane_df6$ci == c, ]
  
  # Get unique sample IDs
  sample_ids <- unique(sub_df$x)
  
  richness_values <- numeric(length(sample_ids))
  
  # Leave-one-out loop for jackknife richness
  for (j in seq_along(sample_ids)) {
    id_to_leave_out <- sample_ids[j]
    
    df_minus_one <- sub_df[sub_df$x != id_to_leave_out, ]
    
    richness_values[j] <- length(unique(df_minus_one$psite_spp_x))
  }
  
  # Sum total parasite count in this group
  total_count <- sum(sub_df$psite_count, na.rm = TRUE)
  
  # Store results
  jackknife_results <- rbind(jackknife_results, data.frame(
    event = e,
    timing = t,
    ci = c,
    jackknife_mean_richness = mean(richness_values),
    total_psite_count = total_count
  ))
}






# prelim plot
ggplot(hurricane_diveristy,
       aes(x = psite_spp_id, y = psite_count, fill = timing)) + 
  geom_line() + facet_wrap(event ~ ci) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("") + 
  xlab("") + 
  scale_fill_manual(
  values = c("post" = "#F28A8A", "pre" = "#1BB6AF"))

```


# Models -- testing which model is the best fit for the data
## Abundance
### 3 parasite types
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom1, data = drought_flood_df)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df)

# nbinom2 log

nbinom2log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2, data = drought_flood_df)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df)

# nbinom12 log

nbinom12log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom12, data = drought_flood_df)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom1, data = drought_flood_df)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom2, data = drought_flood_df)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = drought_flood_df)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = drought_flood_df)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = drought_flood_df)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = drought_flood_df)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = drought_flood_df)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df)


# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()

# this model is the best fit

dfa_nbinom2log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2, data = drought_flood_df)

simulateResiduals(fittedModel = dfa_nbinom2log, plot = TRUE)
summary(dfa_nbinom2log)
plot(parameters(dfa_nbinom2log))
```

### Monogene Abundance
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1, data = dfam)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1(link = "sqrt"), data = dfam)

# nbinom2 log

nbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = dfam)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom2(link = "sqrt"), data = dfam)

# nbinom12 log

nbinom12log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12, data = dfam)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12(link = "sqrt"), data = dfam)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1, data = dfam)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1(link = "sqrt"), data = dfam)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2, data = dfam)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2(link = "sqrt"), data = dfam)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = dfam)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = dfam)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = dfam)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = dfam)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = dfam)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = dfam)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = dfam)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),  
                                family = truncated_nbinom1(link = "sqrt"), data = dfam)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = dfam)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),
                                family = truncated_nbinom2(link = "sqrt"), data = dfam)

# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()

# this is best model 
mono_final_df <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = dfam)

simulateResiduals(fittedModel = mono_final_df, plot = TRUE)
summary(mono_final_df)
plot(parameters(mono_final_df))


```

### Trematode Abundance
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1, data = dfat)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1(link = "sqrt"), data = dfat)

# nbinom2 log

nbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = dfat)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom2(link = "sqrt"), data = dfat)

# nbinom12 log

nbinom12log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12, data = dfat)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12(link = "sqrt"), data = dfat)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1, data = dfat)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1(link = "sqrt"), data = dfat)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2, data = dfat)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2(link = "sqrt"), data = dfat)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = dfat)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = dfat)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = dfat)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = dfat)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = dfat)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = dfat)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = dfat)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),  
                                family = truncated_nbinom1(link = "sqrt"), data = dfat)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = dfat)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),
                                family = truncated_nbinom2(link = "sqrt"), data = dfat)

# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()

# this is best model (none of them fit super well)
trem_final_df <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = dfat)

simulateResiduals(fittedModel = trem_final_df, plot = TRUE)
summary(trem_final_df)
plot(parameters(trem_final_df))


```


### Trematode Metacercaria Abundance
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1, data = dfatm)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1(link = "sqrt"), data = dfatm)

# nbinom2 log

nbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = dfatm)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom2(link = "sqrt"), data = dfatm)

# nbinom12 log

nbinom12log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12, data = dfatm)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12(link = "sqrt"), data = dfatm)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1, data = dfatm)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1(link = "sqrt"), data = dfatm)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2, data = dfatm)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2(link = "sqrt"), data = dfatm)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = dfatm)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = dfatm)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = dfatm)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = dfatm)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = dfatm)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = dfatm)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = dfatm)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),  
                                family = truncated_nbinom1(link = "sqrt"), data = dfatm)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = dfatm)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),
                                family = truncated_nbinom2(link = "sqrt"), data = dfatm)

# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()

# this is best model -- not the lowest AIC but the best fit of all parameters and isnt
meta_final_df <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1(link = "sqrt"), data = dfatm)


simulateResiduals(fittedModel = meta_final_df, plot = TRUE)
summary(meta_final_df)
plot(parameters(meta_final_df))
```

## Prevalence  
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1, data = drought_flood_df_m)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_m)

# nbinom2 log

nbinom2log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = drought_flood_df_m)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df_m)

# nbinom12 log

nbinom12log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom12, data = drought_flood_df_m)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom1, data = drought_flood_df_m)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom2, data = drought_flood_df_m)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df_m)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = drought_flood_df_m)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_m)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = drought_flood_df_m)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df_m)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = drought_flood_df_m)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = drought_flood_df_m)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = drought_flood_df_m)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df_m)


# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()

# this model is the best fit -- swapped 4/27

dfp_tnbinom2log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom2, data = drought_flood_df_m)


simulateResiduals(fittedModel = dfp_tnbinom2log, plot = TRUE)
summary(dfp_tnbinom2log)
plot(parameters(dfp_tnbinom2log))
```




# Final Models Summary
```{r}
# abundance 3 types
dfa_nbinom2log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2, data = drought_flood_df)

simulateResiduals(fittedModel = dfa_nbinom2log, plot = TRUE)
summary(dfa_nbinom2log)
plot(parameters(dfa_nbinom2log))

# prevalence -- DONT USE THIS ONE
dfp_tnbinom2log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom2, data = drought_flood_df_m)


simulateResiduals(fittedModel = dfp_tnbinom2log, plot = TRUE)
summary(dfp_tnbinom2log)
plot(parameters(dfp_tnbinom2log))


### USE THIS MODEL FOR PREVALENCE NOT THE TRUNCATED ONE - nbinom1sqrtoff
df_myxo <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_m)

simulateResiduals(fittedModel = df_myxo, plot = TRUE)
summary(df_myxo)
plot(parameters(df_myxo))


```

# PLOTS
Setup plot aesthetics
```{r}
# color palette -- hurricane = #CB87B4, control = #F4B95A, drought = #D84D16, flood = #1BB6AF
# trem = #c9ad79 , meta = #F66387 , mono = #A6E000 , myxo = #07c4c5
connor_theme <- theme(legend.position = "top", 
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 14),
        strip.background = element_rect(fill = NA, color = NA),
        panel.background = element_rect(fill = NA, color = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.spacing.x = unit(0, "lines"),
        panel.spacing.y = unit(0, "lines"),
        axis.text = element_text(size = 8, color = "grey30"),
        axis.ticks = element_line(size = 0.2, color = "darkgrey"))
```


Trematode abundance was positively modulated by drought (estimate = 0.52793, p value = 0.04806). (A) Tremaode metacercaria were less abundant than other parasites at baseline conditions (estimate = -1.30291, p value = 0.03564), (A) but this relationship was modulated positively by both drought (estimate = 1.8602, p value < 0.001) and flood (estimate = 0.82453, p value = 0.00559). (A)
```{r}
df1a <- ggpredict(dfa_nbinom2log, terms = c("psite_type", "event"))
df1a <- df1a %>%
  rename(
    psite_type = x,
    estimate = predicted,
    se = std.error,
    lower = conf.low,
    upper = conf.high,
    event = group)

# add significance bars
meta_sig_df <- data.frame(
  group1 = c("control", "control", "control"),
  group2 = c("drought", "drought", "flood"),
  psite_type = c("trematode", "trematode_metacercaria", "trematode_metacercaria"),
  y.position = c(6, 7, 8), 
  p.value = c(0.04806, 0.0000000147, 0.00559) 
)

meta_sig_df <- meta_sig_df %>%
  mutate(
    stars = cut(p.value,
                breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                labels = c("***", "**", "*", "ns"))
  )

dodge_offset <- 0.16

meta_sig_df_dodged <- meta_sig_df %>%
  filter(psite_type == "trematode_metacercaria") %>%
  mutate(
    xmin = as.numeric(factor(group1, levels = c("control", "drought", "flood"))) + dodge_offset,
    xmax = as.numeric(factor(group2, levels = c("control", "drought", "flood"))) + dodge_offset
  )

meta_sig_df_nododge <- meta_sig_df %>%
  filter(psite_type == "trematode") %>%
  mutate(
    xmin = as.numeric(factor(group1, levels = c("control", "drought", "flood"))),
    xmax = as.numeric(factor(group2, levels = c("control", "drought", "flood")))
  )

# plot df1a
df1ap <- ggplot(df1a,
       aes(x = event, y = estimate)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, group = psite_type),
                width = 0.05,
                position = position_dodge(width = 0.5)) +
  geom_line(aes(group = psite_type, linetype = psite_type),
            position = position_dodge(width = 0.5)) +
  geom_point(aes(fill = psite_type, group = psite_type),
             pch = 21, size = 5,
             position = position_dodge(width = 0.5)) +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79", "myxozoan" = "#07c3c5")) + 
    scale_y_continuous(limits = c(0, 8), breaks = seq(0, 8, by = 2)) + 
  labs(x = "Event", y = "Estimate", fill = "Parasite Type", linetype = "Parasite Type") +
  connor_theme  + 
  stat_pvalue_manual(
    data = meta_sig_df_dodged,
    label = "stars",
    xmin = "xmin",
    xmax = "xmax",
    y.position = "y.position",
    tip.length = 0.01
  ) +
  stat_pvalue_manual(
    data = meta_sig_df_nododge,
    label = "stars",
    xmin = "xmin",
    xmax = "xmax",
    y.position = "y.position",
    tip.length = 0.01
  )


#### prevalence plot
# Myxozoans were more prevalent at baseline conditions compared to under drought or flood (estimate = -6.0905, p value < 0.001). Myxozoan parasites were more marginally significantly abundant in the impact category (estimate =0.5444, p value = 0.0875).  
df1p <- ggpredict(df_myxo, terms = c("event", "ci"))

df1p <- df1p %>%
  rename(
    event = x,
    estimate = predicted,
    se = std.error,
    lower = conf.low,
    upper = conf.high,
    ci = group)

df1pp <- ggplot(df1p,
       aes(x = ci, y = estimate)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, group = event),
                width = 0.05,
                position = position_dodge(width = 0.5)) +
  geom_line(aes(group = event, linetype = event),
            position = position_dodge(width = 0.5)) +
  geom_point(aes(fill = event, group = event),
             pch = 21, size = 5,
             position = position_dodge(width = 0.5)) +
  scale_fill_manual(values = c("drought" = "#D84D16", "flood" = "#1BB6AF","control" = "#F4B95A", "impact" = "#FF69B4")) +
  labs(x = "CI Category", y = "Estimate", fill = "Event", linetype = "Event") +
  connor_theme

df_plot <- ggarrange(df1ap, df1pp, common.legend = FALSE, legend = "bottom", labels = c("A", "B"))
plot(df_plot)

## still need to plot the ZIs 
```


