---
title: "Drought and Flood: NOLA CAREER Project"
author: "Connor Whalen"
date: "2025-02-18"
output:
  html_document:
    theme: readable
    highlight: textmate
    toc: true
    toc_float: true
    toc_depth: 3
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


# Introduction
This file contains all code pertaining to the CAREER project in NOLA's drought and flood analysis. 

# Setup
#### Install packages.
```{r package install, eval=FALSE, echo=FALSE}
install.packages("tidyverse")
install.packages("janitor")
install.packages("ggeffects")
install.packages("ggpubr")
install.packages("glmmTMB")
install.packages("devtools")
devtools::install_github("johannesbjork/LaCroixColoR")
install.packages("patchwork")
install.packages("ggh4x")
install.packages("vistime")
install.packages("DHARMa")
```

#### Load packages.
```{r package load, echo=FALSE}
library(ggpubr)
library(ggeffects)
library(tidyverse)
library(readr)
library(dbplyr)
library(lubridate)
library(ggplot2)
library(stringr)
library(glmmTMB)
#library(lmerTest)
library(lme4)
source("~/Desktop/UW/Dissertation/theme_ctmt.R")
library(LaCroixColoR)
library(patchwork)
library(ggh4x)
library(vistime)
library(car)
library(DHARMa)
```
#### Load full datasets (parasites collected and NOAA SPI precipitation data) and prep data for analysis
```{r datasets and dataframe loading and general df clean and prep for analysis, echo=FALSE}
full_data <- read.csv("~/Desktop/UW/TUBRI/data/processed/Full_dataset_physical_2024.09.25.csv") %>% 
  janitor::clean_names()

SPI_data <- read.csv("~/Desktop/UW/Chapter1 NOLA/datasets/SPI data - Sheet1.csv") %>% 
  janitor::clean_names()

# Prep all data for analysis, inclduing assigning parasite type categories, abundance and prevalence counts, and establishing correct column date structure
full_data <- full_data %>%
  mutate(psite_type = case_when(
    str_detect(fish_psite_combo, "ACAN") ~ "acanthocephalan",
    str_detect(fish_psite_combo, "ACANTH") ~ "acanthocephalan",
    str_detect(fish_psite_combo, "CEST") ~ "cestode",
    str_detect(fish_psite_combo, "CILI") ~ "ciliate",
    str_detect(fish_psite_combo, "COPE") ~ "copepod",
    str_detect(fish_psite_combo, "LEECH") ~ "leech",
    str_detect(fish_psite_combo, "META") ~ "trematode_metacercaria",
    str_detect(fish_psite_combo, "MONO") ~ "monogenean",
    str_detect(fish_psite_combo, "MYX") ~ "myxozoan",
    str_detect(fish_psite_combo, "MYXO") ~ "myxozoan",
    str_detect(fish_psite_combo, "NEM") ~ "nematode",
    str_detect(fish_psite_combo, "NMORPH") ~ "nematomorph",
    str_detect(fish_psite_combo, "TREM") ~ "trematode",
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(psite_abundance = case_when(
    str_detect(fish_psite_combo, "ACAN") ~ psite_count,
    str_detect(fish_psite_combo, "ACANTH") ~ psite_count,
    str_detect(fish_psite_combo, "CEST") ~ psite_count,
    str_detect(fish_psite_combo, "CILI") ~ psite_count,
    str_detect(fish_psite_combo, "COPE") ~ psite_count,
    str_detect(fish_psite_combo, "LEECH") ~ psite_count,
    str_detect(fish_psite_combo, "META") ~ psite_count,
    str_detect(fish_psite_combo, "MONO") ~ psite_count,
    str_detect(fish_psite_combo, "NEM") ~ psite_count,
    str_detect(fish_psite_combo, "NMORPH") ~ psite_count,
    str_detect(fish_psite_combo, "TREM") ~ psite_count,
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(psite_prevalence = case_when(
    str_detect(fish_psite_combo, "MYX") ~ psite_count,
    str_detect(fish_psite_combo, "MYXO") ~ psite_count,
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(date = as.Date(paste(year_collected, month_collected, day_collected, sep = "-"))) 

SPI_data <- SPI_data %>% 
  mutate(date = as.Date(date))

full_data <- full_data %>% 
  mutate(psite_prevalence = as.numeric(psite_prevalence))

full_data <- full_data %>% 
  left_join(SPI_data, by = "date")

# view(table(full_data$category))

## assign control and flood categories to the different SPI value categories 
# category = average = true control
# category = abnormally wet / dry = marginal control 
# category = exceptionally wet / dry = full drought/flood

full_data <- full_data %>%
  mutate(event = case_when(
    str_detect(category, "exceptionally wet") ~ "flood",
    str_detect(category, "extremely wet") ~ "flood",
    str_detect(category, "severely wet") ~ "flood",
    str_detect(category, "moderately wet") ~ "flood",
    str_detect(category, "exceptionally dry") ~ "drought",
    str_detect(category, "extremely dry") ~ "drought",
    str_detect(category, "severely dry") ~ "drought",
    str_detect(category, "moderately dry") ~ "drought",
    str_detect(category, "abnormally wet") ~ "control",
    str_detect(category, "abnormally dry") ~ "control",
    str_detect(category, "average") ~ "control", # there are no parasites collected in the "average" grouping
    TRUE ~ "marginal"
  )) %>% 
  mutate(event = as.factor(event)) %>% 
  mutate(category = as.factor(category)) %>% 
  mutate(psite_type = as.factor(psite_type))

table(full_data$event)

```

# Drought / Flood analysis and data prepping
### Controls
Find the average date of a hurricane, so that we can identify when the average hurricane starts and stops and how long it lasts -- this will be used to assign a period of time to our hurricane controls. [This code was used to identify these information, but no longer needs to be run for the analysis to work]. Then, pick out the years in which there was no hurricane, so that we can identify which years to assign as control in our hurricane analysis. 
[These are dates of average drought as it pertains to the initial analysis plan (the one that mirrors the hurricane analysis plan) -- not currently in use.]
```{r dates for controls and average dates, echo=FALSE, eval=FALSE}
# 1963, 1964, 1966, 1970, 1971, 1974, 1975, 1978, 1980, 1982, 1983, 1984, 1987, 1988, 1989, 1990, 1991, 1992, 1993, 1994, 1996, 1997, 1998, 1999, 2001, 2002, 2003, 2004

# select years to represent as controls: alternate years to turn 28 non event years in 14 to match # of years in events - make sure no controls overlap with events (+ before and after)
# 1963, 1988, 1989, 1990, 1991, 1992, 1993, 1996, 1997, 2002, 2003, 2004

average_d <- drought_flood_df %>%
  filter(str_detect(ewe_type, "drought")) %>%
  mutate(
    month = month(date),
    day = day(date)
  ) %>%
  summarise(
    average_month = mean(month),
    average_day = mean(day)
  )

 # average drought occurs on 6/17 of each year

average_f <- drought_flood_df %>%
  filter(str_detect(ewe_type, "flood")) %>%
  mutate(
    month = month(date),
    day = day(date)
  ) %>%
  summarise(
    average_month = mean(month),
    average_day = mean(day)
  )

 # average flood occurs on 7/17 of each year

# find average duration of each event

# Define date ranges for events
drought_events <- data.frame(
  start_date = as.Date(c("1967-01-01", "1976-01-01", "1981-01-01", 
                         "1985-01-01", "2000-01-01")),
  end_date = as.Date(c("1969-01-01", "1978-01-01", "1982-01-01", 
                       "1987-01-01", "2001-01-01"))
)

flood_events <- data.frame(
  start_date = as.Date(c("1965-08-27", "1972-12-01", "1979-04-01", "1995-05-08")),
  end_date = as.Date(c("1965-09-12", "1973-06-01", "1979-05-01", "1995-05-10"))
)

# Calculate durations of each event
drought_events$duration <- as.numeric(drought_events$end_date - drought_events$start_date)
flood_events$duration <- as.numeric(flood_events$end_date - flood_events$start_date)

# Calculate the average duration
average_duration_d <- mean(drought_events$duration)
average_duration_f <- mean(flood_events$duration)

# Print result
average_duration_d
 # 584 days -- 1 year, 6 months

average_duration_f
 # 57 days -- 2 months, 27 days
```

Add actual drought/flood timeline parameters for 6 month (6 month meaning a buffer period of 6 months before a drought/flood [denoted as pre] and 6 months after a drought/flood [denoted post]). These dates for drought/flood occurrence are taken from the [NOAA flooding website](https://www.weather.gov/safety/flood-states-la#) and the CAREER proposal from the Wood Lab, and represent all drought/flood events that occurred near the Pearl River in Louisiana across the sampling period. [This is the old/original analysis the same as hurricanes, but we are going to use the alternate analysis method of the matched SPI data instead -- not currently in use.] 
```{r drought/flood 6 month (old), echo=FALSE, eval = FALSE}
# create drought/flood dataset
drought_flood_df <- full_data %>% 
  mutate(ewe_type = case_when(
    date >= as.Date("1966-06-01") & date <= as.Date("1966-12-31") ~ "pre_drought",
    date >= as.Date("1967-01-01") & date <= as.Date("1970-01-01") ~ "drought",
    date >= as.Date("1970-01-02") & date <= as.Date("1970-06-01") ~ "post_drought",
    date >= as.Date("1975-06-01") & date <= as.Date("1975-12-31") ~ "pre_drought",
    date >= as.Date("1976-01-01") & date <= as.Date("1978-01-01") ~ "drought",
    date >= as.Date("1978-01-02") & date <= as.Date("1978-06-01") ~ "post_drought",
    date >= as.Date("1980-06-01") & date <= as.Date("1980-12-31") ~ "pre_drought",
    date >= as.Date("1981-01-01") & date <= as.Date("1982-01-01") ~ "drought",
    date >= as.Date("1982-01-02") & date <= as.Date("1982-06-01") ~ "post_drought",
    date >= as.Date("1984-06-01") & date <= as.Date("1984-12-31") ~ "pre_drought",
    date >= as.Date("1985-01-01") & date <= as.Date("1987-01-01") ~ "drought",
    date >= as.Date("1987-01-02") & date <= as.Date("1987-06-01") ~ "post_drought",
    date >= as.Date("1999-06-01") & date <= as.Date("1999-12-31") ~ "pre_drought",
    date >= as.Date("2000-01-01") & date <= as.Date("2001-01-01") ~ "drought",
    date >= as.Date("2001-01-02") & date <= as.Date("2001-06-02") ~ "post_drought",
    date >= as.Date("1965-02-26") & date <= as.Date("1965-08-26") ~ "pre_flood",
    date >= as.Date("1965-08-27") & date <= as.Date("1965-09-12") ~ "flood",
    date >= as.Date("1965-09-13") & date <= as.Date("1966-03-13") ~ "post_flood",
    date >= as.Date("1972-05-01") & date <= as.Date("1972-11-30") ~ "pre_flood",
    date >= as.Date("1972-12-01") & date <= as.Date("1973-06-01") ~ "flood",
    date >= as.Date("1973-06-02") & date <= as.Date("1973-12-02") ~ "post_flood",
    date >= as.Date("1978-10-01") & date <= as.Date("1978-03-31") ~ "pre_flood",
    date >= as.Date("1979-04-01") & date <= as.Date("1979-05-01") ~ "flood",
    date >= as.Date("1979-05-02") & date <= as.Date("1979-11-02") ~ "post_flood",
    date >= as.Date("1994-11-07") & date <= as.Date("1995-05-07") ~ "pre_flood",
    date >= as.Date("1995-05-08") & date <= as.Date("1995-05-10") ~ "flood",
    date >= as.Date("1995-05-11") & date <= as.Date("1995-11-11") ~ "post_flood",
    TRUE ~ "no event"
  ))

# create controls for the same dataset -- non events
# only calculated using the drought timeframe, because it encompasses the flood timeframe in it
drought_flood_df <- drought_flood_df %>% 
  mutate(control = case_when(
    date >= as.Date("1963-01-15") & date <= as.Date("1963-06-16") ~ "pre_control",
    date >= as.Date("1963-06-17") & date <= as.Date("1963-12-17") ~ "control",
    date >= as.Date("1964-12-18") & date <= as.Date("1964-06-18") ~ "post_control",
    date >= as.Date("1988-01-15") & date <= as.Date("1988-06-16") ~ "pre_control",
    date >= as.Date("1988-06-17") & date <= as.Date("1988-12-17") ~ "control",
    date >= as.Date("1988-12-18") & date <= as.Date("1989-06-18") ~ "post_control",
    date >= as.Date("1989-01-15") & date <= as.Date("1989-06-16") ~ "pre_control",
    date >= as.Date("1989-06-17") & date <= as.Date("1989-12-17") ~ "control",
    date >= as.Date("1989-12-18") & date <= as.Date("1990-06-18") ~ "post_control",
    date >= as.Date("1990-01-15") & date <= as.Date("1990-06-16") ~ "pre_control",
    date >= as.Date("1990-06-17") & date <= as.Date("1990-12-17") ~ "control",
    date >= as.Date("1990-12-18") & date <= as.Date("1991-06-18") ~ "post_control",
    date >= as.Date("1991-01-15") & date <= as.Date("1991-06-16") ~ "pre_control",
    date >= as.Date("1991-06-17") & date <= as.Date("1991-12-17") ~ "control",
    date >= as.Date("1991-12-18") & date <= as.Date("1992-06-18") ~ "post_control",
    date >= as.Date("1992-01-15") & date <= as.Date("1992-06-16") ~ "pre_control",
    date >= as.Date("1992-06-17") & date <= as.Date("1992-12-17") ~ "control",
    date >= as.Date("1992-12-18") & date <= as.Date("1993-06-18") ~ "post_control",
    date >= as.Date("1993-01-15") & date <= as.Date("1993-06-16") ~ "pre_control",
    date >= as.Date("1993-06-17") & date <= as.Date("1993-12-17") ~ "control",
    date >= as.Date("1993-12-18") & date <= as.Date("1994-06-18") ~ "post_control",
    date >= as.Date("1996-01-15") & date <= as.Date("1996-06-16") ~ "pre_control",
    date >= as.Date("1996-06-17") & date <= as.Date("1996-12-17") ~ "control",
    date >= as.Date("1996-12-18") & date <= as.Date("1997-06-18") ~ "post_control",
    date >= as.Date("1997-01-15") & date <= as.Date("1997-06-16") ~ "pre_control",
    date >= as.Date("1997-06-17") & date <= as.Date("1997-12-17") ~ "control",
    date >= as.Date("1997-12-18") & date <= as.Date("1998-06-18") ~ "post_control",
    date >= as.Date("2002-01-15") & date <= as.Date("2002-06-16") ~ "pre_control",
    date >= as.Date("2002-06-17") & date <= as.Date("2002-12-17") ~ "control",
    date >= as.Date("2002-12-18") & date <= as.Date("2003-06-18") ~ "post_control",
    date >= as.Date("2003-01-15") & date <= as.Date("2003-06-16") ~ "pre_control",
    date >= as.Date("2003-06-17") & date <= as.Date("2003-12-17") ~ "control",
    date >= as.Date("2003-12-18") & date <= as.Date("2004-06-18") ~ "post_control",
    date >= as.Date("2004-01-15") & date <= as.Date("2004-06-16") ~ "pre_control",
    date >= as.Date("2004-06-17") & date <= as.Date("2004-12-17") ~ "control",
    date >= as.Date("2004-12-18") & date <= as.Date("2005-06-18") ~ "post_control",
    TRUE ~ "no event"
  ))

drought_flood_df <- drought_flood_df %>% 
  mutate(event = case_when(
    ewe_type == "drought" ~ "drought",
    ewe_type == "flood" ~ "flood",
    ewe_type == "pre_drought" ~ "drought",
    ewe_type == "pre_flood" ~ "flood",
    ewe_type == "post_drought" ~ "drought",
    ewe_type == "post_flood" ~ "flood",
    ewe_type == "no event" & control == "pre_control" ~ "control",
    ewe_type == "no event" & control == "post_control" ~ "control",
    ewe_type == "no event" & control == "control" ~ "control",
    TRUE ~ "NA"
  )) %>%
  filter(!str_detect(event, "NA")) 

drought_flood_df <- drought_flood_df %>% 
  mutate(timing = case_when(
    ewe_type == "pre_drought" ~ "pre",
    ewe_type == "post_drought" ~ "post",    
    ewe_type == "pre_flood" ~ "pre",
    ewe_type == "post_flood" ~ "post",
    control == "pre_control" ~ "pre",
    control == "post_control" ~ "post",
    ewe_type == "drought" & event == "drought" ~ "during_drought",
    ewe_type == "flood" & event == "flood" ~ "during_flood",
    control == "control" & event == "control" ~ "during_control",
    TRUE ~ "NA"
  )) %>%
  filter(!str_detect(timing, "NA")) 

drought_flood_df <- drought_flood_df %>%
  mutate(timing = factor(timing, levels = c("pre", "post", "during_control", "during_drought", "during_flood"))) %>%
  mutate(timing = relevel(timing, ref = "pre"))

df_table <- table(drought_flood_df$timing)
df_table <- table(drought_flood_df$event)
# view(df_table)

```

Create a new df that only has parasite types that have high replication in the dataset [remove nematomorph, leech, cilliate, and myxozoan (since myxozoans go into a different type of analysis)]
```{r filtering, eval = FALSE}
# drop low replicate categories
drought_flood_df <- full_data %>%
  filter(psite_type %in% c("trematode", "trematode_metacercaria", "monogenean"))

# filter out all remaining NAs from the psite_abundance column
drought_flood_df <- drought_flood_df %>%
  filter(!is.na(psite_abundance))

# create new category for myxos
drought_flood_df_m <- full_data %>%
  filter(psite_type %in% c("myxozoan"))

# filter out all remaining NAs from the psite_abundance column
drought_flood_df_m <- drought_flood_df_m %>%
  filter(!is.na(psite_prevalence))
```

Visualization and checking of data frame.
```{r head}
head(drought_flood_df)
table(drought_flood_df$event)
```

# Plots
Create color palette and assign faceting labels.
```{r color palette and facet labels, echo=FALSE}
lacroix_palettes_list <- LaCroixColoR::lacroix_palettes

my_pal <- lacroix_palette("Pamplemousse", n = 5, type = "continuous")

parasite_order <- c(
  "trematode", "trematode_metacercaria", "myxozoan", "monogenean", "ciliate",
  "nematode", "acanthocephalan", "cestode", "copepod", "nematomorph"
)

parasite_labels <- c(
  "trematode" = "Trematode",
  "trematode_metacercaria" = "Metacercaria",
  "myxozoan" = "Myxozoan",
  "monogenean" = "Monogenean",
  "ciliate" = "Ciliate",
  "nematode" = "Nematode",
  "cestode" = "Cestode",
  "acanthocephalan" = "Acanthocephalan",
  "copepod" = "Copepod", 
  "nematomorph" = "Nematomorph"
)


storm_order <- c("five", "four", "three", "two", "one", "ts", "control")

storm_labels <- c(
  "five" = "5",
  "four" = "4",
  "three" = "3",
  "two" = "2",
  "one" = "1",
  "ts" = "TS", 
  "no event" = "control"
)

season_order <- c(
  "winter", "spring", "summer", "fall"
)

season_labels <- c(
  "winter" = "Winter",
  "spring" = "Spring", 
  "summer" = "Summer", 
  "fall" = "Fall"
)

timing_order <- c(
  "pre", "during", "post"
)

timing_labels <- c(
  "pre" = "Pre",
  "post" = "Post", 
  "control" = "During",
  "flood" = "During", 
  "drought" = "During"
)

event_labels <- c(
  "drought" = "drought", 
  "flood" = "flood"
)

```
Mutate the drought/flood dataset so that the total sum of each type of parasite can be plotted:
```{r drought/flood sum to plot all parasites added together and scale to mean, echo=FALSE, eval=FALSE}
drought_flood_df_sum <- drought_flood_df %>%
  group_by(psite_type, year_collected, event, timing, drought_flood, category) %>%
  summarize(total_psite_count = sum(psite_count, na.rm = TRUE), .groups = "drop") %>% 
  filter(total_psite_count != "0") %>%
  filter(!is.na(psite_type), 
         psite_type != "leech", 
         psite_type != "nematomorph")

drought_flood_df_sum <- drought_flood_df_sum %>%
    mutate(psite_type = fct_relevel(psite_type, parasite_order))

drought_flood_df_sum <- drought_flood_df_sum %>%
    mutate(season = fct_relevel(season, season_order))

drought_flood_df_sum <- drought_flood_df_sum %>%
    mutate(timing = fct_relevel(timing, timing_order))

# including zeroes
drought_flood_df_sum2 <- drought_flood_df %>%
  group_by(psite_type, year_collected, season, event, timing, drought_flood, category) %>%
  summarize(total_psite_count = sum(psite_count, na.rm = TRUE), .groups = "drop") %>%
  filter(!is.na(psite_type), 
         psite_type != "leech")

drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
    mutate(psite_type = fct_relevel(psite_type, parasite_order))

drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
    mutate(season = fct_relevel(season, season_order))

drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
    mutate(timing = fct_relevel(timing, timing_order))

# scale to mean -- should probably update this parameter
sum(drought_flood_df_sum2$total_psite_count, na.rm = TRUE)
28842/195 # average rate of parasitism across all observations is 147.9077
# in this case, each categorical 0 is counted only once, so the sum of each category includes summing all the zeroes but if there is only zeroes in a category, then those will show up as zero

drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
  mutate(relative_count = total_psite_count - 148)
```
Various plots.
```{r various plots, echo=FALSE, eval=FALSE}
ggplot(drought_flood_df_sum,
       aes(x = year_collected, y = drought_flood, fill = event)) + 
  geom_col(position = "dodge") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("") + 
  xlab("") + 
  scale_fill_manual(
  values = c("drought" = "#F28A8A", "flood" = "#1BB6AF"), 
  name = "",
  labels = timing_labels) 

######

ggplot(full_data,
       aes(x = year_collected, y = drought_minus_flood)) + 
  geom_col(position = "dodge") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("") + 
  xlab("")

ggplot(full_data,
       aes(x = drought_minus_flood, y = psite_abundance)) + 
  geom_bin_2d() +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("") + 
  xlab("")

custom_y_t3 <- list(
  scale_y_continuous(limits = c(0, 3000), breaks = c(0, 1500, 3000)),
  scale_y_continuous(limits = c(0, 1200), breaks = c(0, 600, 1200)),
  scale_y_continuous(limits = c(0, 600), breaks = c(0, 300, 600)),
  scale_y_continuous(limits = c(0, 400), breaks = c(0, 200, 400)),
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100)),
  scale_y_continuous(limits = c(0, 50), breaks = c(0, 25, 50)),  
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 10, 20)),
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 5, 10)),
  scale_y_continuous(limits = c(0, 2), breaks = c(0, 1, 2))
)

# by parasite spp
ggplot(drought_flood_df_sum,
       aes(x = event, y = total_psite_count, fill = timing)) + 
  geom_col(position = "dodge") + 
  facet_wrap(~ psite_type, labeller = labeller(psite_type = parasite_labels), scales = "free_y") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF", "drought" = "#95C65C", "flood" = "#95C65C", "control" = "#95C65C"), 
  name = "",
  labels = timing_labels) 

## by just timing
ggplot(drought_flood_df_sum,
       aes(x = event, y = total_psite_count, fill = timing)) + 
  geom_col() + 
  facet_wrap(~ timing) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF", "drought" = "#95C65C", "flood" = "#95C65C", "control" = "#95C65C"), 
  name = "",
  labels = timing_labels) 

## by species??

## by relative count
ggplot(drought_flood_df_sum2,
       aes(x = event, y = relative_count, fill = timing)) + 
  geom_col(position = "dodge") + 
  facet_wrap(~ psite_type, labeller = labeller(psite_type = parasite_labels), scales = "free_y") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF", "drought" = "#95C65C", "flood" = "#95C65C", "control" = "#95C65C"), 
  name = "",
  labels = timing_labels) 


## include year of collection
ggplot(drought_flood_df_sum2,
       aes(x = year_collected, y = relative_count, fill = event)) + 
  geom_col() +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) + 
  geom_hline(yintercept = 0, color = "black") +
  ylab("Relative Parasite Count") + 
  xlab("Year Collected") + 
  scale_fill_manual(
    values = c("drought" = "#F28A8A", "flood" = "#1BB6AF", "control" = "#95C65C"), 
    name = "",
    labels = season_labels
  )

ggplot(drought_flood_df_sum,
       aes(x = event, y = total_psite_count, fill = event)) + 
  geom_col() +
  facet_wrap(~ timing) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("drought" = "#F28A8A", "flood" = "#1BB6AF", "control" = "#95C65C"), 
  name = "",
  labels = season_labels) 

facet_labels2 <- c(
  "drought" = "Drought",
  "flood" = "Flood"
)

ggplot(drought_flood_df,
       aes(x = season, y = psite_abundance, fill = ewe_type)) + 
  geom_boxplot() + facet_wrap(~ci) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "darkgrey"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines")
  ) +
  ylab("Parasite Abundance") + 
  xlab("Collection Date") +
  scale_fill_manual(values = my_pal[1:5], name = '')
```

# Models
## Drought/Flood count (abundance)
```{r Drought/Flood abundance}
summary(drought_flood_count <- glmmTMB(psite_abundance ~ event*psite_type + (total_length_mm|fish_sp_x/parasite_taxonomic_group) + (1|ci/catalog_number) + (1|year_collected/season) + (1|fish_sp_y/psite_spp_y), 
                          data = drought_flood_df, family = truncated_nbinom1, ziformula = ~ 1))
```
Create diagnostics.
```{r Drought/Flood abundance diagnostics}
# diagnostics
#Evaluate residuals
s = simulateResiduals(fittedModel = drought_flood_count, n = 250)
plot(s)

# other possible diagnostics
#df <- ggpredict(model, terms = "column[n=100]")
#plot(df)
#plot(df, show_data=TRUE)
```

#### Checking all model options
- run each type and then run dHarma 
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom1, data = drought_flood_df)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df)

# nbinom2 log

nbinom2log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2, data = drought_flood_df)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df)

# nbinom12 log

nbinom12log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom12, data = drought_flood_df)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom1, data = drought_flood_df)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom2, data = drought_flood_df)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = drought_flood_df)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = drought_flood_df)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = drought_flood_df)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = drought_flood_df)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = drought_flood_df)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df)

```

```{r}
summary(nbinom1log)
summary(nbinom1sqrt)
summary(nbinom2log)
summary(nbinom2sqrt)
summary(nbinom12log)
summary(nbinom12sqrt)
summary(tnbinom1log)
summary(tnbinom1sqrt)
summary(tnbinom2log)
summary(tnbinom12sqrt)
summary(nbinom1logoff)
summary(nbinom1sqrtoff)
summary(nbinom2logoff)
summary(nbinom2sqrtoff)
summary(nbinom12logoff)
summary(nbinom12sqrtoff)
summary(tnbinom1logoff)
summary(tnbinom1sqrtoff)
summary(tnbinom2logoff)
summary(tnbinom2sqrtoff)

simulateResiduals(fittedModel = nbinom1log, plot = TRUE)
simulateResiduals(fittedModel = nbinom1sqrt, plot = TRUE)
simulateResiduals(fittedModel = nbinom2log, plot = TRUE)
simulateResiduals(fittedModel = nbinom2sqrt, plot = TRUE)
simulateResiduals(fittedModel = nbinom12log, plot = TRUE)
simulateResiduals(fittedModel = nbinom12sqrt, plot = TRUE)
simulateResiduals(fittedModel = tnbinom1log, plot = TRUE)
simulateResiduals(fittedModel = tnbinom1sqrt, plot = TRUE)
simulateResiduals(fittedModel = tnbinom2log , plot = TRUE)
simulateResiduals(fittedModel = tnbinom12sqrt, plot = TRUE)
simulateResiduals(fittedModel = nbinom1logoff, plot = TRUE)
simulateResiduals(fittedModel = nbinom1sqrtoff, plot = TRUE)
simulateResiduals(fittedModel = nbinom2logoff, plot = TRUE)
simulateResiduals(fittedModel = nbinom2sqrtoff, plot = TRUE)
simulateResiduals(fittedModel = nbinom12logoff, plot = TRUE)
simulateResiduals(fittedModel = nbinom12sqrtoff, plot = TRUE)
simulateResiduals(fittedModel = tnbinom1logoff, plot = TRUE)
simulateResiduals(fittedModel = tnbinom1sqrtoff, plot = TRUE)
simulateResiduals(fittedModel = tnbinom2logoff, plot = TRUE)
simulateResiduals(fittedModel = tnbinom2sqrtoff, plot = TRUE)



# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()


# this model is the best fit
simulateResiduals(fittedModel = nbinom2log, plot = TRUE)
summary(nbinom2log)
plot(parameters(nbinom2log))

```





FROM ARIAL's CODE
```{r}

# check zero inflation
table(drought_flood_df$psite_abundance)
sum(drought_flood_df$psite_abundance > 0)
sum(drought_flood_df$psite_abundance < 1)

# check overdispertion likelyhood
mean(drought_flood_df$psite_abundance)
var(drought_flood_df$psite_abundance)

# check covariate levels:
levels(drought_flood_df$event)
levels(drought_flood_df$category)
levels(drought_flood_df$psite_type) # 

# try poisson model
drought_flood_df_pois <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                   (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo), 
                                family = truncated_poisson, data = drought_flood_df)

summary(drought_flood_df_pois)
plot(parameters(drought_flood_df_pois))

# check overdispersion parameter manually (X2/df.resid) Overdispersed > 1
sum(residuals(drought_flood_df_pois, type = "pearson")^2) / 12179 
# 104 = is overdispersed

# check residuals
simulateResiduals(fittedModel = drought_flood_df_pois, plot = TRUE)

# Chi2 Goodness of fit test (null hypothesis = model is correctly specified)  
X2 <- sum((drought_flood_df$psite_abundance - fitted(drought_flood_df_pois))^2 / fitted(drought_flood_df_pois))
df <- length(drought_flood_df$psite_abundance) - length(coef(drought_flood_df_pois))
pchisq(X2, df,lower.tail = FALSE)
# output is 0
# reject null- model not a good fit

# try negative binomial

drought_flood_df_nbin <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                   (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom2, data = drought_flood_df)

summary(drought_flood_df_nbin)
plot(parameters(drought_flood_df_nbin))
plot_residuals(drought_flood_df_nbin)

# check residuals
simulateResiduals(fittedModel = drought_flood_df_nbin, plot = TRUE)

# comparing hurdle poisson and hurdle nb
# likelihood ratio test
print(lrtest(drought_flood_df_pois, drought_flood_df_nbin)) 
# result is confusing

# AIC
AICtab(drought_flood_df_pois, drought_flood_df_nbin)
# NAs in the AIC 

# calculate 95% CI
conf <- confint(drought_flood_df_nbin)

###plot coefficients and CI
#zero-inflation (first part of hurdle- binomial)
# Create the dataframe
conf_df <- as.data.frame(conf) %>%
  rownames_to_column("variable") %>%
  rename(lower = `2.5 %`, upper = `97.5 %`) %>%
  mutate(estimate = conf[ , "Estimate"]) %>%
  select(variable, estimate, lower, upper) %>%
  mutate(sig = ifelse(lower * upper > 0, "yes", "no"))  # confidence interval does not cross 0

# filter out zi's to create conditional only and filter out NA's in sig (inf values)
conf_cond <- conf_df %>% 
  filter(str_starts(variable, "cond.")) %>% 
  filter(!is.infinite(upper)) %>% 
  filter(upper <= 5) # remove the one that is so huge

ggplot(data = conf_cond, aes(x = estimate, y = variable, color = sig)) +
  geom_point(size=3.5) +
  geom_pointrange(aes(xmin = lower, xmax = upper), lwd = 0.75) +
  geom_vline(xintercept = 0, lty = 2, lwd = 0.5) +
  theme_classic() +
  scale_x_continuous(breaks = seq(-4, 4, by = 1)) +
  labs(x = "Coefficient", y = "Variable", color = "Significant") +
  theme(text = element_text(family = "serif", size = 14)) +
  scale_color_manual(values = c("red3","deepskyblue4"))

# filter out cond's to create zero inflated only and filter out NA's in sig (inf values)
conf_zi <- conf_df %>% 
  filter(str_starts(variable, "zi.")) %>% 
  filter(!is.infinite(upper)) %>% 
  filter(upper <= 5) # remove the one that is so huge

ggplot(data = conf_zi, aes(x = estimate, y = variable, color = sig)) +
  geom_point(size=3.5) +
  geom_pointrange(aes(xmin = lower, xmax = upper), lwd = 0.75) +
  geom_vline(xintercept = 0, lty = 2, lwd = 0.5) +
  theme_classic() +
  scale_x_continuous(breaks = seq(-4, 4, by = 1)) +
  labs(x = "Coefficient", y = "Variable", color = "Significant") +
  theme(text = element_text(family = "serif", size = 14)) +
  scale_color_manual(values = c("red3","deepskyblue4"))

```


## Drought/Flood prevalence (presence/absence for myxozoans) [not currently working]
```{r Drought/Flood prevalence, echo=FALSE}
summary(drought_flood_prevalence <- glmmTMB(psite_prevalence ~ event*psite_type + (total_length_mm|fish_sp_x/parasite_taxonomic_group) + (1|ci/catalog_number) + (1|storm_intensity) + (1|year_collected/season) + (1|fish_sp_y/psite_spp_y), 
                      data = drought_flood_prevalence, family = binomial(link = "logit"), ziformula = ~ 1)) 

# diagnostics
#Evaluate residuals
s = simulateResiduals(fittedModel = drought_flood_prevalence, n = 250)
s$scaledResiduals
plot(s)
```




# prevalence 
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm), 
                                family = nbinom1, data = drought_flood_df_m)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm),
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_m)

# nbinom2 log

nbinom2log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm), 
                                family = nbinom2, data = drought_flood_df_m)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df_m)

# nbinom12 log

nbinom12log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm), 
                                family = nbinom12, data = drought_flood_df_m)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm), 
                                family = truncated_nbinom1, data = drought_flood_df_m)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm), 
                                family = truncated_nbinom2, data = drought_flood_df_m)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x/total_length_mm), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df_m)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = drought_flood_df_m)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_m)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = drought_flood_df_m)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df_m)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = drought_flood_df_m)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = drought_flood_df_m)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = drought_flood_df_m)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df_m)

```

```{r}
summary(nbinom1log)
summary(nbinom1sqrt)
summary(nbinom2log)
summary(nbinom2sqrt)
summary(nbinom12log)
summary(nbinom12sqrt)
summary(tnbinom1log)
summary(tnbinom1sqrt)
summary(tnbinom2log)
summary(tnbinom12sqrt)
summary(nbinom1logoff)
summary(nbinom1sqrtoff)
summary(nbinom2logoff)
summary(nbinom2sqrtoff)
summary(nbinom12logoff)
summary(nbinom12sqrtoff)
summary(tnbinom1logoff)
summary(tnbinom1sqrtoff)
summary(tnbinom2logoff)
summary(tnbinom2sqrtoff)

simulateResiduals(fittedModel = nbinom1log, plot = TRUE)
simulateResiduals(fittedModel = nbinom1sqrt, plot = TRUE)
simulateResiduals(fittedModel = nbinom2log, plot = TRUE)
simulateResiduals(fittedModel = nbinom2sqrt, plot = TRUE)
simulateResiduals(fittedModel = nbinom12log, plot = TRUE)
simulateResiduals(fittedModel = nbinom12sqrt, plot = TRUE)
simulateResiduals(fittedModel = tnbinom1log, plot = TRUE)
simulateResiduals(fittedModel = tnbinom1sqrt, plot = TRUE)
simulateResiduals(fittedModel = tnbinom2log , plot = TRUE)
simulateResiduals(fittedModel = tnbinom12sqrt, plot = TRUE)
simulateResiduals(fittedModel = nbinom1logoff, plot = TRUE)
simulateResiduals(fittedModel = nbinom1sqrtoff, plot = TRUE)
simulateResiduals(fittedModel = nbinom2logoff, plot = TRUE)
simulateResiduals(fittedModel = nbinom2sqrtoff, plot = TRUE)
simulateResiduals(fittedModel = nbinom12logoff, plot = TRUE)
simulateResiduals(fittedModel = nbinom12sqrtoff, plot = TRUE)
simulateResiduals(fittedModel = tnbinom1logoff, plot = TRUE)
simulateResiduals(fittedModel = tnbinom1sqrtoff, plot = TRUE)
simulateResiduals(fittedModel = tnbinom2logoff, plot = TRUE)
simulateResiduals(fittedModel = tnbinom2sqrtoff, plot = TRUE)



# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()


# this model is the best fit
simulateResiduals(fittedModel = tnbinom2log, plot = TRUE)
summary(tnbinom2log)
plot(parameters(tnbinom2log))

```





