---
title: "Drought and Flood: NOLA CAREER Project"
author: "Connor Whalen"
date: "2025-02-18"
output:
  html_document:
    theme: readable
    highlight: textmate
    toc: true
    toc_float: true
    toc_depth: 3
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Introduction
This file contains all code pertaining to the CAREER project in NOLA's drought and flood analysis. 

# Setup
#### Install packages.
```{r package install, eval=FALSE, echo=FALSE}
install.packages("tidyverse")
install.packages("janitor")
install.packages("ggeffects")
install.packages("ggpubr")
install.packages("glmmTMB")
install.packages("devtools")
devtools::install_github("johannesbjork/LaCroixColoR")
install.packages("patchwork")
install.packages("ggh4x")
install.packages("vistime")
install.packages("DHARMa")
```

#### Load packages.
```{r package load, echo=FALSE}
library(ggpubr)
library(ggeffects)
library(tidyverse)
library(readr)
library(dbplyr)
library(lubridate)
library(ggplot2)
library(stringr)
library(glmmTMB)
#library(lmerTest)
library(lme4)
source("~/Desktop/UW/Dissertation/theme_ctmt.R")
library(LaCroixColoR)
library(patchwork)
library(ggh4x)
library(vistime)
library(car)
library(DHARMa)
```
#### Load full datasets (parasites collected and NOAA SPI precipitation data) and prep data for analysis
```{r datasets and dataframe loading and general df clean and prep for analysis, echo=FALSE}
full_data <- read.csv("~/Desktop/UW/TUBRI/data/processed/Full_dataset_physical_2024.09.25.csv") %>% 
  janitor::clean_names()

SPI_data <- read.csv("~/Desktop/UW/Chapter1 NOLA/datasets/SPI data - Sheet1.csv") %>% 
  janitor::clean_names()

# Prep all data for analysis, inclduing assigning parasite type categories, abundance and prevalence counts, and establishing correct column date structure
full_data <- full_data %>%
  mutate(psite_type = case_when(
    str_detect(fish_psite_combo, "ACAN") ~ "acanthocephalan",
    str_detect(fish_psite_combo, "ACANTH") ~ "acanthocephalan",
    str_detect(fish_psite_combo, "CEST") ~ "cestode",
    str_detect(fish_psite_combo, "CILI") ~ "ciliate",
    str_detect(fish_psite_combo, "COPE") ~ "copepod",
    str_detect(fish_psite_combo, "LEECH") ~ "leech",
    str_detect(fish_psite_combo, "META") ~ "trematode_metacercaria",
    str_detect(fish_psite_combo, "MONO") ~ "monogenean",
    str_detect(fish_psite_combo, "MYX") ~ "myxozoan",
    str_detect(fish_psite_combo, "MYXO") ~ "myxozoan",
    str_detect(fish_psite_combo, "NEM") ~ "nematode",
    str_detect(fish_psite_combo, "NMORPH") ~ "nematomorph",
    str_detect(fish_psite_combo, "TREM") ~ "trematode",
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(psite_abundance = case_when(
    str_detect(fish_psite_combo, "ACAN") ~ psite_count,
    str_detect(fish_psite_combo, "ACANTH") ~ psite_count,
    str_detect(fish_psite_combo, "CEST") ~ psite_count,
    str_detect(fish_psite_combo, "CILI") ~ psite_count,
    str_detect(fish_psite_combo, "COPE") ~ psite_count,
    str_detect(fish_psite_combo, "LEECH") ~ psite_count,
    str_detect(fish_psite_combo, "META") ~ psite_count,
    str_detect(fish_psite_combo, "MONO") ~ psite_count,
    str_detect(fish_psite_combo, "NEM") ~ psite_count,
    str_detect(fish_psite_combo, "NMORPH") ~ psite_count,
    str_detect(fish_psite_combo, "TREM") ~ psite_count,
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(psite_prevalence = case_when(
    str_detect(fish_psite_combo, "MYX") ~ psite_count,
    str_detect(fish_psite_combo, "MYXO") ~ psite_count,
    TRUE ~ NA
  ))

full_data <- full_data %>%
  mutate(date = as.Date(paste(year_collected, month_collected, day_collected, sep = "-"))) 

SPI_data <- SPI_data %>% 
  mutate(date = as.Date(date))

full_data <- full_data %>% 
  mutate(psite_prevalence = as.numeric(psite_prevalence))

full_data <- full_data %>% 
  left_join(SPI_data, by = "date")

# view(table(full_data$category))

## assign control and flood categories to the different SPI value categories 
# category = average = true control
# category = abnormally wet / dry = marginal control 
# category = exceptionally wet / dry = full drought/flood

full_data <- full_data %>%
  mutate(event = case_when(
    str_detect(category, "exceptionally wet") ~ "flood",
    str_detect(category, "extremely wet") ~ "flood",
    str_detect(category, "severely wet") ~ "flood",
    str_detect(category, "moderately wet") ~ "flood",
    str_detect(category, "exceptionally dry") ~ "drought",
    str_detect(category, "extremely dry") ~ "drought",
    str_detect(category, "severely dry") ~ "drought",
    str_detect(category, "moderately dry") ~ "drought",
    str_detect(category, "abnormally wet") ~ "control",
    str_detect(category, "abnormally dry") ~ "control",
    str_detect(category, "average") ~ "control", # there are no parasites collected in the "average" grouping
    TRUE ~ "marginal"
  )) %>% 
  mutate(event = as.factor(event)) %>% 
  mutate(category = as.factor(category)) %>% 
  mutate(psite_type = as.factor(psite_type))

```

## Data Prep and Cleaning
```{r filtering, eval = FALSE}
# check how many observations are in each category
table(full_data$psite_type)
# check how many of these are > 0 
full_data %>%
  filter(psite_abundance > 0) %>%
  count(psite_type)


# drop low replicate categories
drought_flood_df <- full_data %>%
  filter(psite_type %in% c("trematode", "trematode_metacercaria", "monogenean"))

# filter out all remaining NAs from the psite_abundance column
drought_flood_df <- drought_flood_df %>%
  filter(!is.na(psite_abundance))

#relevel to drop the non-used categories
drought_flood_df <- drought_flood_df %>%
  mutate(psite_type = factor(psite_type, 
                             levels = c("monogenean", "trematode", "trematode_metacercaria")))

# create new category for myxos
drought_flood_df_m <- full_data %>%
  filter(psite_type %in% c("myxozoan"))

# filter out all remaining NAs from the psite_abundance column
drought_flood_df_m <- drought_flood_df_m %>%
  filter(!is.na(psite_prevalence))

# filter each parasite type into their own df
dfam <- drought_flood_df %>% 
  filter(psite_type %in% c("monogenean"))
dfat <- drought_flood_df %>% 
  filter(psite_type %in% c("trematode"))
dfatm <- drought_flood_df %>% 
  filter(psite_type %in% c("trematode_metacercaria"))
```

Visualization and checking of data frame.
```{r head}
head(drought_flood_df)
table(drought_flood_df$event)
```

# Models
## Abundance
### 3 parasite types
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom1, data = drought_flood_df)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df)

# nbinom2 log

nbinom2log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2, data = drought_flood_df)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df)

# nbinom12 log

nbinom12log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom12, data = drought_flood_df)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom1, data = drought_flood_df)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom2, data = drought_flood_df)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = drought_flood_df)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = drought_flood_df)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = drought_flood_df)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = drought_flood_df)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = drought_flood_df)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df)


# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()

# this model is the best fit

dfa_nbinom2log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2, data = drought_flood_df)

simulateResiduals(fittedModel = dfa_nbinom2log, plot = TRUE)
summary(dfa_nbinom2log)
plot(parameters(dfa_nbinom2log))
```

### Monogene Abundance
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1, data = dfam)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1(link = "sqrt"), data = dfam)

# nbinom2 log

nbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = dfam)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom2(link = "sqrt"), data = dfam)

# nbinom12 log

nbinom12log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12, data = dfam)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12(link = "sqrt"), data = dfam)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1, data = dfam)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1(link = "sqrt"), data = dfam)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2, data = dfam)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2(link = "sqrt"), data = dfam)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = dfam)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = dfam)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = dfam)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = dfam)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = dfam)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = dfam)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = dfam)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),  
                                family = truncated_nbinom1(link = "sqrt"), data = dfam)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = dfam)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),
                                family = truncated_nbinom2(link = "sqrt"), data = dfam)

# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()

# this is best model 
mono_final_df <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = dfam)

simulateResiduals(fittedModel = mono_final_df, plot = TRUE)
summary(mono_final_df)
plot(parameters(mono_final_df))


```

### Trematode Abundance
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1, data = dfat)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1(link = "sqrt"), data = dfat)

# nbinom2 log

nbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = dfat)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom2(link = "sqrt"), data = dfat)

# nbinom12 log

nbinom12log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12, data = dfat)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12(link = "sqrt"), data = dfat)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1, data = dfat)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1(link = "sqrt"), data = dfat)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2, data = dfat)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2(link = "sqrt"), data = dfat)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = dfat)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = dfat)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = dfat)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = dfat)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = dfat)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = dfat)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = dfat)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),  
                                family = truncated_nbinom1(link = "sqrt"), data = dfat)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = dfat)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),
                                family = truncated_nbinom2(link = "sqrt"), data = dfat)

# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()

# this is best model (none of them fit super well)
trem_final_df <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = dfat)

simulateResiduals(fittedModel = trem_final_df, plot = TRUE)
summary(trem_final_df)
plot(parameters(trem_final_df))


```


### Trematode Metacercaria Abundance
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1, data = dfatm)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1(link = "sqrt"), data = dfatm)

# nbinom2 log

nbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = dfatm)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom2(link = "sqrt"), data = dfatm)

# nbinom12 log

nbinom12log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12, data = dfatm)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom12(link = "sqrt"), data = dfatm)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1, data = dfatm)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom1(link = "sqrt"), data = dfatm)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2, data = dfatm)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = truncated_nbinom2(link = "sqrt"), data = dfatm)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = dfatm)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = dfatm)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = dfatm)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = dfatm)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = dfatm)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = dfatm)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = dfatm)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),  
                                family = truncated_nbinom1(link = "sqrt"), data = dfatm)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = dfatm)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) +
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)),
                                family = truncated_nbinom2(link = "sqrt"), data = dfatm)

# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()

# this is best model -- not the lowest AIC but the best fit of all parameters and isnt
meta_final_df <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1(link = "sqrt"), data = dfatm)


simulateResiduals(fittedModel = meta_final_df, plot = TRUE)
summary(meta_final_df)
plot(parameters(meta_final_df))
```

## Prevalence  
```{r}
## normal

# nbinom1 log

nbinom1log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1, data = drought_flood_df_m)

# nbinom1 sqrt

nbinom1sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_m)

# nbinom2 log

nbinom2log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = drought_flood_df_m)

# nbinom2 sqrt

nbinom2sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df_m)

# nbinom12 log

nbinom12log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom12, data = drought_flood_df_m)

#nbinom12 sqrt

nbinom12sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom1 log

tnbinom1log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom1, data = drought_flood_df_m)

# truncated_nbinom1 sqrt

tnbinom1sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom2 log

tnbinom2log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom2, data = drought_flood_df_m)

# truncated_nbinom2 sqrt

tnbinom12sqrt <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df_m)


## offset

# nbinom1 log

nbinom1logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = drought_flood_df_m)

# nbinom1 sqrt

nbinom1sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_m)

# nbinom2 log

nbinom2logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2, data = drought_flood_df_m)

# nbinom2 sqrt

nbinom2sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom2(link = "sqrt"), data = drought_flood_df_m)

# nbinom12 log

nbinom12logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12, data = drought_flood_df_m)

#nbinom12 sqrt

nbinom12sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom12(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom1 log

tnbinom1logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1, data = drought_flood_df_m)

# truncated_nbinom1 sqrt

tnbinom1sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom1(link = "sqrt"), data = drought_flood_df_m)

# truncated_nbinom2 log

tnbinom2logoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2, data = drought_flood_df_m)

# truncated_nbinom2 sqrt

tnbinom2sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = truncated_nbinom2(link = "sqrt"), data = drought_flood_df_m)


# List of all model objects
models <- list(
  nbinom1log, nbinom1sqrt, nbinom2log, nbinom2sqrt, nbinom12log, nbinom12sqrt,
  tnbinom1log, tnbinom1sqrt, tnbinom2log, tnbinom12sqrt,
  nbinom1logoff, nbinom1sqrtoff, nbinom2logoff, nbinom2sqrtoff,
  nbinom12logoff, nbinom12sqrtoff, tnbinom1logoff, tnbinom1sqrtoff,
  tnbinom2logoff, tnbinom2sqrtoff
)

# Model names
model_names <- c(
  "nbinom1log", "nbinom1sqrt", "nbinom2log", "nbinom2sqrt", "nbinom12log", "nbinom12sqrt",
  "tnbinom1log", "tnbinom1sqrt", "tnbinom2log", "tnbinom12sqrt",
  "nbinom1logoff", "nbinom1sqrtoff", "nbinom2logoff", "nbinom2sqrtoff",
  "nbinom12logoff", "nbinom12sqrtoff", "tnbinom1logoff", "tnbinom1sqrtoff",
  "tnbinom2logoff", "tnbinom2sqrtoff"
)

# Simulate residuals and extract diagnostics
residual_summaries <- map2_df(models, model_names, function(model, name) {
  sim <- simulateResiduals(fittedModel = model, plot = FALSE)
  data.frame(
    model = name,
    dispersion = testDispersion(sim)$p.value,
    uniformity = testUniformity(sim)$p.value,
    outliers = testOutliers(sim)$p.value,
    AIC = AIC(model)
  )
})

# View and sort by AIC (lower is better) and test stats (higher p-values indicate better fit)
residual_summaries %>%
  arrange(AIC) %>%
  print()

# this model is the best fit -- swapped 4/27

dfp_tnbinom2log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom2, data = drought_flood_df_m)


simulateResiduals(fittedModel = dfp_tnbinom2log, plot = TRUE)
summary(dfp_tnbinom2log)
plot(parameters(dfp_tnbinom2log))
```




# ALL MODELS SUMMARY 
```{r}
# abundance 3 types
dfa_nbinom2log <- glmmTMB(psite_abundance ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + 
                                  (1|fish_sp_x) + (total_length_mm|fish_psite_combo),
                                ziformula = ~ event*psite_type + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_psite_combo) + (1|fish_sp_x) +
                                  (total_length_mm|fish_psite_combo), 
                                family = nbinom2, data = drought_flood_df)

simulateResiduals(fittedModel = dfa_nbinom2log, plot = TRUE)
summary(dfa_nbinom2log)
plot(parameters(dfa_nbinom2log))

# prevalence -- DONT USE THIS ONE
dfp_tnbinom2log <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = truncated_nbinom2, data = drought_flood_df_m)


simulateResiduals(fittedModel = dfp_tnbinom2log, plot = TRUE)
summary(dfp_tnbinom2log)
plot(parameters(dfp_tnbinom2log))


### USE THIS MODEL FOR PREVALENCE NOT THE TRUNCATED ONE
nbinom1sqrtoff <- glmmTMB(psite_prevalence ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(sqrt(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + 
                                  offset(sqrt(total_length_mm)), 
                                family = nbinom1(link = "sqrt"), data = drought_flood_df_m)

simulateResiduals(fittedModel = nbinom1sqrtoff, plot = TRUE)
summary(nbinom1sqrtoff)
plot(parameters(nbinom1sqrtoff))


```

NO LONGER USING THESE ONES
```{r}
# abundance mono
mono_final_df <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + 
                                  (1|fish_sp_x) + offset(log(total_length_mm)),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (1|fish_sp_x) + offset(sqrt(total_length_mm)), 
                                family = nbinom1, data = dfam)

simulateResiduals(fittedModel = mono_final_df, plot = TRUE)
summary(mono_final_df)
plot(parameters(mono_final_df))

# abundance trem
trem_final_df <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom2, data = dfat)

simulateResiduals(fittedModel = trem_final_df, plot = TRUE)
summary(trem_final_df)
plot(parameters(trem_final_df))

# abundance meta
meta_final_df <- glmmTMB(psite_abundance ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x),
                                ziformula = ~ event + ci + (1|catalog_number) + (1|year_collected/season) + (total_length_mm|fish_sp_x), 
                                family = nbinom1(link = "sqrt"), data = dfatm)


simulateResiduals(fittedModel = meta_final_df, plot = TRUE)
summary(meta_final_df)
plot(parameters(meta_final_df))


```

# Plots
###
Create color palette and assign faceting labels.
```{r color palette and facet labels, echo=FALSE}
lacroix_palettes_list <- LaCroixColoR::lacroix_palettes

my_pal <- lacroix_palette("Pamplemousse", n = 5, type = "continuous")

parasite_order <- c(
  "trematode", "trematode_metacercaria", "myxozoan", "monogenean", "ciliate",
  "nematode", "acanthocephalan", "cestode", "copepod", "nematomorph"
)

parasite_labels <- c(
  "trematode" = "Trematode",
  "trematode_metacercaria" = "Metacercaria",
  "myxozoan" = "Myxozoan",
  "monogenean" = "Monogenean",
  "ciliate" = "Ciliate",
  "nematode" = "Nematode",
  "cestode" = "Cestode",
  "acanthocephalan" = "Acanthocephalan",
  "copepod" = "Copepod", 
  "nematomorph" = "Nematomorph"
)


storm_order <- c("five", "four", "three", "two", "one", "ts", "control")

storm_labels <- c(
  "five" = "5",
  "four" = "4",
  "three" = "3",
  "two" = "2",
  "one" = "1",
  "ts" = "TS", 
  "no event" = "control"
)

season_order <- c(
  "winter", "spring", "summer", "fall"
)

season_labels <- c(
  "winter" = "Winter",
  "spring" = "Spring", 
  "summer" = "Summer", 
  "fall" = "Fall"
)

timing_order <- c(
  "pre", "during", "post"
)

timing_labels <- c(
  "pre" = "Pre",
  "post" = "Post", 
  "control" = "During",
  "flood" = "During", 
  "drought" = "During"
)

event_labels <- c(
  "drought" = "drought", 
  "flood" = "flood"
)

```
Mutate the drought/flood dataset so that the total sum of each type of parasite can be plotted:
```{r drought/flood sum to plot all parasites added together and scale to mean, echo=FALSE, eval=FALSE}
drought_flood_df_sum <- drought_flood_df %>%
  group_by(psite_type, year_collected, event, timing, drought_flood, category) %>%
  summarize(total_psite_count = sum(psite_count, na.rm = TRUE), .groups = "drop") %>% 
  filter(total_psite_count != "0") %>%
  filter(!is.na(psite_type), 
         psite_type != "leech", 
         psite_type != "nematomorph")

drought_flood_df_sum <- drought_flood_df_sum %>%
    mutate(psite_type = fct_relevel(psite_type, parasite_order))

drought_flood_df_sum <- drought_flood_df_sum %>%
    mutate(season = fct_relevel(season, season_order))

drought_flood_df_sum <- drought_flood_df_sum %>%
    mutate(timing = fct_relevel(timing, timing_order))

# including zeroes
drought_flood_df_sum2 <- drought_flood_df %>%
  group_by(psite_type, year_collected, season, event, timing, drought_flood, category) %>%
  summarize(total_psite_count = sum(psite_count, na.rm = TRUE), .groups = "drop") %>%
  filter(!is.na(psite_type), 
         psite_type != "leech")

drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
    mutate(psite_type = fct_relevel(psite_type, parasite_order))

drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
    mutate(season = fct_relevel(season, season_order))

drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
    mutate(timing = fct_relevel(timing, timing_order))

# scale to mean -- should probably update this parameter
sum(drought_flood_df_sum2$total_psite_count, na.rm = TRUE)
28842/195 # average rate of parasitism across all observations is 147.9077
# in this case, each categorical 0 is counted only once, so the sum of each category includes summing all the zeroes but if there is only zeroes in a category, then those will show up as zero

drought_flood_df_sum2 <- drought_flood_df_sum2 %>%
  mutate(relative_count = total_psite_count - 148)
```
Various plots.
```{r various plots, echo=FALSE, eval=FALSE}
ggplot(drought_flood_df_sum,
       aes(x = year_collected, y = drought_flood, fill = event)) + 
  geom_col(position = "dodge") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("") + 
  xlab("") + 
  scale_fill_manual(
  values = c("drought" = "#F28A8A", "flood" = "#1BB6AF"), 
  name = "",
  labels = timing_labels) 

######

ggplot(full_data,
       aes(x = year_collected, y = drought_minus_flood)) + 
  geom_col(position = "dodge") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("") + 
  xlab("")

ggplot(full_data,
       aes(x = drought_minus_flood, y = psite_abundance)) + 
  geom_bin_2d() +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("") + 
  xlab("")

custom_y_t3 <- list(
  scale_y_continuous(limits = c(0, 3000), breaks = c(0, 1500, 3000)),
  scale_y_continuous(limits = c(0, 1200), breaks = c(0, 600, 1200)),
  scale_y_continuous(limits = c(0, 600), breaks = c(0, 300, 600)),
  scale_y_continuous(limits = c(0, 400), breaks = c(0, 200, 400)),
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100)),
  scale_y_continuous(limits = c(0, 50), breaks = c(0, 25, 50)),  
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 10, 20)),
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 5, 10)),
  scale_y_continuous(limits = c(0, 2), breaks = c(0, 1, 2))
)

# by parasite spp
ggplot(drought_flood_df_sum,
       aes(x = event, y = total_psite_count, fill = timing)) + 
  geom_col(position = "dodge") + 
  facet_wrap(~ psite_type, labeller = labeller(psite_type = parasite_labels), scales = "free_y") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF", "drought" = "#95C65C", "flood" = "#95C65C", "control" = "#95C65C"), 
  name = "",
  labels = timing_labels) 

## by just timing
ggplot(drought_flood_df_sum,
       aes(x = event, y = total_psite_count, fill = timing)) + 
  geom_col() + 
  facet_wrap(~ timing) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF", "drought" = "#95C65C", "flood" = "#95C65C", "control" = "#95C65C"), 
  name = "",
  labels = timing_labels) 

## by species??

## by relative count
ggplot(drought_flood_df_sum2,
       aes(x = event, y = relative_count, fill = timing)) + 
  geom_col(position = "dodge") + 
  facet_wrap(~ psite_type, labeller = labeller(psite_type = parasite_labels), scales = "free_y") +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("pre" = "#F28A8A", "post" = "#1BB6AF", "drought" = "#95C65C", "flood" = "#95C65C", "control" = "#95C65C"), 
  name = "",
  labels = timing_labels) 


## include year of collection
ggplot(drought_flood_df_sum2,
       aes(x = year_collected, y = relative_count, fill = event)) + 
  geom_col() +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) + 
  geom_hline(yintercept = 0, color = "black") +
  ylab("Relative Parasite Count") + 
  xlab("Year Collected") + 
  scale_fill_manual(
    values = c("drought" = "#F28A8A", "flood" = "#1BB6AF", "control" = "#95C65C"), 
    name = "",
    labels = season_labels
  )

ggplot(drought_flood_df_sum,
       aes(x = event, y = total_psite_count, fill = event)) + 
  geom_col() +
  facet_wrap(~ timing) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines"),
    axis.text = element_text(size = 8, color = "grey30"),
    axis.ticks = element_line(size = 0.2, color = "darkgrey")
  ) +
  ylab("Parasite Count") + 
  xlab("Timing") + 
  scale_fill_manual(
  values = c("drought" = "#F28A8A", "flood" = "#1BB6AF", "control" = "#95C65C"), 
  name = "",
  labels = season_labels) 

facet_labels2 <- c(
  "drought" = "Drought",
  "flood" = "Flood"
)

ggplot(drought_flood_df,
       aes(x = season, y = psite_abundance, fill = ewe_type)) + 
  geom_boxplot() + facet_wrap(~ci) +
  theme(
    strip.background = element_rect(fill = NA, color = NA),
    panel.background = element_rect(fill = NA, color = "darkgrey"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    panel.spacing.y = unit(0, "lines")
  ) +
  ylab("Parasite Abundance") + 
  xlab("Collection Date") +
  scale_fill_manual(values = my_pal[1:5], name = '')
```







## primary
drought/flood conditional
```{r}
# Drought/Flood Conditional Model Results
df_conditional <- tribble(
  ~Parasite_Type, ~Effect, ~Estimate, ~SE, ~p_value,
  "Trematode", "Drought vs Baseline (Monogene)", 1.977, 1.0, 0.0406,
  "Trematode_Metacercaria", "Flood vs Baseline (Monogene)", 2.771, 1.0, 0.00559,
  "Trematode_Metacercaria", "Impact vs Control", 6.940, 1.0, 0.0001,
  "Trematode_Metacercaria", "Flood Event vs None", 2.505, 1.0, 0.0123,
  "Monogenean", "Baseline (Intercept)", -5.506, 1.0, 0.0001
)

ggplot(df_conditional, aes(x = reorder(Effect, Estimate), y = Estimate, fill = Parasite_Type)) +
  geom_col(width = 0.6) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.2) +
  coord_flip() +
  labs(
    title = "Drought/Flood Effects on Parasite Abundance (Conditional Model)",
    x = NULL,
    y = "Model Estimate (log scale)"
  ) +
  scale_fill_brewer(palette = "Paired") +
  theme_minimal(base_size = 13)

```

drought/flood zi
```{r}
# Drought/Flood Zero-Inflated Model Results
df_zi <- tribble(
  ~Parasite_Type, ~Effect, ~Estimate, ~SE, ~p_value,
  "Trematode_Metacercaria", "Flood/Drought vs Monogene", -2.101, 1.0, 0.03564,
  "Trematode", "Baseline Zero Inflation (vs Monogene)", 2.508, 1.0, 0.0122,
  "Trematode_Metacercaria", "TMC Zero Counts", 3.037, 1.0, 0.00239,
  "Trematode", "More Zeros under Drought", 2.401, 1.0, 0.01633,
  "Drought_Event", "Zeros Decrease Under Drought", -1.977, 1.0, 0.04802,
  "Monogenean", "Drought Event (Fewer Zeros)", -2.667, 1.0, 0.00765,
  "Monogenean", "Baseline (Intercept)", -9.645, 1.0, 0.0001,
  "All", "Overall High Zero Inflation", 3.096, 1.0, 0.00196,
  "All", "Baseline Zero Inflation", 6.315, 1.0, 0.0001
)

# Clean up labeling if needed
ggplot(df_zi, aes(x = reorder(Effect, Estimate), y = Estimate, fill = Parasite_Type)) +
  geom_col(width = 0.6) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.2) +
  coord_flip() +
  labs(
    title = "Drought/Flood Effects on Parasite Prevalence (Zero-Inflated Model)",
    x = NULL,
    y = "Model Estimate (log odds of zero abundance)"
  ) +
  scale_fill_brewer(palette = "Set3") +
  theme_minimal(base_size = 13)

```




abundance:
```{r}
# color palette -- hurricane = #CB87B4, control = #F4B95A, drought = #D84D16, flood = #1BB6AF
# trem = #c9ad79 , meta = #F66387 , mono = #A6E000 , myxo = #07c4c5
connor_theme <- theme(legend.position = "top", 
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 14),
        strip.background = element_rect(fill = NA, color = NA),
        panel.background = element_rect(fill = NA, color = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.spacing.x = unit(0, "lines"),
        panel.spacing.y = unit(0, "lines"),
        axis.text = element_text(size = 8, color = "grey30"),
        axis.ticks = element_line(size = 0.2, color = "darkgrey"))

# finding 3) metas are more abundant in drought
# finding 4) metas are more abundant in flood

md_1 <- ggpredict(dfa_nbinom2log, terms = c("psite_type"))

md_1 <- md_1 %>%
  rename(
    psite_type = x,
    estimate = predicted,
    se = std.error,
    lower = conf.low,
    upper = conf.high,
    event = group)

# finding 1) meta abundance is lower than reference
ggplot(md_1,
       aes(x = event, y = estimate)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, group = psite_type),
                width = 0.05,
                position = position_dodge(width = 0.5)) +
  geom_line(aes(group = psite_type, linetype = psite_type),
            position = position_dodge(width = 0.5)) +
  geom_point(aes(fill = psite_type, group = psite_type),
             pch = 21, size = 5,
             position = position_dodge(width = 0.5)) +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79")) +
  labs(x = "Event", y = "Estimate", fill = "Event", linetype = "Event") +
  connor_theme

# finding 2) trematode abundance in drought is higher than in control
md_2 <- ggpredict(dfa_nbinom2log, terms = c("psite_type", "event"))

md_2 <- md_2 %>%
  rename(
    psite_type = x,
    estimate = predicted,
    se = std.error,
    lower = conf.low,
    upper = conf.high,
    event = group)

# remove trems from dataset:
md_2 <- md_2 %>% 
  filter(psite_type %in% c("trematode", "monogenean"))

# finding 1) meta abundance is lower than reference
ggplot(md_2,
       aes(x = event, y = estimate)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, group = psite_type),
                width = 0.05,
                position = position_dodge(width = 0.5)) +
  geom_line(aes(group = psite_type, linetype = psite_type),
            position = position_dodge(width = 0.5)) +
  geom_point(aes(fill = psite_type, group = psite_type),
             pch = 21, size = 5,
             position = position_dodge(width = 0.5)) +
  scale_fill_manual(values = c("trematode_metacercaria" = "#AFDFEF", "monogenean" = "#A6E000", "trematode" = "#c9ad79")) +
  labs(x = "Event", y = "Estimate", fill = "Event", linetype = "Event") +
  connor_theme



## still need to plot the ZIs 
```

```{r}
library(emmeans)

# Estimate marginal means
emm <- emmeans(dfa_nbinom2log, ~ psite_type * event)

# Pairwise comparisons (optional: by event or by psite_type)
pairwise_tests <- contrast(emm, method = "pairwise", by = "event", adjust = "tukey")
summary(pairwise_tests)
```





prevalence:
```{r}


## still need to plot the ZIs 
```














